### 2020-05-12 manuscript.tex
Zero draft.

\documentclass[review]{elsarticle}

\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{soul,color}
\usepackage{textcomp}

\usepackage{lineno,hyperref}
\modulolinenumbers[1]

\newcommand{\tr}[1]{\mathrm{Tr} \left\{ #1 \right\}}
\newcommand{\sx}{I_\mathrm{x}}
\newcommand{\sy}{I_\mathrm{y}}
\newcommand{\sz}{I_\mathrm{z}}
\newcommand{\hdz}{H_\mathrm{dz}}

\journal{Journal of Magnetic Resonance}

%% `Elsevier LaTeX' style
%\bibliographystyle{elsarticle-num}
\bibliographystyle{naturemag}

%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frontmatter}

\title{Many-spin entanglement in multiple quantum NMR with a dipolar ordered initial state}

\author[icp]{E.~B.~Feldman}
\author[icp,msu]{I.~D.~Lazarev} %

\address[icp]{Institute of Problems of Chemical Physics of Russian Academy of Sciences, \\ Chernogolovka, Moscow Region, Russia 142432}
\address[msu]{Faculty of Fundamental Physical-Chemical Engineering, Lomonosov Moscow State University, GSP-1, Moscow, Russia 119991}

\begin{abstract}
Many-spin entanglement is investigated for a gas spin-carrying molecules (atoms) in nanocavities 
in conditions of the multiple quantum (MQ) NMR with a dipolar ordered initial state.
MQ NMR with the dipolar ordered state opens new possibilities for an exploration of many-spin entanglement. 
The second moment of a distribution of intensities of MQ NMR coherences,
which provides a lower bound of the quantum Fisher information, 
was used for an estimation of the number of entangled spins. 
Many-spin entanglement is investigated at different temperatures and different numbers of spins in the system under consideration.
\end{abstract}

\begin{keyword}
? \sep ?
\end{keyword}

\end{frontmatter}

\linenumbers

\section{Introduction}
\label{sec:1}

Entanglement~\cite{Nielsen_2009} is a very important quantum conception, which is responsible in particular, for advantages of quantum computers our their classical counterparts.
Recently demonstrated quantum supremacy using a programmable superconducting processor~\cite{Arute2019} is also connected with entanglement which is absent in classical Physicsa.
Among numerous methods of an investigation of entanglement we concentrate on multiple quantum (MQ) NMR in solids~\cite{Baum_1985}, which was widely used characterize entanglement in binary system~\cite{Furman_2008,Furman_2009,Fel_dman_2008,Fel_dman_2012}. 
It turned out that the MQ NMR spectroscopy~\cite{Nielsen_2009} allows us to extract also information about many spin entanglement~\cite{?}, 
if one attracts for the analysis the quantum Fisher information~\cite{T_th_2014,Pezz__2018}.

The quantum Fisher information describes quickness of changing quantum states determined by the density matrix at changing some parameter. 
In MQ NMR spectroscopy that parameter is the phase increment between the radio-frequency (rf) pulses irradiating the system on preparation and mixing periods of the MQ NMR experiment~\cite{Baum_1985} in proportional to the evolution time.
That procedure leads to a separation of the signals.
Corresponding to the MQ NMR coherences of different orders, and obtaining the total MQ NM spectrum.
Using the quantum Fisher information (QFI)~\cite{Liu_2014} for an analysis of the MQ NMR spectra one can extract very important information about many-spin entanglement.
The point is that there is a relation between the second moment of the MQ NMR spectrum~\cite{Khitrin_1997} and the quantum Fisher information~\cite{G_rttner_2018,Doronin_2019}.
Moreover the second moment of the MQ NMR spectrum provides a lower bound on the quantum Fisher information~\cite{G_rttner_2018}.
It means that the MQ NMR spectroscopy is a valuable method for solving quantum information problems.

Many-spin entanglement was investigated~\cite{Doronin_2019} on a non spherical nanopore filled with a gas of spin-carrying molecules in a strong external magnetic field~\cite{Baugh_2001,Doronin_2009}.
The thermal equilibrium initial state of the system was determined by the one-spin Zeemann interaction with the external magnetic field~\cite{Doronin_2007a}.
It is also possible to investigate many-spin entanglement when the same system is initially prepared in the dipolar ordered state~\cite{Andrew_1971} using either the adiabatic demagnetization method in a rotating reference frame (RRF)~\cite{Andrew_1971,Slichter_1961} or the two-pulse Broekart-Jeener sequence~\cite{Andrew_1971,Jeener_1967}.
The MQ NMR dynamics with this initial state have been simulated both in small spin-systems~\cite{Doronin_2007a,Doronin_2007b} and in the system consisting of 200-600 spin-carrying molecules (atoms) filled in a nanopore~\cite{Doronin_2011}.
The approaches developed for those investigations are restricted by high temperatures and cannot be applied in order to study many-spin entanglement.

In the present article we consider an intermediate temperature case with low Zeemann temperatures and high dipolar ones. 
Nuclear magnetic ordering~\cite{Abragam_1982} is outside our consideration.
Notice also that the two-pulse Broekart-Jeneer experiment~\cite{Jeener_1967} was performed in the high temperature case.
We prove theoretically that the experiment~\cite{Jeener_1967} can be realized also for the intermediate temperature case of the article. 
It was shown~\cite{Doronin_2011} that in the MQ NMR experiment with the dipolar ordered initial state MQ NMR coherences emerge faster 
than in the MQ NMR experiment with the thermal equilibrium initial state in a strong external magnetic field.
It is important for many-spin entanglement investigations, because they are connected with calculations of the second moment of the distribution at MQ NMR coherences. 
It is also very important for an investigation of the spreading correlation~\cite{Baugh_2001,Baum_1986,S_nchez_2014,Munowitz_1987} and localization effects~\cite{Alvarez_2015,Wei_2018}.
At that the spreading rate can be described through out-of-time ordered correlations which are connected with the distribution of MQ NMR coherences.

The present paper investigates many-spin entanglement using the MQ NMR spectrum of spin-carrying atoms (molecules) in a nanopore when the system is prepared in the dipolar ordered state.
In Sec.~\ref{sec:2} the theory of MQ NMR dynamics at low Zeemann and high dipolar temperatures is developed.
An analytical solution for the MQ NMR dynamics of a three-spin system is obtained at such temperatures in Sec.~\ref{sec:3}.
The second moment of the MQ NMR spectrum as a measure of many-spin entanglement is considered in Sec.~\ref{sec:4}.
The dependence of many-spin entanglement on the dipolar temperature and the number of spin in the system is investigated in Sec.~\ref{sec:5}.
We briefly summarize our results in the concluding Sec.~\ref{sec:6}.
In Appendix we show that the two-pulse Broekart-Jeener sequence can be used in the case when the Zeemann temperature is low and the dipole one is high.

\section{Theory of MQ NMR dynamics in a nanopore at low Zeemann and high dipolar temperatures}
\label{sec:2}

MQ NMR dynamics in a nanopore governs the Hamiltonian~\cite{Doronin_2019,Doronin_2009} 
%
\begin{equation}
    \label{eq:1}
    H_{\mathrm{MQ}} = - \dfrac{D}{4} \left[
        \left(I^{+}\right)^{2} 
        + \left(I^{-}\right)^{2} 
    \right] ,
\end{equation}
%
where 
%
\begin{equation}
    \label{eq:2}
    I^{\pm} = \sum\limits_{j=1}^{N} I_{j}^{\pm},
\end{equation}
%
$N$ is the number of the spins in the nanopore $I^{\pm}_{j}$, are the raising or lowering operators of spin $j$, and $D$ is the dipolar coupling constant averaged by the fast molecular diffusion of spin-carrying atoms (molecules) in nanopores.
We underline that the dipolar coupling constant $D$ is the same for all pairs at interacting spins in the nanopore~\cite{Doronin_2019,Doronin_2009}.
The density matrix $\rho(\tau)$ on the preparation period of the MQ NMR experiment~\cite{Baum_1985} can be obtained from the Liouville evolution equation~\cite{Andrew_1971,Abragam_1982} 
%
\begin{equation}
    \label{eq:3}
    i\dfrac{\mathrm{d}\rho(\tau)}{\mathrm{d}\tau} = \left[
    H_\mathrm{MQ},\rho(\tau)
    \right]
\end{equation}
%
with the initial thermodynamic equilibrium density matrix 
%
\begin{equation}
    \label{eq:4}
       \rho(0) = \rho_\mathrm{eq} = \dfrac{1}{Z}
       e^{
            \frac{\hslash \omega}{k} \alpha_\mathrm{z} I_\mathrm{z} 
            + \frac{\hslash }{k} \beta_\mathrm{d} H_\mathrm{dz}
        },
\end{equation}
%
where 
$Z = \mathrm{Tr} \left\{ e^{\frac{\hslash \omega}{k} \alpha_\mathrm{z} I_\mathrm{z} + \frac{\hslash  }{k} \beta_\mathrm{d} H_\mathrm{dz}} \right\}$ is the partition function, 
$\hslash$ and $k$ are the Plank and Boltzmann constants, 
$\omega_{0}$  is the Larmor frequency , $I_\mathrm{z}$ is the operator of the projection of the total spin angular momentum on the z-axis, 
which is directed along the strong external magnetic field,  
$H_\mathrm{dz}$ is the secular part of the dipole-dipole interaction~\cite{?}.
Hamiltonian in a strong external magnetic field, and $\alpha_\mathrm{z}$, $\beta_\mathrm{d}$ are the inverse Zeemann and dipolar temperatures. 
We will consider the case when the Zeemann temperature is low $({\frac{\hslash \omega}{k} \alpha_\mathrm{z}}\gg 1)$ 
and the dipolar temperature is high $\left( \frac{\hslash{D}}{k}\beta_\mathrm{d} \ll 1\right)$.
For concreteness we suppose that $\omega_{0} = 2\hslash \cdot 500 \cdot 10^{6}$~s$^{-1}$ and $D = 2\pi \cdot 10^{4}$~s$^{-1}$.
In Appendix we proved that the two-pulse Broekart-Jeener sequence~\cite{Andrew_1971,Jeener_1967} results in the dipolar ordered state even at the low Zeemann temperature.
The adiabatic demagnetization~\cite{Andrew_1971,Slichter_1961} is the second method of preparing the system in the dipolar ordered state.
Using those methods we can obtain the system in the thermodynamic equilibrium state with the density matrix
%
\begin{equation}
    \label{eq:5}
    \rho_i = \frac{1}{Z_i} e^\frac{\hslash\beta_\mathrm{d}}{k}H_\mathrm{dz}
    \approx \frac{1}{Z_i}(1 + \frac{\hslash\beta_\mathrm{d}}{k} H_\mathrm{dz}),
\end{equation}
%
where the partition function
%
\begin{equation}
    \label{eq:6}
    Z_i = \mathrm{Tr} \left\{ e^\frac{\hslash\beta_\mathrm{d}}{k} H_\mathrm{dz}\right\} \approx 2^{N}.
\end{equation}
%
MQ NMR dynamics in the nanopore will be investigated on the basis of Eq.~(\ref{eq:3}) with the initial state of Eq.~(\ref{eq:6}).
It is also significant that the Hamiltonian $H_{dz}$ is partially averaged by the fast molecular diffusion in in the nanopore and the averaged Hamiltonian can be written as ???
%
\begin{equation}
    \label{eq:7}
    H_\mathrm{dz} = \dfrac{D}{2} (3 I^{2}_{z} - I^{2}) , % ?
\end{equation}
%
where $I^{2}$ is the square of the spin angular momentum.

The averaged over the equilibrium density matrix of Eq.~(\ref{eq:5})the resulting signal $G(\tau,\phi)$ after the preparation, evolution and mixing periods of the MQ NMR experiment~\cite{Baum_1985} can be written as~\cite{Doronin_2019} 
%
\begin{equation}
    \begin{split}
        \label{eq:8}
        G(\tau,\phi) 
        & = \mathrm{Tr}\left\{
            e^{i H_\mathrm{MQ} \tau} e^{i\phi I_\mathrm{z}} e^{-i H_\mathrm{MQ}\tau} 
            \rho_i 
            e^{i H_\mathrm{MQ} \tau} e^{-i \phi I_\mathrm{z}} e^{-i \phi H_\mathrm{MQ} \tau} 
            \rho_i 
        \right\} \\
        & = \mathrm{Tr} \left\{
        e^{i \phi I_\mathrm{z}}
        \rho(\tau) 
        e^{-i \phi I_\mathrm{z}} 
        \rho(\tau) 
        \right\},
    \end{split}
\end{equation}
%
where
%
\begin{equation}
    \label{eq:9}
    \rho(\tau) 
    = e^{-i H_\mathrm{MQ} \tau } 
    \rho_i 
    e^{i H_\mathrm{MQ} \tau}
\end{equation}
%
is the solution of Eq.~(\ref{eq:3}) at the initial condition of Eq.~(\ref{eq:5}).
It is convenient to expand the spin density matrix, $\rho(\tau)$, in series as
%
\begin{equation}
    \label{eq:10}
    \rho(\tau) = \sum\limits_n \rho_n(\tau),
\end{equation}
%
where $\rho_{n}(\tau)$ is the contribution to $\rho(\tau)$ from the MQ coherence of the $n$-th order~\cite{Fel_dman_1996}.
Then the function $G(\tau,\phi)$ of Eq.~(\ref{eq:8}) can be rewritten as 
%
\begin{equation}
    \label{eq:11}
    G(\tau,\phi) 
    = \sum\limits_n e^{i n \phi} \mathrm{Tr} \left\{ 
        \rho_{n}(\tau) \rho_{-n}(\tau) 
    \right\},
\end{equation}
%
where we took into account that
%
\begin{equation}
    \label{eq:12}
    \left[ I_{\mathrm{z}},\rho_n(\tau) \right] = n \rho_n(\tau)
\end{equation}
%
It is necessary for further calculations to introduce the normalized intensities $J_{n}(\tau)$ $(n=0, \pm 2, \pm 4, \cdots)$ of the MQ NMR coherences
%
\begin{equation}
    \label{eq:13}
    J_{n}(\tau) = \dfrac{\mathrm{Tr} \left\{
    \rho_{n}(\tau) \rho_{-n}(\tau) 
    \right\}} 
    {\mathrm{Tr} \left\{\rho^2_{i} \right\}}
\end{equation}
%
Using Eqs.~(\ref{eq:9})~(\ref{eq:10}) one can verity that 
%
\begin{multline}
    \label{eq:14}
    \sum\limits_{n} J_{n}(\tau)
    = \dfrac{
        \mathrm{Tr} \left\{
            \sum_{n} \rho_{n}(\tau) \rho_{-n}(\tau)
        \right\}}
    {\mathrm{Tr} \left\{ \rho^2_{i} \right\}} 
    - \dfrac{
        \mathrm{Tr} \left\{
            \sum_{\mathrm{m,n}} \rho_n(\tau)\rho_m(\tau)
    \right\}}
    {\mathrm{Tr} \left\{\rho^2_{i}\right\}}
    \\
    = \dfrac{
        \mathrm{Tr}\left\{\rho^2(\tau)\right\}
    }
    {
        \mathrm{Tr}\left\{\rho^2_{i}(\tau)\right\}
    }
    = \dfrac{
        \mathrm{Tr} \left\{ 
            e^{-i H_\mathrm{MQ} \tau} 
            \rho^{2}_{i}
            e^{i H_\mathrm{MQ} \tau} 
        \right\}
    }
    {
        \mathrm{Tr} \left\{ \rho_{i}^{2} \right\}
    } 
    = 1
\end{multline}
%
One can conclude from Eq.~(\ref{eq:14}) that the sum of the MQ NMR coherences is conserved on the preparation period of the MQ NMR experiment~\cite{Nielsen_2009}.

The basis consisting of eigenstates of the operator $I_\mathrm{z}$ (so called the multiplicative basis) is widely used for numerical calculations of MQ NMR dynamics~\cite{Zhang_2009}.
Due to the fast expansion of the Hilbert space with the growth of the number of spins such calculations are possible only for systems with a small number of spins.
That approach is not suitable for investigations of many-spin entanglement.
Since the Hamiltonian $H_{MQ}$ of Eq.~(\ref{eq:1}) commutes with the square of the total spin angular momentum $\hat I^2$ 
it is possible to use the basis consisting of the common eigenstates of $\hat I^2$ and $I_\mathrm{z}$ in order to study MQ NMR dynamics as was done in Ref.~\cite{Doronin_2009,Doronin_2011,Doronin_2019}.
In this basis the Hamiltonian $H_{MQ}$ and the initial density matrix of Eq.~(\ref{eq:5}) see also Eq.~(\ref{eq:7}) consist of blocks corresponding to different values of the spin angular momentum~\cite{Doronin_2009}.
Then the investigation of MQ NMR dynamics can be reduced to solving a set of problems of less dimensions.

Since the Hamiltonian $H_{MQ}$ of Eq.~(\ref{eq:1}) commutes with the operator $e^{i\pi I_\mathrm{z}}$, $2^N \times 2^N$ Hamiltonian matrix is reduced to two $2^{N-1} \times 2^{N-1}$ submatrices~\cite{Doronin_2009}.
For odd $N$, both submatrices give the same contribution to the MQ NMR coherences, and one should solve the problem using only one $2^{N-1} \times 2^{N-1}$ submatrix and double the obtained intensities. 
In our calculations we take only odd numbers of spin.
Using this method one can investigate MQ NMR dynamics in systems consisting of hundred spins.

\section{Analytical solution for MQ NMR dynamics for a three-spin system in a nanopore in dipolar ordered state}
\label{sec:3}

\begin{figure}
    \centering
  	\includegraphics[width=0.5\linewidth]{coherences_n3_beta5.eps}
	\caption{
	    Intensities of MQ NRM coherenes $J_{n}$ ($n=0, 2$) in a nanopore with $N=3$.
	}
	\label{fig:1}
\end{figure}

Obtaining the exact solution for MQ NMR dynamics for a three-spin system in the dipolar ordered state in a nanopore is analogously to the case considered in~\cite{Doronin_2019} for the initial thermodynamic equilibrium in a strong external magnetic field. 
We does not use here the high temperature approximation~\cite{Andrew_1971}.

The Hamiltonian $H_{MQ}$ of Eq.~(\ref{eq:1}) consists here of the two blocks for two possible values of spin angular momentum $(I^2 = S(S+1),  \quad S=3/2,1/2)$.
Those blocks, the corresponding eigenvalues and eigenstates are given in~\cite{Doronin_2019}.
The density matrix of the system consists also of the two blocks $\rho^{3/2}(\tau)$, $\rho^{1/2}(\tau)$, and 
%
\begin{equation}
    \label{eq:15} 
    \rho^{3/2}(0) = \dfrac 1 Z
    \begin{pmatrix}
        e^{\frac{3b}{2}} & 0 & 0 & 0 
        \\
        0 & e^{\frac{-3b}{2}} & 0 & 0 
        \\
        0 & 0 & e^{-\frac{-3b}{2}} & 0 
        \\
        0 & 0 & 0 & e^{\frac{3b}{2}}
    \end{pmatrix}, 
    \quad
    \rho^{1/2}(0) = 
    \begin{pmatrix}
        \frac 1 2 & 0 
        \\
        0 & \frac 1 2
    \end{pmatrix}
\end{equation}
%
where $b = \dfrac{\hslash D}{k\mathrm{T}}$and $T$ is the temperature.
After simple calculations one can obtain the density matrices $\rho^{3/2}(\tau)$ and $\rho^{1/2}(\tau)$ 
which allow us to find intensities of the MQ NMR coherences.

Only the MQ NMR coherences of the zeroth and plus/minus second orders appear in the considered systems. 
The intensities of these coherences are
%
\begin{equation}
    \begin{split}
        \label{eq:16}
        J_0(\tau) & = 1 
        - \tanh^2\left( \dfrac{3b}{2} \right)
            \sin^2 \left( \sqrt{3} Dt \right), 
        \\
        J_{\pm2}(\tau) & = \dfrac{1}{4} 
            \tanh^2 \left( \dfrac{3b}{2} \right)
            \sin^2 \left( \sqrt{3} Dt \right)
    \end{split}
\end{equation}
%
The sum of intensities of Eq.~(\ref{eq:16}) equals one in accordance with Eq.~(\ref{eq:14}).
The dependencies of the calculated intensities $J_{n}(\tau)$ $(n=0,2)$ on the evolution time are shown in Fig.~(\ref{fig:1}).

\section{Second moment of the MQ NMR spectrum as a measure of may-spin entanglement}
\label{sec:4}

The expression~(\ref{eq:8}) for the MQ NMR signal $G(\tau,\phi)$ can be expended in series over the phase increment $\phi$:
%
\begin{equation}
    \begin{split}
        \label{eq:17}
        G(\tau,\phi)  
        & = \mathrm{Tr} \left\{ 
            \rho(\tau) e^{i \phi I_\mathrm{z} }
            \rho(\tau) e^{-i\phi I_\mathrm{z}}
        \right\}  \\
        & = \mathrm{Tr} \left\{ \rho^2(\tau) \right\} 
        - \phi^2 \mathrm{Tr} \left\{ 
            \rho^2(\tau) I^2_\mathrm{z} 
            - (\rho(\tau) I_\mathrm{z})^2
        \right\} 
        + O(\phi^3)
    \end{split}
\end{equation}
%
It is possible to prove~\cite{Girolami_2017} that the quantum Fisher information $F_\mathrm{Q}(\rho,I_\mathrm{z})$~\cite{Helstrom_1969}
%
\begin{equation}
    \label{eq:18}
    F_\mathrm{Q}(\rho,I_\mathrm{z}) \geq 4 \mathrm{Tr} \left\{ \rho^2 I^2_\mathrm{z} - (\rho I_\mathrm{z})^2 \right\}
\end{equation}
%
At the same time, it is easily to verify that $2 \mathrm{Tr} \left\{ \rho^2(\tau) I_\mathrm{z}^2 - \left( \rho(\tau) I_\mathrm{z} \right)^2 \right\}$ equals to the second moment $M_2$ of the distribution of intensities of the MQ NMR coherences~\cite{Khitrin_1997}
%
\begin{equation}
    \label{eq:19}
    M_2 = \sum_{n} n^2 J_n (\tau) ,
\end{equation}
%
where $J_n(\tau)$ ($n=0,\pm 2, \pm 4, \cdots$) is determined by Eq.~(\ref{eq:13}).
Thus, the second moment of the MQ NMR spectrum provides a low bound on the quantum Fisher information $F_\mathrm{Q}(\rho,I_\mathrm{z})$
It was also shown~\cite{T_th_2014,Pezz__2018} that if
%
\begin{equation}
    \label{eq:20}
    F_\mathrm{Q} (\rho,I_\mathrm{z}) > n k^2 + (N - n k)^2
\end{equation}
%
Where $n$ is the integer part of {N/k}, then the system with the density matrix $\rho(\tau)$ is $k+1$-spin entangled~\cite{Pezz__2009,Hyllus_2012,T_th_2012}.
The results of the numerical analysis of the many-spin entanglement in the system of spin-carrying molecules (atoms) initially prepared in the dipolar ordered state are presented in the following section.

\section{Numerical analysis of many-spin entanglement a different temperatures and the numbers of spins in the system}
\label{sec:5}

\begin{figure}
  	\includegraphics[width=0.95\linewidth]{fisher_low_bound_n101.eps}
	\caption{
	    The dependence of the low bound of thequantum Fisher Information $F_\mathrm{Q} = 2 M_{2}$ 
	    on the dimensionless time $D\tau$ at $N=101$, 
	    a) $T=6\cdot10^{-4}$~K, the inequality~(\ref{eq:20}) yields the region of pair entanglement (k+1=2), the region is above the horizontal line; 
	    b) $T=3.2\cdot10^{-4}$~K, the region of the many-spin entanglement is a strip bounded by the horizontal lines with~$k=32$~and~$k=46$; 
	    c) $T = 1.6\cdot10^{_4}$~K, the horizontal lines ($k=47$ and k=$86$) bound the strip with many spin enatnglement;
	    d) $T=4.8\cdot10^{-5}$~K, entangled clusters with $47-92$ spins emerge.
	}
	\label{fig:2}
\end{figure}

The considered model of the spin-carrying molecules (atoms) in a nanopore in the dipolar ordered states expends possibilities of an investigation of many-spin entanglement in comparison to the analogous model~\cite{Doronin_2019}
when the system was initially in the thermodynamic equilibrium in a strong external magnetic field.
The model~\cite{Doronin_2019}  is restricted for investigation of the time evolution of the system
because the stationary distribution of MQ NMR coherences establishes very quickly~\cite{Doronin_2009}.
The temperature dependence of many-spin entanglement occurs in the model~\cite{Doronin_2019} in a very narrow temperature interval.
For example, all spins are entangled in the system consisting of 201 spins at temperature $T=6.856\cdot10^{-3}$~K~\cite{Doronin_2019}.

The time dependence of the quantum Fisher information in the system consisting of 101 spins is presented in Fig.~(\ref{fig:2}) at different temperatures. 
One can see from Fig.~(\ref{fig:2}a) that the pair entanglement exists only at temperature $T=6\cdot10^{-4}$~K.
At the temperature $T=3.2\cdot10^{-4}$ one can see a strip Fig.~(\ref{fig:2}b), in which the inequality~(\ref{eq:20}) can be satisfied when ${32}\leq {k}\leq{46}$.
Thus, there is many-spin entanglement in spin clusters consisting of 33-47 spins at temperature $3.2\cdot10^{-4}$~K.
When the temperature decreases, the width of the strip, in which many-spin entanglement exists, increases. 
At temperature $T=1.6\cdot10^{-4}$~K (Fig.~(\ref{fig:2}c)) clusters of 48-87 entangled spins emerge, and at temperature $T=4.8\cdot10^{-5}$~K (Fig.~(\ref{fig:2}d)) we have 47-92 entangled spins.

\begin{figure}
  	\includegraphics[width=0.95\linewidth]{entangled_spins_by_n.eps}
	\caption{
	    The dependence of the maximal number of the entangled spins,
	    averaged over the evolution time $(0 \leq D\tau \leq 3)$, 
	    on the temperature at $N=51, 75, 101$.
	}
	\label{fig:3}
\end{figure}

The dependence of the maximal number of the entangled spins averaged over the evolution time $({0}\leq \mathrm{D}\tau\leq{3})$, on the temperature at different numbers of spins in a nanopore is presented in Fig.~(\ref{fig:3}).
The maximal number of entangled spins decreases when the temperature increases. 
The maximal number of entangled spins increases when the number of spins in the nanopore increases also, because the system in the nanopore gets more dense.

\section{Conclusion}
\label{sec:6}

We investigated many-spin entanglement in the system of spin-carrying molecules (atoms) filled in the non-spherical nanopore, initially prepared in the dipolar ordered state, in the conditions of the MQ NMR spectroscopy .
The dependence of many-spin entanglement on the temperature and the number of spins in the nanopore were investigated.

We believe that the MQ NMR spectroscopy is a subtle and useful method for investigations of different quantum information problems.
In particularly, it is a very effective method for exploration of quantum entanglement.

\section{Acknowledgements}
This work was performed as a part of a state task, State Registration No. 0089-2019-0002. This work was partially supported by the Russian Foundation for Basic Research (Grants Nos. 20-03-00147, 19-32-80004) I.L Acknowledge support from the Advancement of Theoretical Physics and Mathematics BASIS No. 19-1-5-130-1.

\appendix
\section{The two-pulse Broekart-Jeener experiment at the low Zeemann and high dipolar temperatures.}

Initially the system is in the thermodynamic equilibrium state in the striong external magnetic field with the density matrix
%
\begin{equation}
    \label{eq:a1}
   \sigma_{i} = \dfrac{e^{\beta_\mathrm{d} \omega_{0} I_\mathrm{z}}}{Z_{i}} ,
   \quad
   Z_{i} = \mathrm{Tr}\left\{e^{\beta_\mathrm{d} \omega_{0} I_\mathrm{z}} \right\}
\end{equation}
%
After the first resonance rf x-pulse one has
%
\begin{equation}
    \label{eq:a2}
    \sigma'(0) = e^{ i \frac \pi 2 I_\mathrm{x}}
    \sigma_{i}
    e^{-i \frac \pi 2 I_\mathrm{x}}
    = \dfrac{e^{\beta_\mathrm{d} \omega_{0} I_\mathrm{y}}}{Z_{i}}  .
\end{equation}
%
Then the system evolves freely time $\tau$ 
and one applies the second resonance y-pulse rotation spins by angle $\theta$ around the y-axis of the RRF.
As a result, one obtains that
\begin{equation}
    \label{eq:a3}
    \sigma'(\tau) 
    = \dfrac{
      e^{-i \theta I_\mathrm{y}} e^{-i H_\mathrm{dz} \tau} 
      e^{\beta_\mathrm{d} \omega_{0} I_\mathrm{y}}
      e^{i H_\mathrm{dz} \tau} e^{i \theta I_\mathrm{y}}
    }{Z_{i}}. 
\end{equation}
%
After time $T_2$ ($T_2$ is the spin relaxation time \cite{Andrew_1971}) the system achieves the thermodynamic equilibrium state
\begin{equation}
    \label{eq:a4}
    \sigma_{f} 
    = \dfrac{ e^{\alpha \omega_{0} I_\mathrm{z} + \beta H_\mathrm{dz}} }{Z_f},
\end{equation}
%
where $\alpha$ and $\beta$ are the inverse Zeeman and dipolar temperature.
It is evident that the system has the single equilibrium state 
and the temperatures $\alpha$ and $\beta$ are also single.
Those temperatures can be obtained from the conservation laws
\begin{align}
    \label{eq:a5}
    \mathrm{Tr} \left\{ I_\mathrm{z} \sigma'(\tau) \right\}
    & = \mathrm{Tr} \left\{ I_\mathrm{z} \sigma_{f}(\tau) \right\}
    \\
    \label{eq:a6}
    \mathrm{Tr} \left\{ H_\mathrm{dz} \sigma'(\tau) \right\}
    & = \mathrm{Tr} \left\{ H_\mathrm{dz} \sigma_{f}(\tau) \right\}
\end{align}
%
One can rewrite $\mathrm{Tr} \left\{ I_\mathrm{z} \sigma'(\tau) \right\}$ as 
%
\begin{multline}
    \label{eq:a7} 
    \tr{I_\mathrm{z} \sigma'(\tau)}
    =  \dfrac{1}{Z_{i}} \tr{
        e^{i \theta \sy} \sz e^{-i \theta \sy}
        e^{-i \hdz \tau} e^{\beta_\mathrm{d} \omega_{0} \sy} e^{i \hdz \tau}
    } 
    \\
    = \dfrac{1}{Z_i} \tr{
        \left( \cos(\theta) \sz - \sin(\theta) \sx \right) 
        e^{-i \hdz \tau} e^{\beta_\mathrm{d} \omega_{0} \sy} e^{i \hdz \tau}
    }
    \\
    = \dfrac{1}{Z_i} \tr{
        e^{-i \pi \sy}  
        \left( \cos(\theta) \sz - \sin(\theta) \sx \right) 
        e^{-i \hdz \tau} e^{\beta_\mathrm{d} \omega_{0} \sy} e^{i \hdz \tau}
        e^{i \pi \sy}  
    }
    \\
    = - \dfrac{1}{Z_i} \tr{
        \left( \cos(\theta) \sz - \sin(\theta) \sx \right) 
        e^{-i \hdz \tau} e^{\beta_\mathrm{d} \omega_{0} \sy} e^{i \hdz \tau} 
    } = 0
\end{multline}
%
In~(\ref{eq:a7} we took into account that $\left[ e^{-i \pi \sy}, \hdz \right] = 0$.
Since we consider the case of a high dipolar temperature it is possible for rewrite~(\ref{eq:a5}) as
\begin{equation}
    \label{eq:a8}
    0 = \dfrac{1}{Z_i} \tr{ \sz e^{\alpha \omega_0 \sz}}
    + \dfrac{\beta}{Z_i} \tr{\sz e^{\alpha \omega_0 \hdz}}.
\end{equation}
%
Notice that $\tr{\sz} = \tr{\sz\hdz} = 0$. It mean that $\alpha = 0$ satisfies Eq.~(\ref{eq:5}). 
Thus we obtain the dipolar ordered state in the considered case.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{bibliography}
\end{document}

### 2020-05-12 manuscript.tex
Fix text and equations

@@
 \begin{keyword}
-? \sep ?
+multiple quantum (MQ) NMR \sep  
+quantum correlations \sep 
+quantum Fisher information \sep 
+entanglement, nano-pore \sep 
+MQ NMR coherence \sep 
+second moment, temperature \sep 
+dipolar ordered state \sep 
+two-pulse Broekart-Jeener sequence
 \end{keyword}
@@
 
-Entanglement~\cite{Nielsen_2009} is a very important quantum conception, which is responsible in particular, for advantages of quantum computers our their classical counterparts.
-Recently demonstrated quantum supremacy using a programmable superconducting processor~\cite{Arute2019} is also connected with entanglement which is absent in classical Physicsa.
-Among numerous methods of an investigation of entanglement we concentrate on multiple quantum (MQ) NMR in solids~\cite{Baum_1985}, which was widely used characterize entanglement in binary system~\cite{Furman_2008,Furman_2009,Fel_dman_2008,Fel_dman_2012}.
-It turned out that the MQ NMR spectroscopy~\cite{Nielsen_2009} allows us to extract also information about many spin entanglement~\cite{?}, 
+Entanglement~\cite{Nielsen_2009} is a very important quantum conception, which is responsible in particular, for advantages of quantum computers over their classical counterparts.
+Recently demonstrated quantum supremacy using a programmable superconducting processor~\cite{Arute2019} is also connected with entanglement which is absent in classical physics.
+Among numerous methods of an investigation of entanglement we concentrate on multiple quantum (MQ) NMR in solids~\cite{Baum_1985}, which was widely used to characterize entanglement in binary system~\cite{Furman_2008,Furman_2009,Fel_dman_2008,Fel_dman_2012}.
+It turned out that the MQ NMR spectroscopy~\cite{Baum_1985} allows us to extract also information about many spin entanglement~\cite{G_rttner_2018}, 
 if one attracts for the analysis the quantum Fisher information~\cite{T_th_2014,Pezz__2018}.
@@
 In MQ NMR spectroscopy that parameter is the phase increment between the radio-frequency (rf) pulses irradiating the system on preparation and mixing periods of the MQ NMR experiment~\cite{Baum_1985} in proportional to the evolution time.
-That procedure leads to a separation of the signals.
-Corresponding to the MQ NMR coherences of different orders, and obtaining the total MQ NM spectrum.
+That procedure leads to a separation of the signals,
+corresponding to the MQ NMR coherences of different orders, and obtaining the total MQ NMR spectrum.
 Using the quantum Fisher information (QFI)~\cite{Liu_2014} for an analysis of the MQ NMR spectra one can extract very important information about many-spin entanglement.
@@
 
-Many-spin entanglement was investigated~\cite{Doronin_2019} on a non spherical nanopore filled with a gas of spin-carrying molecules in a strong external magnetic field~\cite{Baugh_2001,Doronin_2009}.
+Many-spin entanglement was investigated~\cite{Doronin_2019} on a nonspherical nanopore filled with a gas of spin-carrying molecules in a strong external magnetic field~\cite{Baugh_2001,Doronin_2009}.
 The thermal equilibrium initial state of the system was determined by the one-spin Zeemann interaction with the external magnetic field~\cite{Doronin_2007a}.
-It is also possible to investigate many-spin entanglement when the same system is initially prepared in the dipolar ordered state~\cite{Andrew_1971} using either the adiabatic demagnetization method in a rotating reference frame (RRF)~\cite{Andrew_1971,Slichter_1961} or the two-pulse Broekart-Jeener sequence~\cite{Andrew_1971,Jeener_1967}.
+It is also possible to investigate many-spin entanglement when the same system is initially prepared in the dipolar ordered state~\cite{Goldman_1970} using either the adiabatic demagnetization method in a rotating reference frame (RRF)~\cite{Goldman_1970,Slichter_1961} or the two-pulse Broekart-Jeener sequence~\cite{Goldman_1970,Jeener_1967}.
 The MQ NMR dynamics with this initial state have been simulated both in small spin-systems~\cite{Doronin_2007a,Doronin_2007b} and in the system consisting of 200-600 spin-carrying molecules (atoms) filled in a nanopore~\cite{Doronin_2011}.
@@
 The second moment of the MQ NMR spectrum as a measure of many-spin entanglement is considered in Sec.~\ref{sec:4}.
-The dependence of many-spin entanglement on the dipolar temperature and the number of spin in the system is investigated in Sec.~\ref{sec:5}.
+The dependence of many-spin entanglement on the dipolar temperature and the number of spins in the system is investigated in Sec.~\ref{sec:5}.
 We briefly summarize our results in the concluding Sec.~\ref{sec:6}.
@@
 %
-$N$ is the number of the spins in the nanopore $I^{\pm}_{j}$, are the raising or lowering operators of spin $j$, and $D$ is the dipolar coupling constant averaged by the fast molecular diffusion of spin-carrying atoms (molecules) in nanopores.
+$N$ is the number of the spins in the nanopore, $I^{\pm}_{j}$ are the raising or lowering operators of spin $j$, and $D$ is the dipolar coupling constant averaged by the fast molecular diffusion of spin-carrying atoms (molecules) in nanopores.
 We underline that the dipolar coupling constant $D$ is the same for all pairs at interacting spins in the nanopore~\cite{Doronin_2019,Doronin_2009}.
-The density matrix $\rho(\tau)$ on the preparation period of the MQ NMR experiment~\cite{Baum_1985} can be obtained from the Liouville evolution equation~\cite{Andrew_1971,Abragam_1982} 
+The density matrix $\rho(\tau)$ on the preparation period of the MQ NMR experiment~\cite{Baum_1985} can be obtained from the Liouville evolution equation~\cite{Goldman_1970,Abragam_1982} 
 %
@@
 which is directed along the strong external magnetic field,  
-$H_\mathrm{dz}$ is the secular part of the dipole-dipole interaction~\cite{?}.
+$H_\mathrm{dz}$ is the secular part of the dipole-dipole interaction~(DDI).
 Hamiltonian in a strong external magnetic field, and $\alpha_\mathrm{z}$, $\beta_\mathrm{d}$ are the inverse Zeemann and dipolar temperatures. 
@@
 and the dipolar temperature is high $\left( \frac{\hslash{D}}{k}\beta_\mathrm{d} \ll 1\right)$.
-For concreteness we suppose that $\omega_{0} = 2\hslash \cdot 500 \cdot 10^{6}$~s$^{-1}$ and $D = 2\pi \cdot 10^{4}$~s$^{-1}$.
-In Appendix we proved that the two-pulse Broekart-Jeener sequence~\cite{Andrew_1971,Jeener_1967} results in the dipolar ordered state even at the low Zeemann temperature.
-The adiabatic demagnetization~\cite{Andrew_1971,Slichter_1961} is the second method of preparing the system in the dipolar ordered state.
+For concreteness we suppose that $\omega_{0} = 2\pi \cdot 500 \cdot 10^{6}$~s$^{-1}$ and $D = 2\pi \cdot 10^{4}$~s$^{-1}$.
+In Appendix we proved that the two-pulse Broekart-Jeener sequence~\cite{Goldman_1970,Jeener_1967} results in the dipolar ordered state even at the low Zeemann temperature.
+The adiabatic demagnetization~\cite{Goldman_1970,Slichter_1961} is the second method of preparing the system in the dipolar ordered state.
 Using those methods we can obtain the system in the thermodynamic equilibrium state with the density matrix
@@
 %
-MQ NMR dynamics in the nanopore will be investigated on the basis of Eq.~(\ref{eq:3}) with the initial state of Eq.~(\ref{eq:6}).
-It is also significant that the Hamiltonian $H_{dz}$ is partially averaged by the fast molecular diffusion in in the nanopore and the averaged Hamiltonian can be written as ???
+MQ NMR dynamics in the nanopore will be investigated on the basis of Eq.~(\ref{eq:3}) with the initial state of Eq.~(\ref{eq:5}).
+It is also significant that the Hamiltonian $H_{dz}$ is partially averaged by the fast molecular diffusion in the nanopore and the averaged Hamiltonian can be written as \cite{Fel_dman_2004,Doronin_2011}
 %
@@
     {\mathrm{Tr} \left\{ \rho^2_{i} \right\}} 
-    - \dfrac{
+    = \dfrac{
         \mathrm{Tr} \left\{
@@
 %
-One can conclude from Eq.~(\ref{eq:14}) that the sum of the MQ NMR coherences is conserved on the preparation period of the MQ NMR experiment~\cite{Nielsen_2009}.
+One can conclude from Eq.~(\ref{eq:14}) that the sum of the MQ NMR coherences is conserved on the preparation period of the MQ NMR experiment~\cite{Baum_1985}.
 
@@
 it is possible to use the basis consisting of the common eigenstates of $\hat I^2$ and $I_\mathrm{z}$ in order to study MQ NMR dynamics as was done in Ref.~\cite{Doronin_2009,Doronin_2011,Doronin_2019}.
-In this basis the Hamiltonian $H_{MQ}$ and the initial density matrix of Eq.~(\ref{eq:5}) see also Eq.~(\ref{eq:7}) consist of blocks corresponding to different values of the spin angular momentum~\cite{Doronin_2009}.
+In this basis the Hamiltonian $H_{MQ}$ and the initial density matrix of Eq.~(\ref{eq:5}) (see also Eq.~(\ref{eq:7})) consist of blocks corresponding to different values of the spin angular momentum~\cite{Doronin_2009}.
 Then the investigation of MQ NMR dynamics can be reduced to solving a set of problems of less dimensions.
@@
 Obtaining the exact solution for MQ NMR dynamics for a three-spin system in the dipolar ordered state in a nanopore is analogously to the case considered in~\cite{Doronin_2019} for the initial thermodynamic equilibrium in a strong external magnetic field.
-We does not use here the high temperature approximation~\cite{Andrew_1971}.
+We does not use here the high temperature approximation~\cite{Goldman_1970}.
 
@@
         J_0(\tau) & = 1 
-        - \tanh^2\left( \dfrac{3b}{2} \right)
+        - \dfrac 1 2 \tanh^2\left( \dfrac{3b}{2} \right)
             \sin^2 \left( \sqrt{3} Dt \right), 
@@
 
-\section{Second moment of the MQ NMR spectrum as a measure of may-spin entanglement}
+\section{Second moment of the MQ NMR spectrum as a measure of many-spin entanglement}
 \label{sec:4}
@@
     \label{eq:20}
-    F_\mathrm{Q} (\rho,I_\mathrm{z}) > n k^2 + (N - n k)^2
+    F_\mathrm{Q} (\rho,I_\mathrm{z}) > n k^2 + (N - n k)^2,
 \end{equation}
 %
-Where $n$ is the integer part of {N/k}, then the system with the density matrix $\rho(\tau)$ is $k+1$-spin entangled~\cite{Pezz__2009,Hyllus_2012,T_th_2012}.
-The results of the numerical analysis of the many-spin entanglement in the system of spin-carrying molecules (atoms) initially prepared in the dipolar ordered state are presented in the following section.
+where $n$ is the integer part of {N/k}, then the system with the density matrix $\rho(\tau)$ is $k+1$-spin entangled~\cite{Pezz__2009,Hyllus_2012,T_th_2012}.
+The results of the numerical analysis of many-spin entanglement in the system of spin-carrying molecules (atoms) initially prepared in the dipolar ordered state are presented in the following section.
 
-\section{Numerical analysis of many-spin entanglement a different temperatures and the numbers of spins in the system}
+\section{Numerical analysis of many-spin entanglement at different temperatures and the numbers of spins in the system}
 \label{sec:5}
@@
 	\caption{
-	    The dependence of the low bound of thequantum Fisher Information $F_\mathrm{Q} = 2 M_{2}$ 
+	    The dependence of the low bound of the quantum Fisher Information $F_\mathrm{Q} = 2 M_{2}$ 
 	    on the dimensionless time $D\tau$ at $N=101$, 
@@
 
-The considered model of the spin-carrying molecules (atoms) in a nanopore in the dipolar ordered states expends possibilities of an investigation of many-spin entanglement in comparison to the analogous model~\cite{Doronin_2019}
+The considered model of the spin-carrying molecules (atoms) in a nanopore in the dipolar ordered states expands possibilities of an investigation of many-spin entanglement in comparison to the analogous model~\cite{Doronin_2019}
 when the system was initially in the thermodynamic equilibrium in a strong external magnetic field.
@@
 The time dependence of the quantum Fisher information in the system consisting of 101 spins is presented in Fig.~(\ref{fig:2}) at different temperatures. 
-One can see from Fig.~(\ref{fig:2}a) that the pair entanglement exists only at temperature $T=6\cdot10^{-4}$~K.
+One can see from Fig.~(\ref{fig:2}a) that the only pair entanglement exists at temperature $T=6\cdot10^{-4}$~K.
 At the temperature $T=3.2\cdot10^{-4}$ one can see a strip Fig.~(\ref{fig:2}b), in which the inequality~(\ref{eq:20}) can be satisfied when ${32}\leq {k}\leq{46}$.
@@
 	    averaged over the evolution time $(0 \leq D\tau \leq 3)$, 
-	    on the temperature at $N=51, 75, 101$.
+	    on the temperature at a) $N=51$; b) $N=75$; c) $N=101$.
 	}
@@
 \section{Acknowledgements}
-This work was performed as a part of a state task, State Registration No.
-0089-2019-0002.
-This work was partially supported by the Russian Foundation for Basic Research (Grants Nos.
-20-03-00147, 19-32-80004) I.L Acknowledge support from the Advancement of Theoretical Physics and Mathematics BASIS No.
-19-1-5-130-1.
+This work was performed as a part of a state task, State Registration No. 0089-2019-0002. 
+This work was partially supported by the Russian Foundation for Basic Research (Grants Nos. 20-03-00147, 19-32-80004). 
+I.L. Acknowledge support from the Advancement of Theoretical Physics and Mathematics BASIS No. 19-1-5-130-1.
 
@@
 
-Initially the system is in the thermodynamic equilibrium state in the striong external magnetic field with the density matrix
+Initially the system is in the thermodynamic equilibrium state in the strong external magnetic field with the density matrix
 %
@@
 Then the system evolves freely time $\tau$ 
-and one applies the second resonance y-pulse rotation spins by angle $\theta$ around the y-axis of the RRF.
+and one applies the second resonance y-pulse ratating spins by angle $\theta$ around the y-axis of the RRF.
 As a result, one obtains that
@@
 %
-After time $T_2$ ($T_2$ is the spin relaxation time \cite{Andrew_1971}) the system achieves the thermodynamic equilibrium state
+After time $T_2$ ($T_2$ is the spin relaxation time \cite{Goldman_1970}) the system achieves the thermodynamic equilibrium state
 \begin{equation}
@@
 %
-where $\alpha$ and $\beta$ are the inverse Zeeman and dipolar temperature.
+where $\alpha$ and $\beta$ are the inverse Zeeman and dipolar temperatures.
 It is evident that the system has the single equilibrium state 
@@
         e^{i \theta \sy} \sz e^{-i \theta \sy}
-        e^{-i \hdz \tau} e^{\beta_\mathrm{d} \omega_{0} \sy} e^{i \hdz \tau}
+        e^{-i \hdz \tau} e^{\beta_\mathrm{L} \omega_{0} \sy} e^{i \hdz \tau}
     } 
@@
         \left( \cos(\theta) \sz - \sin(\theta) \sx \right) 
-        e^{-i \hdz \tau} e^{\beta_\mathrm{d} \omega_{0} \sy} e^{i \hdz \tau}
+        e^{-i \hdz \tau} e^{\beta_\mathrm{L} \omega_{0} \sy} e^{i \hdz \tau}
     }
@@
         \left( \cos(\theta) \sz - \sin(\theta) \sx \right) 
-        e^{-i \hdz \tau} e^{\beta_\mathrm{d} \omega_{0} \sy} e^{i \hdz \tau}
+        e^{-i \hdz \tau} e^{\beta_\mathrm{L} \omega_{0} \sy} e^{i \hdz \tau}
         e^{i \pi \sy}  
@@
         \left( \cos(\theta) \sz - \sin(\theta) \sx \right) 
-        e^{-i \hdz \tau} e^{\beta_\mathrm{d} \omega_{0} \sy} e^{i \hdz \tau} 
+        e^{-i \hdz \tau} e^{\beta_\mathrm{L} \omega_{0} \sy} e^{i \hdz \tau} 
     } = 0
@@
     \label{eq:a8}
-    0 = \dfrac{1}{Z_i} \tr{ \sz e^{\alpha \omega_0 \sz}}
-    + \dfrac{\beta}{Z_i} \tr{\sz e^{\alpha \omega_0 \hdz}}.
+    0 = \dfrac{1}{Z_f} \tr{ \sz e^{\alpha \omega_0 \sz}}
+    + \dfrac{\beta}{Z_f} \tr{\sz e^{\alpha \omega_0 \sz} \hdz}.
 \end{equation}
 %
-Notice that $\tr{\sz} = \tr{\sz\hdz} = 0$. It mean that $\alpha = 0$ satisfies Eq.~(\ref{eq:5}). 
+Notice that $\tr{\sz} = \tr{\sz\hdz} = 0$. It means that $\alpha = 0$ satisfies Eq.~(\ref{eq:5}). 
 Thus we obtain the dipolar ordered state in the considered case.

### 2020-05-14 manuscript.tex
Fix bugs: references, indexes, typos

@@
 than in the MQ NMR experiment with the thermal equilibrium initial state in a strong external magnetic field.
-It is important for many-spin entanglement investigations, because they are connected with calculations of the second moment of the distribution at MQ NMR coherences. 
+It is important for many-spin entanglement investigations, because they are connected with calculations of the second moment of the distribution of MQ NMR coherences. 
 It is also very important for an investigation of the spreading correlation~\cite{Baugh_2001,Baum_1986,S_nchez_2014,Munowitz_1987} and localization effects~\cite{Alvarez_2015,Wei_2018}.
@@
 which is directed along the strong external magnetic field,  
-$H_\mathrm{dz}$ is the secular part of the dipole-dipole interaction~(DDI).
-Hamiltonian in a strong external magnetic field, and $\alpha_\mathrm{z}$, $\beta_\mathrm{d}$ are the inverse Zeemann and dipolar temperatures. 
+$H_\mathrm{dz}$ is the secular part of the dipole-dipole interaction~(DDI) Hamiltonian in a strong external magnetic field, and $\alpha_\mathrm{z}$, $\beta_\mathrm{d}$ are the inverse Zeemann and dipolar temperatures.
 We will consider the case when the Zeemann temperature is low $({\frac{\hslash \omega}{k} \alpha_\mathrm{z}}\gg 1)$ 
@@
 
-The expression~(\ref{eq:8}) for the MQ NMR signal $G(\tau,\phi)$ can be expended in series over the phase increment $\phi$:
+The expression~(\ref{eq:8}) for the MQ NMR signal $G(\tau,\phi)$ can be expanded in series over the phase increment $\phi$:
 %
@@
 The time dependence of the quantum Fisher information in the system consisting of 101 spins is presented in Fig.~(\ref{fig:2}) at different temperatures. 
-One can see from Fig.~(\ref{fig:2}a) that the only pair entanglement exists at temperature $T=6\cdot10^{-4}$~K.
+One can see from Fig.~(\ref{fig:2}a) that only the pair entanglement exists at temperature $T=6\cdot10^{-4}$~K.
 At the temperature $T=3.2\cdot10^{-4}$ one can see a strip Fig.~(\ref{fig:2}b), in which the inequality~(\ref{eq:20}) can be satisfied when ${32}\leq {k}\leq{46}$.
@@
 This work was partially supported by the Russian Foundation for Basic Research (Grants Nos. 20-03-00147, 19-32-80004). 
-I.L. Acknowledge support from the Advancement of Theoretical Physics and Mathematics BASIS No. 19-1-5-130-1.
+I.L. acknowledges support from the Advancement of Theoretical Physics and Mathematics BASIS No. 19-1-5-130-1.
 
@@
     \label{eq:a1}
-   \sigma_{i} = \dfrac{e^{\beta_\mathrm{d} \omega_{0} I_\mathrm{z}}}{Z_{i}} ,
+   \sigma_{i} = \dfrac{e^{\beta_\mathrm{L} \omega_{0} I_\mathrm{z}}}{Z_{i}} ,
    \quad
-   Z_{i} = \mathrm{Tr}\left\{e^{\beta_\mathrm{d} \omega_{0} I_\mathrm{z}} \right\}
+   Z_{i} = \mathrm{Tr}\left\{e^{\beta_\mathrm{L} \omega_{0} I_\mathrm{z}} \right\}
 \end{equation}
@@
     e^{-i \frac \pi 2 I_\mathrm{x}}
-    = \dfrac{e^{\beta_\mathrm{d} \omega_{0} I_\mathrm{y}}}{Z_{i}}  .
+    = \dfrac{e^{\beta_\mathrm{L} \omega_{0} I_\mathrm{y}}}{Z_{i}}  .
 \end{equation}
@@
 Then the system evolves freely time $\tau$ 
-and one applies the second resonance y-pulse ratating spins by angle $\theta$ around the y-axis of the RRF.
+and one applies the second resonance y-pulse rotating spins by angle $\theta$ around the y-axis of the RRF.
 As a result, one obtains that
@@
       e^{-i \theta I_\mathrm{y}} e^{-i H_\mathrm{dz} \tau} 
-      e^{\beta_\mathrm{d} \omega_{0} I_\mathrm{y}}
+      e^{\beta_\mathrm{L} \omega_{0} I_\mathrm{y}}
       e^{i H_\mathrm{dz} \tau} e^{i \theta I_\mathrm{y}}

### 2020-05-15 manuscript.tex
Fix bugs: eq15, Helstrom year, Broekaert

@@
 dipolar ordered state \sep 
-two-pulse Broekart-Jeener sequence
+two-pulse Broekaert-Jeener sequence
 \end{keyword}
@@
 Recently demonstrated quantum supremacy using a programmable superconducting processor~\cite{Arute2019} is also connected with entanglement which is absent in classical physics.
-Among numerous methods of an investigation of entanglement we concentrate on multiple quantum (MQ) NMR in solids~\cite{Baum_1985}, which was widely used to characterize entanglement in binary system~\cite{Furman_2008,Furman_2009,Fel_dman_2008,Fel_dman_2012}.
-It turned out that the MQ NMR spectroscopy~\cite{Baum_1985} allows us to extract also information about many spin entanglement~\cite{G_rttner_2018}, 
+Among numerous methods of an investigation of entanglement we concentrate on multiple quantum (MQ) NMR in solids~\cite{Baum_1985}, which was widely used to characterize entanglement in binary systems~\cite{Furman_2008,Furman_2009,Fel_dman_2008,Fel_dman_2012}.
+It turned out that the MQ NMR spectroscopy~\cite{Baum_1985} allows us to extract also information about many-spin entanglement~\cite{G_rttner_2018}, 
 if one attracts for the analysis the quantum Fisher information~\cite{T_th_2014,Pezz__2018}.
@@
 The thermal equilibrium initial state of the system was determined by the one-spin Zeemann interaction with the external magnetic field~\cite{Doronin_2007a}.
-It is also possible to investigate many-spin entanglement when the same system is initially prepared in the dipolar ordered state~\cite{Goldman_1970} using either the adiabatic demagnetization method in a rotating reference frame (RRF)~\cite{Goldman_1970,Slichter_1961} or the two-pulse Broekart-Jeener sequence~\cite{Goldman_1970,Jeener_1967}.
+It is also possible to investigate many-spin entanglement when the same system is initially prepared in the dipolar ordered state~\cite{Goldman_1970} using either the adiabatic demagnetization method in a rotating reference frame (RRF)~\cite{Goldman_1970,Slichter_1961} or the two-pulse Broekaert-Jeener sequence~\cite{Goldman_1970,Jeener_1967}.
 The MQ NMR dynamics with this initial state have been simulated both in small spin-systems~\cite{Doronin_2007a,Doronin_2007b} and in the system consisting of 200-600 spin-carrying molecules (atoms) filled in a nanopore~\cite{Doronin_2011}.
@@
 Nuclear magnetic ordering~\cite{Abragam_1982} is outside our consideration.
-Notice also that the two-pulse Broekart-Jeneer experiment~\cite{Jeener_1967} was performed in the high temperature case.
+Notice also that the two-pulse Broekaert-Jeneer experiment~\cite{Jeener_1967} was performed in the high temperature case.
 We prove theoretically that the experiment~\cite{Jeener_1967} can be realized also for the intermediate temperature case of the article. 
@@
 We briefly summarize our results in the concluding Sec.~\ref{sec:6}.
-In Appendix we show that the two-pulse Broekart-Jeener sequence can be used in the case when the Zeemann temperature is low and the dipole one is high.
+In Appendix we show that the two-pulse Broekaert-Jeener sequence can be used in the case when the Zeemann temperature is low and the dipole one is high.
 
@@
 $N$ is the number of the spins in the nanopore, $I^{\pm}_{j}$ are the raising or lowering operators of spin $j$, and $D$ is the dipolar coupling constant averaged by the fast molecular diffusion of spin-carrying atoms (molecules) in nanopores.
-We underline that the dipolar coupling constant $D$ is the same for all pairs at interacting spins in the nanopore~\cite{Doronin_2019,Doronin_2009}.
+We underline that the dipolar coupling constant $D$ is the same for all pairs of interacting spins in the nanopore~\cite{Doronin_2019,Doronin_2009}.
 The density matrix $\rho(\tau)$ on the preparation period of the MQ NMR experiment~\cite{Baum_1985} can be obtained from the Liouville evolution equation~\cite{Goldman_1970,Abragam_1982} 
@@
 For concreteness we suppose that $\omega_{0} = 2\pi \cdot 500 \cdot 10^{6}$~s$^{-1}$ and $D = 2\pi \cdot 10^{4}$~s$^{-1}$.
-In Appendix we proved that the two-pulse Broekart-Jeener sequence~\cite{Goldman_1970,Jeener_1967} results in the dipolar ordered state even at the low Zeemann temperature.
+In Appendix we proved that the two-pulse Broekaert-Jeener sequence~\cite{Goldman_1970,Jeener_1967} results in the dipolar ordered state even at the low Zeemann temperature.
 The adiabatic demagnetization~\cite{Goldman_1970,Slichter_1961} is the second method of preparing the system in the dipolar ordered state.
@@
     \label{eq:5}
-    \rho_i = \frac{1}{Z_i} e^\frac{\hslash\beta_\mathrm{d}}{k}H_\mathrm{dz}
+    \rho_i = \frac{1}{Z_i} e^\frac{\hslash\beta_\mathrm{d} \hdz}{k}
     \approx \frac{1}{Z_i}(1 + \frac{\hslash\beta_\mathrm{d}}{k} H_\mathrm{dz}),
@@
     \label{eq:6}
-    Z_i = \mathrm{Tr} \left\{ e^\frac{\hslash\beta_\mathrm{d}}{k} H_\mathrm{dz}\right\} \approx 2^{N}.
+	Z_i = \mathrm{Tr} \left\{ e^\frac{\hslash\beta_\mathrm{d} \hdz}{k} \right\} \approx 2^{N}.
 \end{equation}
@@
     \quad
-    \rho^{1/2}(0) = 
+    \rho^{1/2}(0) = \dfrac 1 Z
     \begin{pmatrix}
-        \frac 1 2 & 0 
+       	1 & 0 
         \\
-        0 & \frac 1 2
+        0 & 1
     \end{pmatrix}
@@
 %
-It is possible to prove~\cite{Girolami_2017} that the quantum Fisher information $F_\mathrm{Q}(\rho,I_\mathrm{z})$~\cite{Helstrom_1969}
+It is possible to prove~\cite{Girolami_2017} that the quantum Fisher information $F_\mathrm{Q}(\rho,I_\mathrm{z})$~\cite{Helstrom_1976}
 %
@@
 \appendix
-\section{The two-pulse Broekart-Jeener experiment at the low Zeemann and high dipolar temperatures.}
+\section{The two-pulse Broekaert-Jeener experiment at the low Zeemann and high dipolar temperatures.}
 

### 2020-05-16 manuscript.tex
English improvements by Dmitriy Feldman

@@
 
-\title{Many-spin entanglement in multiple quantum NMR with a dipolar ordered initial state}
+\title{Many-spin entanglement in multiple quantum NMR with a dipolar-ordered initial state}
 
@@
 \begin{abstract}
-Many-spin entanglement is investigated for a gas spin-carrying molecules (atoms) in nanocavities 
-in conditions of the multiple quantum (MQ) NMR with a dipolar ordered initial state.
-MQ NMR with the dipolar ordered state opens new possibilities for an exploration of many-spin entanglement. 
-The second moment of a distribution of intensities of MQ NMR coherences,
-which provides a lower bound of the quantum Fisher information, 
-was used for an estimation of the number of entangled spins. 
-Many-spin entanglement is investigated at different temperatures and different numbers of spins in the system under consideration.
+Multiple quantum (MQ) NMR with a dipolar-ordered initial state opens new possibilities for the exploration of many-spin entanglement. 
+In this paper, we investigate many-spin entanglement in a gas of spin-carrying molecules (atoms) in nanocavities 
+in the conditions of MQ NMR with a dipolar-ordered initial state.
+The second moment of the distribution of the intensities of MQ NMR coherences,
+which provides a lower bound on the quantum Fisher information, 
+is used for an estimate of the number of the entangled spins. 
+Many-spin entanglement is investigated at different temperatures and different numbers of spins.
 \end{abstract}
@@
 
-Entanglement~\cite{Nielsen_2009} is a very important quantum conception, which is responsible in particular, for advantages of quantum computers over their classical counterparts.
-Recently demonstrated quantum supremacy using a programmable superconducting processor~\cite{Arute2019} is also connected with entanglement which is absent in classical physics.
-Among numerous methods of an investigation of entanglement we concentrate on multiple quantum (MQ) NMR in solids~\cite{Baum_1985}, which was widely used to characterize entanglement in binary systems~\cite{Furman_2008,Furman_2009,Fel_dman_2008,Fel_dman_2012}.
-It turned out that the MQ NMR spectroscopy~\cite{Baum_1985} allows us to extract also information about many-spin entanglement~\cite{G_rttner_2018}, 
-if one attracts for the analysis the quantum Fisher information~\cite{T_th_2014,Pezz__2018}.
+Entanglement~\cite{Nielsen_2009} is an important notion in quantum mechanics. It is responsible, in particular, for advantages of quantum computers over their classical counterparts.
+Recently demonstrated quantum supremacy of a programmable superconducting processor~\cite{Arute2019} is also connected with entanglement, which is absent in classical physics.
+Among numerous methods of the investigation of entanglement, we focus on multiple quantum (MQ) NMR in solids~\cite{Baum_1985}, which is widely used to characterize entanglement in binary systems~\cite{Furman_2008,Furman_2009,Fel_dman_2008,Fel_dman_2012}.
+It turns out that the MQ NMR spectroscopy~\cite{Baum_1985} allows us to extract information about many-spin entanglement~\cite{G_rttner_2018} by using the quantum Fisher information~\cite{T_th_2014,Pezz__2018}.
 
-The quantum Fisher information describes quickness of changing quantum states determined by the density matrix at changing some parameter. 
-In MQ NMR spectroscopy that parameter is the phase increment between the radio-frequency (rf) pulses irradiating the system on preparation and mixing periods of the MQ NMR experiment~\cite{Baum_1985} in proportional to the evolution time.
-That procedure leads to a separation of the signals,
-corresponding to the MQ NMR coherences of different orders, and obtaining the total MQ NMR spectrum.
-Using the quantum Fisher information (QFI)~\cite{Liu_2014} for an analysis of the MQ NMR spectra one can extract very important information about many-spin entanglement.
+The quantum Fisher information describes the quickness of a change of quantum states determined by a density matrix in response to a change of some parameter. 
+In MQ NMR spectroscopy that parameter is the phase increment between the radio-frequency (rf) pulses, irradiating the system on the preparation and mixing periods of the MQ NMR experiment~\cite{Baum_1985}, \hl{in proportional to the evolution time}.
+The phase increment leads to the separation of the signals,
+corresponding to MQ NMR coherences of different orders, and allows obtaining the total MQ NMR spectrum.
+Using the quantum Fisher information (QFI)~\cite{Liu_2014} for the analysis of the MQ NMR spectra, one can extract important information about many-spin entanglement.
 The point is that there is a relation between the second moment of the MQ NMR spectrum~\cite{Khitrin_1997} and the quantum Fisher information~\cite{G_rttner_2018,Doronin_2019}.
-Moreover the second moment of the MQ NMR spectrum provides a lower bound on the quantum Fisher information~\cite{G_rttner_2018}.
-It means that the MQ NMR spectroscopy is a valuable method for solving quantum information problems.
+Moreover, the second moment of the MQ NMR spectrum provides a lower bound on the quantum Fisher information~\cite{G_rttner_2018}.
+This means that the MQ NMR spectroscopy is a valuable method for solving quantum information problems.
 
-Many-spin entanglement was investigated~\cite{Doronin_2019} on a nonspherical nanopore filled with a gas of spin-carrying molecules in a strong external magnetic field~\cite{Baugh_2001,Doronin_2009}.
-The thermal equilibrium initial state of the system was determined by the one-spin Zeemann interaction with the external magnetic field~\cite{Doronin_2007a}.
-It is also possible to investigate many-spin entanglement when the same system is initially prepared in the dipolar ordered state~\cite{Goldman_1970} using either the adiabatic demagnetization method in a rotating reference frame (RRF)~\cite{Goldman_1970,Slichter_1961} or the two-pulse Broekaert-Jeener sequence~\cite{Goldman_1970,Jeener_1967}.
-The MQ NMR dynamics with this initial state have been simulated both in small spin-systems~\cite{Doronin_2007a,Doronin_2007b} and in the system consisting of 200-600 spin-carrying molecules (atoms) filled in a nanopore~\cite{Doronin_2011}.
-The approaches developed for those investigations are restricted by high temperatures and cannot be applied in order to study many-spin entanglement.
+Many-spin entanglement was investigated~\cite{Doronin_2019} for a nonspherical nanopore filled with a gas of spin-carrying molecules in a strong external magnetic field~\cite{Baugh_2001,Doronin_2009}.
+The thermally equilibrium initial state of the system was determined by the one-spin Zeeman interaction with the external magnetic field~\cite{Doronin_2007a}.
+It is also possible to investigate many-spin entanglement when the same system is initially prepared in the dipolar-ordered state~\cite{Goldman_1970} using either the adiabatic demagnetization method in a rotating reference frame (RRF)~\cite{Goldman_1970,Slichter_1961} or the two-pulse Broekaert-Jeener sequence~\cite{Goldman_1970,Jeener_1967}.
+The MQ NMR dynamics with this initial state have been simulated both in small spin systems~\cite{Doronin_2007a,Doronin_2007b} and in a system consisting of 200-600 spin-carrying molecules (atoms) filling a nanopore~\cite{Doronin_2011}.
+The approaches developed for those investigations are restricted to  high temperatures and cannot be applied to  many-spin entanglement.
 
-In the present article we consider an intermediate temperature case with low Zeemann temperatures and high dipolar ones. 
-Nuclear magnetic ordering~\cite{Abragam_1982} is outside our consideration.
-Notice also that the two-pulse Broekaert-Jeneer experiment~\cite{Jeener_1967} was performed in the high temperature case.
-We prove theoretically that the experiment~\cite{Jeener_1967} can be realized also for the intermediate temperature case of the article. 
-It was shown~\cite{Doronin_2011} that in the MQ NMR experiment with the dipolar ordered initial state MQ NMR coherences emerge faster 
-than in the MQ NMR experiment with the thermal equilibrium initial state in a strong external magnetic field.
-It is important for many-spin entanglement investigations, because they are connected with calculations of the second moment of the distribution of MQ NMR coherences. 
-It is also very important for an investigation of the spreading correlation~\cite{Baugh_2001,Baum_1986,S_nchez_2014,Munowitz_1987} and localization effects~\cite{Alvarez_2015,Wei_2018}.
-At that the spreading rate can be described through out-of-time ordered correlations which are connected with the distribution of MQ NMR coherences.
+In the present article we consider the intermediate-temperature case with low Zeeman temperatures and high dipolar ones. 
+Nuclear magnetic ordering~\cite{Abragam_1982} is beyond the scope of this paper.
+Notice that the two-pulse Broekaert-Jeneer experiment~\cite{Jeener_1967} was performed in the high-temperature case.
+We prove theoretically that the experiment~\cite{Jeener_1967} can be realized also for the intermediate-temperature case. 
+It was shown~\cite{Doronin_2011} that in the MQ NMR experiment with the dipolar-ordered initial state, MQ NMR coherences emerge faster 
+than in the MQ NMR experiment with the thermal-equilibrium initial state in a strong external magnetic field.
+This observation is important for many-spin entanglement investigations, because they involve calculations of the second moment of the distribution of MQ NMR coherences. 
+It is also important for the investigation of the spreading-correlation~\cite{Baugh_2001,Baum_1986,S_nchez_2014,Munowitz_1987} and localization effects~\cite{Alvarez_2015,Wei_2018}.
+Indeed, the spreading rate can be described through out-of-time ordered correlations, which are connected with the distribution of MQ NMR coherences.
 
-The present paper investigates many-spin entanglement using the MQ NMR spectrum of spin-carrying atoms (molecules) in a nanopore when the system is prepared in the dipolar ordered state.
-In Sec.~\ref{sec:2} the theory of MQ NMR dynamics at low Zeemann and high dipolar temperatures is developed.
+The present paper investigates many-spin entanglement using the MQ NMR spectrum of spin-carrying atoms (molecules) in a nanopore when the system is prepared in a dipolar-ordered state.
+In Sec.~\ref{sec:2}, the theory of MQ NMR dynamics at a low Zeeman temperature and a high dipolar temperature is developed.
 An analytical solution for the MQ NMR dynamics of a three-spin system is obtained at such temperatures in Sec.~\ref{sec:3}.
 The second moment of the MQ NMR spectrum as a measure of many-spin entanglement is considered in Sec.~\ref{sec:4}.
-The dependence of many-spin entanglement on the dipolar temperature and the number of spins in the system is investigated in Sec.~\ref{sec:5}.
-We briefly summarize our results in the concluding Sec.~\ref{sec:6}.
-In Appendix we show that the two-pulse Broekaert-Jeener sequence can be used in the case when the Zeemann temperature is low and the dipole one is high.
+The dependence of many-spin entanglement on the dipolar temperature and the number of the spins in the system is investigated in Sec.~\ref{sec:5}.
+We briefly summarize our results in concluding Sec.~\ref{sec:6}.
+In the Appendix, we show that the two-pulse Broekaert-Jeener sequence can be used in the case when the Zeeman temperature is low and the dipole one is high.
 
-\section{Theory of MQ NMR dynamics in a nanopore at low Zeemann and high dipolar temperatures}
+\section{Theory of MQ NMR dynamics in a nanopore at a low Zeeman temperature and a high dipolar temperature}
 \label{sec:2}
 
-MQ NMR dynamics in a nanopore governs the Hamiltonian~\cite{Doronin_2019,Doronin_2009} 
+MQ NMR dynamics in a nanopore is governed by the Hamiltonian~\cite{Doronin_2019,Doronin_2009} 
 %
@@
 %
-$N$ is the number of the spins in the nanopore, $I^{\pm}_{j}$ are the raising or lowering operators of spin $j$, and $D$ is the dipolar coupling constant averaged by the fast molecular diffusion of spin-carrying atoms (molecules) in nanopores.
-We underline that the dipolar coupling constant $D$ is the same for all pairs of interacting spins in the nanopore~\cite{Doronin_2019,Doronin_2009}.
+$N$ is the number of the spins in the nanopore, $I^{\pm}_{j}$ are the raising or lowering operators of spin $j$, and $D$ is the dipolar-coupling constant averaged by the fast molecular diffusion of spin-carrying atoms (molecules) in the nanopore.
+We emphasize that the dipolar-coupling constant $D$ is the same for all pairs of interacting spins in the nanopore~\cite{Doronin_2019,Doronin_2009}.
 The density matrix $\rho(\tau)$ on the preparation period of the MQ NMR experiment~\cite{Baum_1985} can be obtained from the Liouville evolution equation~\cite{Goldman_1970,Abragam_1982} 
@@
 which is directed along the strong external magnetic field,  
-$H_\mathrm{dz}$ is the secular part of the dipole-dipole interaction~(DDI) Hamiltonian in a strong external magnetic field, and $\alpha_\mathrm{z}$, $\beta_\mathrm{d}$ are the inverse Zeemann and dipolar temperatures.
-We will consider the case when the Zeemann temperature is low $({\frac{\hslash \omega}{k} \alpha_\mathrm{z}}\gg 1)$ 
+$H_\mathrm{dz}$ is the secular part of the dipole-dipole interaction~(DDI) Hamiltonian in a strong external magnetic field, and $\alpha_\mathrm{z}$, $\beta_\mathrm{d}$ are the inverse Zeeman and dipolar temperatures.
+We will consider the case when the Zeeman temperature is low $({\frac{\hslash \omega}{k} \alpha_\mathrm{z}}\gg 1)$ 
 and the dipolar temperature is high $\left( \frac{\hslash{D}}{k}\beta_\mathrm{d} \ll 1\right)$.
-For concreteness we suppose that $\omega_{0} = 2\pi \cdot 500 \cdot 10^{6}$~s$^{-1}$ and $D = 2\pi \cdot 10^{4}$~s$^{-1}$.
-In Appendix we proved that the two-pulse Broekaert-Jeener sequence~\cite{Goldman_1970,Jeener_1967} results in the dipolar ordered state even at the low Zeemann temperature.
-The adiabatic demagnetization~\cite{Goldman_1970,Slichter_1961} is the second method of preparing the system in the dipolar ordered state.
-Using those methods we can obtain the system in the thermodynamic equilibrium state with the density matrix
+For concreteness, we suppose that $\omega_{0} = 2\pi \cdot 500 \cdot 10^{6}$~s$^{-1}$ and $D = 2\pi \cdot 10^{4}$~s$^{-1}$.
+In the Appendix, we prove that the two-pulse Broekaert-Jeener sequence~\cite{Goldman_1970,Jeener_1967} results in the dipolar ordered state even at a low Zeeman temperature.
+The adiabatic demagnetization~\cite{Goldman_1970,Slichter_1961} is the second method of preparing a system in the dipolar ordered state.
+Using those methods, we can obtain the system in the thermodynamic equilibrium state with the density matrix
 %
@@
 
-The averaged over the equilibrium density matrix of Eq.~(\ref{eq:5})the resulting signal $G(\tau,\phi)$ after the preparation, evolution and mixing periods of the MQ NMR experiment~\cite{Baum_1985} can be written as~\cite{Doronin_2019}
+Let   $G(\tau,\phi)$  be the signal after the preparation, evolution and mixing periods of the MQ NMR experiment~\cite{Baum_1985}, averaged over the equilibrium density matrix.
+$G(\tau,\phi)$ can be written as~\cite{Doronin_2019}
 %
@@
 %
-Using Eqs.~(\ref{eq:9})~(\ref{eq:10}) one can verity that 
+Using Eqs.~(\ref{eq:9}),~(\ref{eq:10}) one can verity that 
 %
@@
 
-The basis consisting of eigenstates of the operator $I_\mathrm{z}$ (so called the multiplicative basis) is widely used for numerical calculations of MQ NMR dynamics~\cite{Zhang_2009}.
-Due to the fast expansion of the Hilbert space with the growth of the number of spins such calculations are possible only for systems with a small number of spins.
+The basis consisting of the eigenstates of the operator $I_\mathrm{z}$ (dubbed the multiplicative basis) is widely used for numerical calculations of MQ NMR dynamics~\cite{Zhang_2009}.
+Due to the rapid expansion of the Hilbert space with the growth of the number of spins such calculations are possible only for systems with a small number of spins.
 That approach is not suitable for investigations of many-spin entanglement.
-Since the Hamiltonian $H_{MQ}$ of Eq.~(\ref{eq:1}) commutes with the square of the total spin angular momentum $\hat I^2$ 
+Since the Hamiltonian $H_{MQ}$ of Eq.~(\ref{eq:1}) commutes with the square of the total spin angular momentum $\hat I^2$, 
 it is possible to use the basis consisting of the common eigenstates of $\hat I^2$ and $I_\mathrm{z}$ in order to study MQ NMR dynamics as was done in Ref.~\cite{Doronin_2009,Doronin_2011,Doronin_2019}.
-In this basis the Hamiltonian $H_{MQ}$ and the initial density matrix of Eq.~(\ref{eq:5}) (see also Eq.~(\ref{eq:7})) consist of blocks corresponding to different values of the spin angular momentum~\cite{Doronin_2009}.
-Then the investigation of MQ NMR dynamics can be reduced to solving a set of problems of less dimensions.
+In this basis, the Hamiltonian $H_{MQ}$ and the initial density matrix of Eq.~(\ref{eq:5}) (see also Eq.~(\ref{eq:7})) consist of blocks, corresponding to different values of the spin angular momentum~\cite{Doronin_2009}.
+Then the investigation of MQ NMR dynamics can be reduced to solving a set of problems of lower dimensions.
 
-Since the Hamiltonian $H_{MQ}$ of Eq.~(\ref{eq:1}) commutes with the operator $e^{i\pi I_\mathrm{z}}$, $2^N \times 2^N$ Hamiltonian matrix is reduced to two $2^{N-1} \times 2^{N-1}$ submatrices~\cite{Doronin_2009}.
+Since the Hamiltonian $H_{MQ}$ of Eq.~(\ref{eq:1}) commutes with the operator $e^{i\pi I_\mathrm{z}}$, the $2^N \times 2^N$ Hamiltonian matrix reduces to two $2^{N-1} \times 2^{N-1}$ submatrices~\cite{Doronin_2009}.
 For odd $N$, both submatrices give the same contribution to the MQ NMR coherences, and one should solve the problem using only one $2^{N-1} \times 2^{N-1}$ submatrix and double the obtained intensities.
-In our calculations we take only odd numbers of spin.
-Using this method one can investigate MQ NMR dynamics in systems consisting of hundred spins.
+In our calculations, we take only odd numbers of spins.
+Using this method, one can investigate MQ NMR dynamics in systems consisting of hundreds spins.
 
-\section{Analytical solution for MQ NMR dynamics for a three-spin system in a nanopore in dipolar ordered state}
+\section{Analytical solution for MQ NMR dynamics of a three-spin system in a nanopore in a dipolar-ordered state}
 \label{sec:3}
@@
 
-Obtaining the exact solution for MQ NMR dynamics for a three-spin system in the dipolar ordered state in a nanopore is analogously to the case considered in~\cite{Doronin_2019} for the initial thermodynamic equilibrium in a strong external magnetic field.
-We does not use here the high temperature approximation~\cite{Goldman_1970}.
+Obtaining the exact solution for MQ NMR dynamics of a three-spin system in a dipolar-ordered state in a nanopore is similar to the problem considered in Ref.~\cite{Doronin_2019} for the initial thermodynamic equilibrium in a strong external magnetic field.
+Here we do not use the high temperature approximation~\cite{Goldman_1970}.
 
-The Hamiltonian $H_{MQ}$ of Eq.~(\ref{eq:1}) consists here of the two blocks for two possible values of spin angular momentum $(I^2 = S(S+1),  \quad S=3/2,1/2)$.
-Those blocks, the corresponding eigenvalues and eigenstates are given in~\cite{Doronin_2019}.
-The density matrix of the system consists also of the two blocks $\rho^{3/2}(\tau)$, $\rho^{1/2}(\tau)$, and 
+The Hamiltonian $H_{MQ}$ of Eq.~(\ref{eq:1}) consists here of two blocks for the two possible values of the spin angular momentum $(I^2 = S(S+1),  \quad S=3/2,1/2)$.
+Those blocks and the corresponding eigenvalues and eigenstates are given in Ref.~\cite{Doronin_2019}.
+The density matrix of the system consists also of two blocks $\rho^{3/2}(\tau)$, $\rho^{1/2}(\tau)$, and 
 %
@@
 where $b = \dfrac{\hslash D}{k\mathrm{T}}$and $T$ is the temperature.
-After simple calculations one can obtain the density matrices $\rho^{3/2}(\tau)$ and $\rho^{1/2}(\tau)$ 
-which allow us to find intensities of the MQ NMR coherences.
+After simple calculations one can obtain the density matrices $\rho^{3/2}(\tau)$ and $\rho^{1/2}(\tau)$, 
+which allow us to find the intensities of the MQ NMR coherences.
 
@@
 %
-The sum of intensities of Eq.~(\ref{eq:16}) equals one in accordance with Eq.~(\ref{eq:14}).
+The sum of the intensities of Eq.~(\ref{eq:16}) equals one in accordance with Eq.~(\ref{eq:14}).
 The dependencies of the calculated intensities $J_{n}(\tau)$ $(n=0,2)$ on the evolution time are shown in Fig.~(\ref{fig:1}).
@@
 
-The expression~(\ref{eq:8}) for the MQ NMR signal $G(\tau,\phi)$ can be expanded in series over the phase increment $\phi$:
+The expression~(\ref{eq:8}) for the MQ NMR signal $G(\tau,\phi)$ can be expanded in series in the phase increment $\phi$:
 %
@@
 %
-At the same time, it is easily to verify that $2 \mathrm{Tr} \left\{ \rho^2(\tau) I_\mathrm{z}^2 - \left( \rho(\tau) I_\mathrm{z} \right)^2 \right\}$ equals to the second moment $M_2$ of the distribution of intensities of the MQ NMR coherences~\cite{Khitrin_1997}
+At the same time, it is easy to verify that $2 \mathrm{Tr} \left\{ \rho^2(\tau) I_\mathrm{z}^2 - \left( \rho(\tau) I_\mathrm{z} \right)^2 \right\}$ equals the second moment $M_2$ of the distribution of the intensities of the MQ NMR coherences~\cite{Khitrin_1997}
 %
@@
 where $J_n(\tau)$ ($n=0,\pm 2, \pm 4, \cdots$) is determined by Eq.~(\ref{eq:13}).
-Thus, the second moment of the MQ NMR spectrum provides a low bound on the quantum Fisher information $F_\mathrm{Q}(\rho,I_\mathrm{z})$
+Thus, the second moment of the MQ NMR spectrum provides a lower bound on the quantum Fisher information $F_\mathrm{Q}(\rho,I_\mathrm{z})$.
 It was also shown~\cite{T_th_2014,Pezz__2018} that if
@@
 %
-where $n$ is the integer part of {N/k}, then the system with the density matrix $\rho(\tau)$ is $k+1$-spin entangled~\cite{Pezz__2009,Hyllus_2012,T_th_2012}.
+where $n$ is the integer part of ${N/k}$, then the system with the density matrix $\rho(\tau)$ is $(k+1)$-spin entangled~\cite{Pezz__2009,Hyllus_2012,T_th_2012}.
 The results of the numerical analysis of many-spin entanglement in the system of spin-carrying molecules (atoms) initially prepared in the dipolar ordered state are presented in the following section.
 
-\section{Numerical analysis of many-spin entanglement at different temperatures and the numbers of spins in the system}
+\section{Numerical analysis of many-spin entanglement at different temperatures and numbers of spins in the system}
 \label{sec:5}
@@
 	\caption{
-	    The dependence of the low bound of the quantum Fisher Information $F_\mathrm{Q} = 2 M_{2}$ 
-	    on the dimensionless time $D\tau$ at $N=101$, 
+	    The dependence of the lower bound on the quantum Fisher Information $F_\mathrm{Q} = 2 M_{2}$ 
+	    on the dimensionless time $D\tau$ at $N=101$.
 	    a) $T=6\cdot10^{-4}$~K, the inequality~(\ref{eq:20}) yields the region of pair entanglement (k+1=2), the region is above the horizontal line; 
 	    b) $T=3.2\cdot10^{-4}$~K, the region of the many-spin entanglement is a strip bounded by the horizontal lines with~$k=32$~and~$k=46$; 
-	    c) $T = 1.6\cdot10^{_4}$~K, the horizontal lines ($k=47$ and k=$86$) bound the strip with many spin enatnglement;
+	    c) $T = 1.6\cdot10^{_4}$~K, the horizontal lines ($k=47$ and k=$86$) bound the strip with many-spin entanglement;
 	    d) $T=4.8\cdot10^{-5}$~K, entangled clusters with $47-92$ spins emerge.
@@
 
-The considered model of the spin-carrying molecules (atoms) in a nanopore in the dipolar ordered states expands possibilities of an investigation of many-spin entanglement in comparison to the analogous model~\cite{Doronin_2019}
-when the system was initially in the thermodynamic equilibrium in a strong external magnetic field.
-The model~\cite{Doronin_2019}  is restricted for investigation of the time evolution of the system
+The considered model of the spin-carrying molecules (atoms) in a nanopore in the dipolar ordered states expands possibilities of the investigation of many-spin entanglement in comparison with the related model~\cite{Doronin_2019},
+in which the system was initially in the thermodynamic equilibrium in a strong external magnetic field.
+The model~\cite{Doronin_2019}  is not useful for the investigation of the time-evolution of the system
 because the stationary distribution of MQ NMR coherences establishes very quickly~\cite{Doronin_2009}.
-The temperature dependence of many-spin entanglement occurs in the model~\cite{Doronin_2019} in a very narrow temperature interval.
-For example, all spins are entangled in the system consisting of 201 spins at temperature $T=6.856\cdot10^{-3}$~K~\cite{Doronin_2019}.
+Many-spin entanglement changes with the temperature in a very narrow temperature interval in the model~\cite{Doronin_2019}.
+For example, all spins are entangled in the system consisting of 201 spins at the temperature $T=6.856\cdot10^{-3}$~K~\cite{Doronin_2019}.
 
 The time dependence of the quantum Fisher information in the system consisting of 101 spins is presented in Fig.~(\ref{fig:2}) at different temperatures. 
-One can see from Fig.~(\ref{fig:2}a) that only the pair entanglement exists at temperature $T=6\cdot10^{-4}$~K.
-At the temperature $T=3.2\cdot10^{-4}$ one can see a strip Fig.~(\ref{fig:2}b), in which the inequality~(\ref{eq:20}) can be satisfied when ${32}\leq {k}\leq{46}$.
-Thus, there is many-spin entanglement in spin clusters consisting of 33-47 spins at temperature $3.2\cdot10^{-4}$~K.
+One can see from Fig.~(\ref{fig:2}a) that only pair entanglement exists at the temperature $T=6\cdot10^{-4}$~K.
+At the temperature $T=3.2\cdot10^{-4}$, one can see a strip in Fig.~(\ref{fig:2}b), in which the inequality~(\ref{eq:20}) can be satisfied when ${32}\leq {k}\leq{46}$.
+Thus, there is many-spin entanglement in spin clusters consisting of 33-47 spins at the temperature $3.2\cdot10^{-4}$~K.
 When the temperature decreases, the width of the strip, in which many-spin entanglement exists, increases. 
-At temperature $T=1.6\cdot10^{-4}$~K (Fig.~(\ref{fig:2}c)) clusters of 48-87 entangled spins emerge, and at temperature $T=4.8\cdot10^{-5}$~K (Fig.~(\ref{fig:2}d)) we have 47-92 entangled spins.
+At the temperature $T=1.6\cdot10^{-4}$~K (Fig.~(\ref{fig:2}c)), clusters of 48-87 entangled spins emerge, and at the temperature $T=4.8\cdot10^{-5}$~K (Fig.~(\ref{fig:2}d)), we have 47-92 entangled spins.
 
@@
 
-The dependence of the maximal number of the entangled spins averaged over the evolution time $({0}\leq \mathrm{D}\tau\leq{3})$, on the temperature at different numbers of spins in a nanopore is presented in Fig.~(\ref{fig:3}).
-The maximal number of entangled spins decreases when the temperature increases. 
-The maximal number of entangled spins increases when the number of spins in the nanopore increases also, because the system in the nanopore gets more dense.
+The dependence of the average of the maximal number of the entangled spins over the evolution time $({0}\leq \mathrm{D}\tau\leq{3})$ on the temperature at different numbers of the spins in a nanopore is presented in Fig.~(\ref{fig:3}).
+The maximal number of the entangled spins decreases when the temperature increases. 
+The maximal number of the entangled spins increases when the number of the spins in the nanopore increases, because the system in the nanopore gets denser.
 
@@
 
-We investigated many-spin entanglement in the system of spin-carrying molecules (atoms) filled in the non-spherical nanopore, initially prepared in the dipolar ordered state, in the conditions of the MQ NMR spectroscopy .
-The dependence of many-spin entanglement on the temperature and the number of spins in the nanopore were investigated.
+We investigated many-spin entanglement in a system of spin-carrying molecules (atoms) filling a non-spherical nanopore in the conditions of the MQ NMR spectroscopy.
+The spins are in the dipolar ordered state initially.
+We found the dependence of many-spin entanglement on the temperature and the number of the spins in the nanopore.
 
-We believe that the MQ NMR spectroscopy is a subtle and useful method for investigations of different quantum information problems.
-In particularly, it is a very effective method for exploration of quantum entanglement.
+We believe that the MQ NMR spectroscopy is a subtle and useful method for the investigation of different quantum information problems.
+In particularly, it is a very effective method for the exploration of quantum entanglement.
 
@@
 \appendix
-\section{The two-pulse Broekaert-Jeener experiment at the low Zeemann and high dipolar temperatures.}
+\section{The two-pulse Broekaert-Jeener experiment at a low Zeeman temperature and a high dipolar temperature.}
 
@@
 %
-After the first resonance rf x-pulse one has
+After the first resonance rf x-pulse, one has
 %
@@
 %
-Then the system evolves freely time $\tau$ 
+Then the system evolves freely during the time $\tau$, 
 and one applies the second resonance y-pulse rotating spins by angle $\theta$ around the y-axis of the RRF.
@@
 %
-After time $T_2$ ($T_2$ is the spin relaxation time \cite{Goldman_1970}) the system achieves the thermodynamic equilibrium state
+After the time $T_2$ ($T_2$ is the spin relaxation time \cite{Goldman_1970}) the system achieves the thermodynamic equilibrium state
 \begin{equation}
@@
 where $\alpha$ and $\beta$ are the inverse Zeeman and dipolar temperatures.
-It is evident that the system has the single equilibrium state 
-and the temperatures $\alpha$ and $\beta$ are also single.
+It is evident that the system has a single equilibrium state 
+and the temperatures $\alpha$ and $\beta$ \hl{are also single}.
 Those temperatures can be obtained from the conservation laws
@@
 %
-In~(\ref{eq:a7} we took into account that $\left[ e^{-i \pi \sy}, \hdz \right] = 0$.
-Since we consider the case of a high dipolar temperature it is possible for rewrite~(\ref{eq:a5}) as
+In~(\ref{eq:a7}) we took into account that $\left[ e^{-i \pi \sy}, \hdz \right] = 0$.
+Since we consider the case of a high dipolar temperature, it is possible for rewrite~(\ref{eq:a5}) as
 \begin{equation}
@@
 Notice that $\tr{\sz} = \tr{\sz\hdz} = 0$. It means that $\alpha = 0$ satisfies Eq.~(\ref{eq:5}). 
-Thus we obtain the dipolar ordered state in the considered case.
+Thus, we obtain the dipolar ordered state in the considered case.
 

### 2020-05-16 manuscript.tex
Fix hl areas

@@
 The quantum Fisher information describes the quickness of a change of quantum states determined by a density matrix in response to a change of some parameter. 
-In MQ NMR spectroscopy that parameter is the phase increment between the radio-frequency (rf) pulses, irradiating the system on the preparation and mixing periods of the MQ NMR experiment~\cite{Baum_1985}, \hl{in proportional to the evolution time}.
-The phase increment leads to the separation of the signals,
+In MQ NMR spectroscopy, that parameter is the phase increment between the radio-frequency (rf) pulses, irradiating the system on the preparation and mixing periods of the MQ NMR experiment~\cite{Baum_1985}.
+The phase increment is proportional to the duration of the evolution period that leads to the separation of the signals,
 corresponding to MQ NMR coherences of different orders, and allows obtaining the total MQ NMR spectrum.
@@
 This observation is important for many-spin entanglement investigations, because they involve calculations of the second moment of the distribution of MQ NMR coherences. 
-It is also important for the investigation of the spreading-correlation~\cite{Baugh_2001,Baum_1986,S_nchez_2014,Munowitz_1987} and localization effects~\cite{Alvarez_2015,Wei_2018}.
+It is also important for the investigation of correlation spreading~\cite{Baugh_2001,Baum_1986,S_nchez_2014,Munowitz_1987} and localization~\cite{Alvarez_2015,Wei_2018}.
 Indeed, the spreading rate can be described through out-of-time ordered correlations, which are connected with the distribution of MQ NMR coherences.
@@
 It is evident that the system has a single equilibrium state 
-and the temperatures $\alpha$ and $\beta$ \hl{are also single}.
+and there is a unique choice of the temperatures $\alpha$ and $\beta$ 
+that is consistent with the conservation laws.
 Those temperatures can be obtained from the conservation laws

### 2020-05-16 manuscript.tex
Fix hl areas

@@
 The quantum Fisher information describes the quickness of a change of quantum states determined by a density matrix in response to a change of some parameter. 
-In MQ NMR spectroscopy, that parameter is the phase increment between the radio-frequency (rf) pulses, irradiating the system on the preparation and mixing periods of the MQ NMR experiment~\cite{Baum_1985}.
-The phase increment is proportional to the duration of the evolution period that leads to the separation of the signals,
-corresponding to MQ NMR coherences of different orders, and allows obtaining the total MQ NMR spectrum.
+In MQ NMR spectroscopy, that parameter is the phase increment between the radio-frequency (rf) pulses, irradiating the system on the preparation and mixing periods of the MQ NMR experiment~\cite{Baum_1985}
+that leads to the separation of the signals, corresponding to MQ NMR coherences of different orders, and allows obtaining the total MQ NMR spectrum. 
+The phase increment is proportional to the duration of the evolution period.
 Using the quantum Fisher information (QFI)~\cite{Liu_2014} for the analysis of the MQ NMR spectra, one can extract important information about many-spin entanglement.

### 2020-05-17 manuscript.tex
Fix defises

@@
 
-\title{Many-spin entanglement in multiple quantum NMR with a dipolar-ordered initial state}
+\title{Many-spin entanglement in multiple quantum NMR with a dipolar ordered initial state}
 
@@
 \begin{abstract}
-Multiple quantum (MQ) NMR with a dipolar-ordered initial state opens new possibilities for the exploration of many-spin entanglement. 
+Multiple quantum (MQ) NMR with a dipolar ordered initial state opens new possibilities for the exploration of many-spin entanglement. 
 In this paper, we investigate many-spin entanglement in a gas of spin-carrying molecules (atoms) in nanocavities 
-in the conditions of MQ NMR with a dipolar-ordered initial state.
+in the conditions of MQ NMR with a dipolar ordered initial state.
 The second moment of the distribution of the intensities of MQ NMR coherences,
@@
 The thermally equilibrium initial state of the system was determined by the one-spin Zeeman interaction with the external magnetic field~\cite{Doronin_2007a}.
-It is also possible to investigate many-spin entanglement when the same system is initially prepared in the dipolar-ordered state~\cite{Goldman_1970} using either the adiabatic demagnetization method in a rotating reference frame (RRF)~\cite{Goldman_1970,Slichter_1961} or the two-pulse Broekaert-Jeener sequence~\cite{Goldman_1970,Jeener_1967}.
+It is also possible to investigate many-spin entanglement when the same system is initially prepared in the dipolar ordered state~\cite{Goldman_1970} using either the adiabatic demagnetization method in a rotating reference frame (RRF)~\cite{Goldman_1970,Slichter_1961} or the two-pulse Broekaert-Jeener sequence~\cite{Goldman_1970,Jeener_1967}.
 The MQ NMR dynamics with this initial state have been simulated both in small spin systems~\cite{Doronin_2007a,Doronin_2007b} and in a system consisting of 200-600 spin-carrying molecules (atoms) filling a nanopore~\cite{Doronin_2011}.
@@
 We prove theoretically that the experiment~\cite{Jeener_1967} can be realized also for the intermediate-temperature case. 
-It was shown~\cite{Doronin_2011} that in the MQ NMR experiment with the dipolar-ordered initial state, MQ NMR coherences emerge faster 
+It was shown~\cite{Doronin_2011} that in the MQ NMR experiment with the dipolar ordered initial state, MQ NMR coherences emerge faster 
 than in the MQ NMR experiment with the thermal-equilibrium initial state in a strong external magnetic field.
@@
 
-The present paper investigates many-spin entanglement using the MQ NMR spectrum of spin-carrying atoms (molecules) in a nanopore when the system is prepared in a dipolar-ordered state.
+The present paper investigates many-spin entanglement using the MQ NMR spectrum of spin-carrying atoms (molecules) in a nanopore when the system is prepared in a dipolar ordered state.
 In Sec.~\ref{sec:2}, the theory of MQ NMR dynamics at a low Zeeman temperature and a high dipolar temperature is developed.
@@
 %
-$N$ is the number of the spins in the nanopore, $I^{\pm}_{j}$ are the raising or lowering operators of spin $j$, and $D$ is the dipolar-coupling constant averaged by the fast molecular diffusion of spin-carrying atoms (molecules) in the nanopore.
-We emphasize that the dipolar-coupling constant $D$ is the same for all pairs of interacting spins in the nanopore~\cite{Doronin_2019,Doronin_2009}.
+$N$ is the number of the spins in the nanopore, $I^{\pm}_{j}$ are the raising or lowering operators of spin $j$, and $D$ is the dipolar coupling constant averaged by the fast molecular diffusion of spin-carrying atoms (molecules) in the nanopore.
+We emphasize that the dipolar coupling constant $D$ is the same for all pairs of interacting spins in the nanopore~\cite{Doronin_2019,Doronin_2009}.
 The density matrix $\rho(\tau)$ on the preparation period of the MQ NMR experiment~\cite{Baum_1985} can be obtained from the Liouville evolution equation~\cite{Goldman_1970,Abragam_1982} 
@@
 
-\section{Analytical solution for MQ NMR dynamics of a three-spin system in a nanopore in a dipolar-ordered state}
+\section{Analytical solution for MQ NMR dynamics of a three-spin system in a nanopore in a dipolar ordered state}
 \label{sec:3}
@@
 
-Obtaining the exact solution for MQ NMR dynamics of a three-spin system in a dipolar-ordered state in a nanopore is similar to the problem considered in Ref.~\cite{Doronin_2019} for the initial thermodynamic equilibrium in a strong external magnetic field.
+Obtaining the exact solution for MQ NMR dynamics of a three-spin system in a dipolar ordered state in a nanopore is similar to the problem considered in Ref.~\cite{Doronin_2019} for the initial thermodynamic equilibrium in a strong external magnetic field.
 Here we do not use the high temperature approximation~\cite{Goldman_1970}.

### 2020-05-17 manuscript.tex
Fix figure: low bound of FI

@@
 	    a) $T=6\cdot10^{-4}$~K, the inequality~(\ref{eq:20}) yields the region of pair entanglement (k+1=2), the region is above the horizontal line; 
-	    b) $T=3.2\cdot10^{-4}$~K, the region of the many-spin entanglement is a strip bounded by the horizontal lines with~$k=32$~and~$k=46$; 
-	    c) $T = 1.6\cdot10^{_4}$~K, the horizontal lines ($k=47$ and k=$86$) bound the strip with many-spin entanglement;
-	    d) $T=4.8\cdot10^{-5}$~K, entangled clusters with $47-92$ spins emerge.
+	    b) $T=3.2\cdot10^{-4}$~K, the region of the many-spin entanglement is a strip bounded by the horizontal lines with~$k=19$~and~$k=46$; 
+	    c) $T = 1.6\cdot10^{_4}$~K, the horizontal lines ($k=18$ and k=$86$) bound the strip with many-spin entanglement;
+	    d) $T=4.8\cdot10^{-5}$~K, entangled clusters with $10-92$ spins emerge.
 	}
@@
 One can see from Fig.~(\ref{fig:2}a) that only pair entanglement exists at the temperature $T=6\cdot10^{-4}$~K.
-At the temperature $T=3.2\cdot10^{-4}$, one can see a strip in Fig.~(\ref{fig:2}b), in which the inequality~(\ref{eq:20}) can be satisfied when ${32}\leq {k}\leq{46}$.
-Thus, there is many-spin entanglement in spin clusters consisting of 33-47 spins at the temperature $3.2\cdot10^{-4}$~K.
+At the temperature $T=3.2\cdot10^{-4}$, one can see a strip in Fig.~(\ref{fig:2}b), in which the inequality~(\ref{eq:20}) can be satisfied when $19 \leq k \leq 46$.
+Thus, there is many-spin entanglement in spin clusters consisting of 20-47 spins at the temperature $3.2\cdot10^{-4}$~K.
 When the temperature decreases, the width of the strip, in which many-spin entanglement exists, increases. 
-At the temperature $T=1.6\cdot10^{-4}$~K (Fig.~(\ref{fig:2}c)), clusters of 48-87 entangled spins emerge, and at the temperature $T=4.8\cdot10^{-5}$~K (Fig.~(\ref{fig:2}d)), we have 47-92 entangled spins.
+At the temperature $T=1.6\cdot10^{-4}$~K (Fig.~(\ref{fig:2}c)), clusters of 19-87 entangled spins emerge, and at the temperature $T=4.8\cdot10^{-5}$~K (Fig.~(\ref{fig:2}d)), we have 11-92 entangled spins.
 

### 2020-05-17 manuscript.tex
Fix bugs

@@
        e^{
-            \frac{\hslash \omega}{k} \alpha_\mathrm{z} I_\mathrm{z} 
+		   \frac{\hslash \omega_{0}}{k} \alpha_\mathrm{z} I_\mathrm{z} 
             + \frac{\hslash }{k} \beta_\mathrm{d} H_\mathrm{dz}
@@
 where 
-$Z = \mathrm{Tr} \left\{ e^{\frac{\hslash \omega}{k} \alpha_\mathrm{z} I_\mathrm{z} + \frac{\hslash  }{k} \beta_\mathrm{d} H_\mathrm{dz}} \right\}$ is the partition function, 
+$Z = \mathrm{Tr} \left\{ e^{\frac{\hslash \omega_{0}}{k} \alpha_\mathrm{z} I_\mathrm{z} + \frac{\hslash  }{k} \beta_\mathrm{d} H_\mathrm{dz}} \right\}$ is the partition function, 
 $\hslash$ and $k$ are the Plank and Boltzmann constants, 
@@
 $H_\mathrm{dz}$ is the secular part of the dipole-dipole interaction~(DDI) Hamiltonian in a strong external magnetic field, and $\alpha_\mathrm{z}$, $\beta_\mathrm{d}$ are the inverse Zeeman and dipolar temperatures.
-We will consider the case when the Zeeman temperature is low $({\frac{\hslash \omega}{k} \alpha_\mathrm{z}}\gg 1)$ 
+We will consider the case when the Zeeman temperature is low $({\frac{\hslash \omega_{0}}{k} \alpha_\mathrm{z}}\gg 1)$ 
 and the dipolar temperature is high $\left( \frac{\hslash{D}}{k}\beta_\mathrm{d} \ll 1\right)$.
@@
 	\caption{
-	    Intensities of MQ NRM coherenes $J_{n}$ ($n=0, 2$) in a nanopore with $N=3$.
+	    Intensities of MQ NMR coherenes $J_{n}$ ($n=0, 2$) in a nanopore with $N=3$.
 	}
@@
 	    c) $T = 1.6\cdot10^{_4}$~K, the horizontal lines ($k=18$ and k=$86$) bound the strip with many-spin entanglement;
-	    d) $T=4.8\cdot10^{-5}$~K, entangled clusters with $10-92$ spins emerge.
+	    d) $T=4.8\cdot10^{-5}$~K, entangled clusters with $11-92$ spins emerge.
 	}

### 2020-05-27 maniscript_rus.tex
Add manuscript translation to Russian.

--- 2020-05-17 manuscript.tex
@@
 \documentclass[review]{elsarticle}
+\usepackage[english,russian]{babel}
 
@@
 
-\title{Many-spin entanglement in multiple quantum NMR with a dipolar ordered initial state}
+\title{Многоспиновая запутанность в многоквантовом ЯМР с диполярно упорядоченным начальным состоянием}
 
-\author[icp]{E.~B.~Feldman}
-\author[icp,msu]{I.~D.~Lazarev} %
+\author[icp]{Э.~Б.~Фельдман}
+\author[icp,msu]{И.~Д.~Лазарев} %
 
-\address[icp]{Institute of Problems of Chemical Physics of Russian Academy of Sciences, \\ Chernogolovka, Moscow Region, Russia 142432}
-\address[msu]{Faculty of Fundamental Physical-Chemical Engineering, Lomonosov Moscow State University, GSP-1, Moscow, Russia 119991}
+\address[icp]{Институт проблем химической физики РАН, \\ Черноголовка, Московская область, Россия 142432}
+\address[msu]{Факультет фундаментальной физико-химической инженерии, МГУ GSP-1, Москва, Россия 119991}
 
 \begin{abstract}
-Multiple quantum (MQ) NMR with a dipolar ordered initial state opens new possibilities for the exploration of many-spin entanglement. 
-In this paper, we investigate many-spin entanglement in a gas of spin-carrying molecules (atoms) in nanocavities 
-in the conditions of MQ NMR with a dipolar ordered initial state.
-The second moment of the distribution of the intensities of MQ NMR coherences,
-which provides a lower bound on the quantum Fisher information, 
-is used for an estimate of the number of the entangled spins. 
-Many-spin entanglement is investigated at different temperatures and different numbers of spins.
+Многоквантовый (МК)  ЯМР с диполярно упорядоченным начальным состоянием открывает новые возможности для изучения многоспиновой запутанности. 
+В данной статье исследуется многоспиновая запутанность в газе спин-несущих молекул (атомов) в нанорезонаторах
+в условиях ЯМР с дипольно упорядоченным начальным состоянием.
+Для оценки количества запутанных спинов используется второй момент распределения интенсивнойстей МК ЯМР-когерентностей, 
+который определяет нижнюю границу квантовой информации Фишера. 
+Многоспиновая запутанность исследуется при различных температурах и различном количестве спинов.
 \end{abstract}
@@
 \begin{keyword}
-multiple quantum (MQ) NMR \sep  
-quantum correlations \sep 
-quantum Fisher information \sep 
-entanglement, nano-pore \sep 
-MQ NMR coherence \sep 
-second moment, temperature \sep 
-dipolar ordered state \sep 
-two-pulse Broekaert-Jeener sequence
+многоквантовый (МК) ЯМР \sep  
+квантовые корреляции \sep 
+квантовая информация Фишера \sep 
+запутанность, нанопора \sep 
+МК ЯМР когерентность \sep 
+второй момент, температура \sep 
+диполярно упорядоченное состояние \sep 
+двухимпульсная последовательность Брукерта-Джинера
 \end{keyword}
@@
 
-\linenumbers
+%\linenumbers
 
@@
 
-Entanglement~\cite{Nielsen_2009} is an important notion in quantum mechanics. It is responsible, in particular, for advantages of quantum computers over their classical counterparts.
-Recently demonstrated quantum supremacy of a programmable superconducting processor~\cite{Arute2019} is also connected with entanglement, which is absent in classical physics.
-Among numerous methods of the investigation of entanglement, we focus on multiple quantum (MQ) NMR in solids~\cite{Baum_1985}, which is widely used to characterize entanglement in binary systems~\cite{Furman_2008,Furman_2009,Fel_dman_2008,Fel_dman_2012}.
-It turns out that the MQ NMR spectroscopy~\cite{Baum_1985} allows us to extract information about many-spin entanglement~\cite{G_rttner_2018} by using the quantum Fisher information~\cite{T_th_2014,Pezz__2018}.
+Запутанность~\cite{Nielsen_2009} является важным понятием квантовой механики. Наличие данного понятия определеяет преимущество квантовых компьютеров перед их классическими аналогами. 
+Продемонстрированное квантовое превосходство программируемого сверхпроводящего процессора~\cite{Arute2019} также связано с понятием запутанности, которое отсутствует в классической физике.
+Среди многочисленных методов исследования запутанности мы сосредоточились на многоквантовом (МК) ЯМР в твердых телах~\cite{Baum_1985}, который широко используется для характеристики запутанности в двоичных системах~\cite{Furman_2008, Furman_2009, Fel_dman_2008, Fel_dman_2012}.
+МК ЯМР-спектроскопия~\cite{Baum_1985} позволяет извлекать информацию о многоспиновой запутанности~\cite{G_rttner_2018} с помощью квантовой информации Фишера~\cite{T_th_2014, Pezz__2018}.
 
-The quantum Fisher information describes the quickness of a change of quantum states determined by a density matrix in response to a change of some parameter. 
-In MQ NMR spectroscopy, that parameter is the phase increment between the radio-frequency (rf) pulses, irradiating the system on the preparation and mixing periods of the MQ NMR experiment~\cite{Baum_1985}
-that leads to the separation of the signals, corresponding to MQ NMR coherences of different orders, and allows obtaining the total MQ NMR spectrum. 
-The phase increment is proportional to the duration of the evolution period.
-Using the quantum Fisher information (QFI)~\cite{Liu_2014} for the analysis of the MQ NMR spectra, one can extract important information about many-spin entanglement.
-The point is that there is a relation between the second moment of the MQ NMR spectrum~\cite{Khitrin_1997} and the quantum Fisher information~\cite{G_rttner_2018,Doronin_2019}.
-Moreover, the second moment of the MQ NMR spectrum provides a lower bound on the quantum Fisher information~\cite{G_rttner_2018}.
-This means that the MQ NMR spectroscopy is a valuable method for solving quantum information problems.
+Квантовая информация Фишера описывает скорость изменения квантовых состояний, определяемых матрицей плотности в ответ на изменение какого-либо параметра.
+В МК спектроскопии ЯМР данный параметр представляет собой приращение фазы между радиочастотными импульсами, облучающими систему в периоды приготовления и смешивания в эксперименте по МК ЯМР~\cite{Baum_1985},
+что приводит к разделению сигналов, соответсвующих МК когерентности ЯМР разных порядков, и позволяет получить полный спектр МК ЯМР. 
+Приращение фазы пропорционально продолжительности периода эволюции.
+Используя квантовую информацию Фишера~\cite{Liu_2014} для анализа спектра МК ЯМР, можно получить важную информацию о многоспиновой запутанности,
+поскольку сущесвует связь между вторым моментом спектра ~\cite{Khitrin_1997} и квантовой информацией Фишера~\cite{G_rttner_2018,Doronin_2019}.
+Кроме того второй момент спектра МК ЯМР определяет нижнюю границу квантовой информации Фишера~\cite{G_rttner_2018}.
+Это означает, что МК ЯМР-спектроскопия является ценным методом решения квантовых информационных задач.
 
-Many-spin entanglement was investigated~\cite{Doronin_2019} for a nonspherical nanopore filled with a gas of spin-carrying molecules in a strong external magnetic field~\cite{Baugh_2001,Doronin_2009}.
-The thermally equilibrium initial state of the system was determined by the one-spin Zeeman interaction with the external magnetic field~\cite{Doronin_2007a}.
-It is also possible to investigate many-spin entanglement when the same system is initially prepared in the dipolar ordered state~\cite{Goldman_1970} using either the adiabatic demagnetization method in a rotating reference frame (RRF)~\cite{Goldman_1970,Slichter_1961} or the two-pulse Broekaert-Jeener sequence~\cite{Goldman_1970,Jeener_1967}.
-The MQ NMR dynamics with this initial state have been simulated both in small spin systems~\cite{Doronin_2007a,Doronin_2007b} and in a system consisting of 200-600 spin-carrying molecules (atoms) filling a nanopore~\cite{Doronin_2011}.
-The approaches developed for those investigations are restricted to  high temperatures and cannot be applied to  many-spin entanglement.
+Многоспиновая запутанность была исследована~\cite{Doronin_2019} для несферической нанопоры, заполненной газом переносящих спин молекул в сильном внешнем магнитном поле~\cite{Baugh_2001,Doronin_2009}.
+Термически равновесное начальное состояние системы определялось односпиновым зеемановским взаимодействием с внешним магнитным полем~\cite{Doronin_2007a}.
+Также возможно исследовать многоспиновую запутанность, когда та же самая система первоначально подготовлена в диполярном упорядоченном состоянии~\cite{Goldman_1970}, используя либо метод адиабатического размагничивания во вращающейся системе отсчета~\cite{Goldman_1970, Slichter_1961} , либо двухимпульную последовательность Брукерта-Джинера~\cite{Goldman_1970, Jeener_1967}.
+Динамика МК ЯМР с этим начальным состоянием моделировалась как в малых спиновых системах~\cite{Doronin_2007a, Doronin_2007b}, так и в системе, состоящей из 200-600 спин-несущих молекул (атомов), заполняющих нанопоры ~\cite{Doronin_2011}.
+Однако подходы, разработанные для этих исследований, ограничены высокими температурами и не могут применяться к многоспиновому запутыванию.
 
-In the present article we consider the intermediate-temperature case with low Zeeman temperatures and high dipolar ones. 
-Nuclear magnetic ordering~\cite{Abragam_1982} is beyond the scope of this paper.
-Notice that the two-pulse Broekaert-Jeneer experiment~\cite{Jeener_1967} was performed in the high-temperature case.
-We prove theoretically that the experiment~\cite{Jeener_1967} can be realized also for the intermediate-temperature case. 
-It was shown~\cite{Doronin_2011} that in the MQ NMR experiment with the dipolar ordered initial state, MQ NMR coherences emerge faster 
-than in the MQ NMR experiment with the thermal-equilibrium initial state in a strong external magnetic field.
-This observation is important for many-spin entanglement investigations, because they involve calculations of the second moment of the distribution of MQ NMR coherences. 
-It is also important for the investigation of correlation spreading~\cite{Baugh_2001,Baum_1986,S_nchez_2014,Munowitz_1987} and localization~\cite{Alvarez_2015,Wei_2018}.
-Indeed, the spreading rate can be described through out-of-time ordered correlations, which are connected with the distribution of MQ NMR coherences.
+В настоящей статье мы рассматриваем среднетемпературный случай с низкими зеемановскими и высокими дипольными.
+Магнитное упорядочевание~\cite{Abragam_1982} выходит за рамки данной статьи.
+Стоит обратить внимание, что двухимпульсный эксперимент     Брукерта-Дженира~\cite{Jeener_1967} был выполнен при высоких температурах.
+В данной статье было доказано, что этот эксперимент~\cite{Jeener_1967} также может выполняться при средних температурах.  
+Было показано~\cite{Doronin_2011}, что в МК эксперименте ЯМР с диполярно упорядоченным начальным состоянием МК когерентности ЯМР возникают быстрее, 
+чем в МК эксперименте ЯМР с начальным состоянием теплового равновесия в сильном внешнем магнитном поле.
+Данное наблюдение является важным в области исследований многоспиновой запутанности, поскольку они используют расчеты второго момента распределения МК когерентностей ЯМР. 
+Также оно является значительным в области исследований распространения корреляции~\cite{Baugh_2001,Baum_1986,S_nchez_2014,Munowitz_1987} и локализации~\cite{Alvarez_2015,Wei_2018}.
+В действительности, скорость распространения может быть описана с помощью вне временных упорядоченных корреляций, которые связаны с распределением МК когерентностей ЯМР.
 
-The present paper investigates many-spin entanglement using the MQ NMR spectrum of spin-carrying atoms (molecules) in a nanopore when the system is prepared in a dipolar ordered state.
-In Sec.~\ref{sec:2}, the theory of MQ NMR dynamics at a low Zeeman temperature and a high dipolar temperature is developed.
-An analytical solution for the MQ NMR dynamics of a three-spin system is obtained at such temperatures in Sec.~\ref{sec:3}.
-The second moment of the MQ NMR spectrum as a measure of many-spin entanglement is considered in Sec.~\ref{sec:4}.
-The dependence of many-spin entanglement on the dipolar temperature and the number of the spins in the system is investigated in Sec.~\ref{sec:5}.
-We briefly summarize our results in concluding Sec.~\ref{sec:6}.
-In the Appendix, we show that the two-pulse Broekaert-Jeener sequence can be used in the case when the Zeeman temperature is low and the dipole one is high.
+В данной статье исследуется многоспиновая запутанность с использованием спектра МК ЯМР спин-несущих атомов (молекул) в нанопоре, когда система подготовлена в диполярно упорядоченном состоянии.
+В разделе~\ref{sec:2} описана разработанная теория МК динамики ЯМР при низкой зеемановской температуре и высокой дипольной температуре.
+Аналитическое решение для МК динамики ЯМР трехспиновой системы получено при таких же температурах и описано в разеделе~\ref{sec:3}.
+Второй момент спектра МК ЯМР в качесвте меры многоспиновой запутанности рассматривается в разделе~\ref{sec:4}.
+В разделе~\ref{sec:5} исследуется зависимость многоспиновой запутанности от дипольной температуры и числа спинов в системе.
+Краткое изложение всех результатов приводится в разделе~\ref{sec:6}.
+В Приложении показано, что двухимпульсная последовательность Брукерта-Джинера может быть использована в случае, когда зеемановская температура низкая, а дипольная - высокая.
 
-\section{Theory of MQ NMR dynamics in a nanopore at a low Zeeman temperature and a high dipolar temperature}
+\section{Теория МК динамики ЯМР в нанопоре при низкой зеемановской температуре и высокой диполярной}
 \label{sec:2}
 
-MQ NMR dynamics in a nanopore is governed by the Hamiltonian~\cite{Doronin_2019,Doronin_2009} 
+МК динамика ЯМР в нанопоре определяется гамильтонианом~\cite{Doronin_2019,Doronin_2009} 
 %
@@
 %
-where 
+где 
 %
@@
 %
-$N$ is the number of the spins in the nanopore, $I^{\pm}_{j}$ are the raising or lowering operators of spin $j$, and $D$ is the dipolar coupling constant averaged by the fast molecular diffusion of spin-carrying atoms (molecules) in the nanopore.
-We emphasize that the dipolar coupling constant $D$ is the same for all pairs of interacting spins in the nanopore~\cite{Doronin_2019,Doronin_2009}.
-The density matrix $\rho(\tau)$ on the preparation period of the MQ NMR experiment~\cite{Baum_1985} can be obtained from the Liouville evolution equation~\cite{Goldman_1970,Abragam_1982} 
+$N$ - число спинов в нанопоре, $I^{\pm}_{j}$ - повышающие или понижающие операторы спина $j$, $D$ - константа диполярной связи, усредненная по быстрой молекулярной диффузии спин-несущих атомов (молекул) в нанопоре.
+Подчеркнем, что константа диполярной связи $D$ одинакова для всех пар взаимодействующих спинов в нанопоре~\cite{Doronin_2019,Doronin_2009}.
+Матрица плотности $\rho(\tau)$ на время подготовки МК эксперимента ЯМР~\cite{Baum_1985} может быть получена из эволюционного уравнения Лиувилля~\cite{Goldman_1970,Abragam_1982} 
 %
@@
 %
-with the initial thermodynamic equilibrium density matrix 
+с начальной термодинамической матрицей равновесной плотности
 %
@@
 %
-where 
-$Z = \mathrm{Tr} \left\{ e^{\frac{\hslash \omega}{k} \alpha_\mathrm{z} I_\mathrm{z} + \frac{\hslash  }{k} \beta_\mathrm{d} H_\mathrm{dz}} \right\}$ is the partition function, 
-$\hslash$ and $k$ are the Plank and Boltzmann constants, 
-$\omega_{0}$  is the Larmor frequency , $I_\mathrm{z}$ is the operator of the projection of the total spin angular momentum on the z-axis, 
-which is directed along the strong external magnetic field,  
-$H_\mathrm{dz}$ is the secular part of the dipole-dipole interaction~(DDI) Hamiltonian in a strong external magnetic field, and $\alpha_\mathrm{z}$, $\beta_\mathrm{d}$ are the inverse Zeeman and dipolar temperatures.
-We will consider the case when the Zeeman temperature is low $({\frac{\hslash \omega}{k} \alpha_\mathrm{z}}\gg 1)$ 
-and the dipolar temperature is high $\left( \frac{\hslash{D}}{k}\beta_\mathrm{d} \ll 1\right)$.
-For concreteness, we suppose that $\omega_{0} = 2\pi \cdot 500 \cdot 10^{6}$~s$^{-1}$ and $D = 2\pi \cdot 10^{4}$~s$^{-1}$.
-In the Appendix, we prove that the two-pulse Broekaert-Jeener sequence~\cite{Goldman_1970,Jeener_1967} results in the dipolar ordered state even at a low Zeeman temperature.
-The adiabatic demagnetization~\cite{Goldman_1970,Slichter_1961} is the second method of preparing a system in the dipolar ordered state.
-Using those methods, we can obtain the system in the thermodynamic equilibrium state with the density matrix
+где 
+$Z = \mathrm{Tr} \left\{ e^{\frac{\hslash \omega}{k} \alpha_\mathrm{z} I_\mathrm{z} + \frac{\hslash  }{k} \beta_\mathrm{d} H_\mathrm{dz}} \right\}$ - функция разделения, 
+$\hslash$ и $k$ - константы Планка и Больцмана, 
+$\omega_{0}$ - частота Лармора , $I_\mathrm{z}$ является оператором проекции полного углового момента вращения на ось z, 
+который направлен вдоль сильного внешнего магнитного поля,  
+$H_\mathrm{dz}$ является секулярной частью гамильтониана диполь-дипольного взаимодействия~(DDI) в сильном внешнем магнитном поле, и $\alpha_\mathrm{z}$, $\beta_\mathrm{d}$ являются обратными зеемановскими и дипольными температурами.
+Мы рассмотрим случай, когда температура Зеемана является низкой $({\frac{\hslash \omega}{k} \alpha_\mathrm{z}}\gg 1)$ 
+, а диполярная высокой $\left( \frac{\hslash{D}}{k}\beta_\mathrm{d} \ll 1\right)$.
+Мы предполагаем, что $\omega_{0} = 2\pi \cdot 500 \cdot 10^{6}$~s$^{-1}$ и $D = 2\pi \cdot 10^{4}$~s$^{-1}$.
+В приложении мы доказываем, что двухимпульсная последовательность Брукерта-Джинера~\cite{Goldman_1970,Jeener_1967} приводит к диполярному упорядоченному состоянию даже при низкой зеемановской температуре.
+Адиабатическое размагничивание~\cite{Goldman_1970,Slichter_1961} является вторым методом подготовки системы в диполярном упорядоченном состоянии.
+Используя эти методы, мы можем получить систему в состоянии термодинамического равновесия с матрицей плотности
 %
@@
 %
-where the partition function
+где функция разделения
 %
@@
 %
-MQ NMR dynamics in the nanopore will be investigated on the basis of Eq.~(\ref{eq:3}) with the initial state of Eq.~(\ref{eq:5}).
-It is also significant that the Hamiltonian $H_{dz}$ is partially averaged by the fast molecular diffusion in the nanopore and the averaged Hamiltonian can be written as \cite{Fel_dman_2004,Doronin_2011}
+МК динамика ЯМР в нанопоре будет исследована на основе уравнения~(\ref{eq:3}) с начальным состоянием уравнения~(\ref{eq:5}).
+Также важно отметить, что гамильтониан $H_{dz}$ частично усредняется быстрой молекулярной диффузией в нанопоре, а усредненный гамильтониан можно записать как \cite{Fel_dman_2004,Doronin_2011}
 %
@@
 %
-where $I^{2}$ is the square of the spin angular momentum.
+где $I^{2}$ - квадрат углового момента вращения.
 
-Let   $G(\tau,\phi)$  be the signal after the preparation, evolution and mixing periods of the MQ NMR experiment~\cite{Baum_1985}, averaged over the equilibrium density matrix.
-$G(\tau,\phi)$ can be written as~\cite{Doronin_2019}
+Пусть $G(\tau,\phi)$ будет сигналом после периодов подготовки, эволюции и смешивания в МК эксперименте ЯМР~\cite{Baum_1985}, усредненном по матрице равновесной плотности.
+$G(\tau,\phi)$ может записать как~\cite{Doronin_2019}
 %
@@
 %
-where
+где
 %
@@
 %
-is the solution of Eq.~(\ref{eq:3}) at the initial condition of Eq.~(\ref{eq:5}).
-It is convenient to expand the spin density matrix, $\rho(\tau)$, in series as
+является решением уравнения~(\ref{eq:3}) при начальном условии уравнения~(\ref{eq:5}).
+Матрица спиновой плотности $\rho(\tau)$ раскладывается в ряд как
 %
@@
 %
-where $\rho_{n}(\tau)$ is the contribution to $\rho(\tau)$ from the MQ coherence of the $n$-th order~\cite{Fel_dman_1996}.
-Then the function $G(\tau,\phi)$ of Eq.~(\ref{eq:8}) can be rewritten as 
+где $\rho_{n}(\tau)$ - вклад в $\rho(\tau)$ из МК когерентности $n$-го порядка~\cite{Fel_dman_1996}.
+ТОгда функция $G(\tau,\phi)$ уравнения ~(\ref{eq:8}) может быть переписана как
 %
@@
 %
-where we took into account that
+где мы учитываем, что
 %
@@
 %
-It is necessary for further calculations to introduce the normalized intensities $J_{n}(\tau)$ $(n=0, \pm 2, \pm 4, \cdots)$ of the MQ NMR coherences
+Для дальнейших расчетов необходимо ввести нормированные интенсивности $J_{n}(\tau)$ $(n=0, \pm 2, \pm 4, \cdots)$ МК когерентностей ЯМР
 %
@@
 %
-Using Eqs.~(\ref{eq:9}),~(\ref{eq:10}) one can verity that 
+Используя уравнения ~(\ref{eq:9}),~(\ref{eq:10}) определим, что
 %
@@
 %
-One can conclude from Eq.~(\ref{eq:14}) that the sum of the MQ NMR coherences is conserved on the preparation period of the MQ NMR experiment~\cite{Baum_1985}.
+Из уравнения~(\ref{eq:14} можно сделать вывод, что сумма МК когерентнойстей ЯМР сохраняется на период МК эксперимента ЯМР~\cite{Baum_1985}.
 
-The basis consisting of the eigenstates of the operator $I_\mathrm{z}$ (dubbed the multiplicative basis) is widely used for numerical calculations of MQ NMR dynamics~\cite{Zhang_2009}.
-Due to the rapid expansion of the Hilbert space with the growth of the number of spins such calculations are possible only for systems with a small number of spins.
-That approach is not suitable for investigations of many-spin entanglement.
-Since the Hamiltonian $H_{MQ}$ of Eq.~(\ref{eq:1}) commutes with the square of the total spin angular momentum $\hat I^2$, 
-it is possible to use the basis consisting of the common eigenstates of $\hat I^2$ and $I_\mathrm{z}$ in order to study MQ NMR dynamics as was done in Ref.~\cite{Doronin_2009,Doronin_2011,Doronin_2019}.
-In this basis, the Hamiltonian $H_{MQ}$ and the initial density matrix of Eq.~(\ref{eq:5}) (see also Eq.~(\ref{eq:7})) consist of blocks, corresponding to different values of the spin angular momentum~\cite{Doronin_2009}.
-Then the investigation of MQ NMR dynamics can be reduced to solving a set of problems of lower dimensions.
+Базис, состоящий из собственных состояний оператора $I_\mathrm{z}$ (названный мультипликативным базисом), широко используется для численных расчетов МК динамики ЯМР~\cite{Zhang_2009}.
+В связи с быстрым расширением гильбертова пространства с ростом числа спинов такие вычисления возможны только для систем с небольшим числом спинов.
+Такой подход не подходит для исследований многоспиновой запутанности.
+Поскольку гамильтониан $H_{MQ}$ уравнения ~(\ref{eq:1}) коммутирует с квадратом полного углового момента спина $\hat I^2$, 
+можно использовать базис, состоящий из общих собственных состояний $\hat I^2$ и $I_\mathrm{z}$ для изучения МК динамики ЯМР, как это было сделано в статьях ~\cite{Doronin_2009,Doronin_2011,Doronin_2019}.
+В этом базисе гамильтониан $H_{MQ}$ и исходная матрица плотности уравнения~(\ref{eq:5}) (см.
+также уравнение~(\ref{eq:7})) состоят из блоков, соответствующих различным значениям углового момента спина~\cite{Doronin_2009}.
+Тогда исследование МК динамики ЯМР может быть сведено к решению ряда задач меньших размеров.
 
-Since the Hamiltonian $H_{MQ}$ of Eq.~(\ref{eq:1}) commutes with the operator $e^{i\pi I_\mathrm{z}}$, the $2^N \times 2^N$ Hamiltonian matrix reduces to two $2^{N-1} \times 2^{N-1}$ submatrices~\cite{Doronin_2009}.
-For odd $N$, both submatrices give the same contribution to the MQ NMR coherences, and one should solve the problem using only one $2^{N-1} \times 2^{N-1}$ submatrix and double the obtained intensities.
-In our calculations, we take only odd numbers of spins.
-Using this method, one can investigate MQ NMR dynamics in systems consisting of hundreds spins.
+Поскольку гамильтониан $H_{MQ}$ уравнения~(\ref{eq:1}) коммутирует с оператором $e^{i\pi I_\mathrm{z}}$, то $2^N \times 2^N$ гамильтонова матрица сводится к двум подматрицам $2^{N-1} \times 2^{N-1}$ подматрицам~\cite{Doronin_2009}.
+Для нечетных $N$ обе подматрицы вносят одинаковый вклад в МК когерентности ЯМР, и нужно решить проблему, используя только одну подматрицу $2^{N-1} \times 2^{N-1}$, и удвоить полученные интенсивности.
+В наших расчетах мы берем только нечетные числа спинов.
+Используя этот метод, можно исследовать МК динамику ЯМР в системах, состоящих и сотен спинов.
 
-\section{Analytical solution for MQ NMR dynamics of a three-spin system in a nanopore in a dipolar ordered state}
+\section{Аналитическое решение для МК динамики ЯМР трехспиновой системы в нанопоре в диполярном упорядоченном состоянии}
 \label{sec:3}
@@
 	\caption{
-	    Intensities of MQ NRM coherenes $J_{n}$ ($n=0, 2$) in a nanopore with $N=3$.
+	    Интенсивность МК когерентности ЯМР $J_{n}$ ($n=0, 2$) в нанопоре с $N=3$.
 	}
@@
 
-Obtaining the exact solution for MQ NMR dynamics of a three-spin system in a dipolar ordered state in a nanopore is similar to the problem considered in Ref.~\cite{Doronin_2019} for the initial thermodynamic equilibrium in a strong external magnetic field.
-Here we do not use the high temperature approximation~\cite{Goldman_1970}.
+Проблема получения точного решения МК динамики ЯМР трехспиновой системы в диполярно упорядоченном состоянии в нанопоре аналогична проблеме, рассмотренной в ~\cite{Doronin_2019} для начального термодинамического равновесия в сильном внешнем магнитном поле.
+В работе мы не используем высокотемпературное приближение~\cite{Goldman_1970}.
 
-The Hamiltonian $H_{MQ}$ of Eq.~(\ref{eq:1}) consists here of two blocks for the two possible values of the spin angular momentum $(I^2 = S(S+1),  \quad S=3/2,1/2)$.
-Those blocks and the corresponding eigenvalues and eigenstates are given in Ref.~\cite{Doronin_2019}.
-The density matrix of the system consists also of two blocks $\rho^{3/2}(\tau)$, $\rho^{1/2}(\tau)$, and 
+Гамильтониан $H_{MQ}$ уравнения ~(\ref{eq:1}) состоит из двух блоков для двух возможных значений углового момента спина $(I^2 = S(S+1),  \quad S=3/2,1/2)$.
+Эти блоки и соответсвующие им собственные значения и собственные состояния приведены в ~\cite{Doronin_2019}.
+Матрица плотности системы также состоит из двух блоков $\rho^{3/2}(\tau)$, $\rho^{1/2}(\tau)$, и
 %
@@
 %
-where $b = \dfrac{\hslash D}{k\mathrm{T}}$and $T$ is the temperature.
-After simple calculations one can obtain the density matrices $\rho^{3/2}(\tau)$ and $\rho^{1/2}(\tau)$, 
-which allow us to find the intensities of the MQ NMR coherences.
+где $b = \dfrac{\hslash D}{k\mathrm{T}}$ и $T$ - температура.
+Простыми вычисленимий можно получить матрицы плотности $\rho^{3/2}(\tau)$ и $\rho^{1/2}(\tau)$,
+которые позволяют нам найти интенсивности МК когерентности ЯМР.
 
-Only the MQ NMR coherences of the zeroth and plus/minus second orders appear in the considered systems. 
-The intensities of these coherences are
+В рассматриваемых системах появляются только МК когерентности ЯМР нулевых и плюс/минус вторых порядков.
+Интенсивность этих когерентностей
 %
@@
 %
-The sum of the intensities of Eq.~(\ref{eq:16}) equals one in accordance with Eq.~(\ref{eq:14}).
-The dependencies of the calculated intensities $J_{n}(\tau)$ $(n=0,2)$ on the evolution time are shown in Fig.~(\ref{fig:1}).
+Сумма интенсивностей уравнения ~(\ref{eq:16}) равна единице в соответсвии с уравнением ~(\ref{eq:14}).
+Зависимости рассчитанных интенсивностей $J_{n}(\tau)$ $(n=0,2)$ от времени эволюции показаны на рисунке ~(\ref{fig:1}).
 
-\section{Second moment of the MQ NMR spectrum as a measure of many-spin entanglement}
+\section{Второй момент спектра МК ЯМР как мера многоспиновой запутанности}
 \label{sec:4}
 
-The expression~(\ref{eq:8}) for the MQ NMR signal $G(\tau,\phi)$ can be expanded in series in the phase increment $\phi$:
+Выражение ~(\ref{eq:8}) для МК сигнала ЯМР $G(\tau,\phi)$ может быть последовательно расширено с приращением фазы $\phi$:
 %
@@
 %
-It is possible to prove~\cite{Girolami_2017} that the quantum Fisher information $F_\mathrm{Q}(\rho,I_\mathrm{z})$~\cite{Helstrom_1976}
+Можно доказать~\cite{Girolami_2017}, что квантовая информация Фишера $F_\mathrm{Q}(\rho,I_\mathrm{z})$~\cite{Helstrom_1976}
 %
@@
 %
-At the same time, it is easy to verify that $2 \mathrm{Tr} \left\{ \rho^2(\tau) I_\mathrm{z}^2 - \left( \rho(\tau) I_\mathrm{z} \right)^2 \right\}$ equals the second moment $M_2$ of the distribution of the intensities of the MQ NMR coherences~\cite{Khitrin_1997}
+В то же время легко проверить что уравнение $2 \mathrm{Tr} \left\{ \rho^2(\tau) I_\mathrm{z}^2 - \left( \rho(\tau) I_\mathrm{z} \right)^2 \right\}$ равно второму моменту $M_2$ распределения интенсивнсти МК когерентностей ЯМР~\cite{Khitrin_1997}
 %
@@
 %
-where $J_n(\tau)$ ($n=0,\pm 2, \pm 4, \cdots$) is determined by Eq.~(\ref{eq:13}).
-Thus, the second moment of the MQ NMR spectrum provides a lower bound on the quantum Fisher information $F_\mathrm{Q}(\rho,I_\mathrm{z})$.
-It was also shown~\cite{T_th_2014,Pezz__2018} that if
+гле $J_n(\tau)$ ($n=0,\pm 2, \pm 4, \cdots$) определяется уравнением ~(\ref{eq:13}).
+Таким образом второй момент спектра МК ЯМР обеспечивает нижнюю границу квантовой информации Фишера $F_\mathrm{Q}(\rho,I_\mathrm{z})$.
+Также показано~\cite{T_th_2014,Pezz__2018}, что, если
 %
@@
 %
-where $n$ is the integer part of ${N/k}$, then the system with the density matrix $\rho(\tau)$ is $(k+1)$-spin entangled~\cite{Pezz__2009,Hyllus_2012,T_th_2012}.
-The results of the numerical analysis of many-spin entanglement in the system of spin-carrying molecules (atoms) initially prepared in the dipolar ordered state are presented in the following section.
+где $n$ - целая часть ${N/k}$, то система с матрицей плотности $\rho(\tau)$ $(k+1)$-спин запутанная~\cite{Pezz__2009,Hyllus_2012,T_th_2012}.
+Результаты численного анализа многоспиновой запутанности в системе спин-несущих молекул (атомов), первоначально приготовленных в диполярном упорядоченном состоянии, представлены в следующем разделе.
 

### 2020-05-28 maniscript_rus.tex
Updates from Overleaf

@@
 
-\section{Introduction}
+\section{Введение}
 \label{sec:1}
@@
 Термически равновесное начальное состояние системы определялось односпиновым зеемановским взаимодействием с внешним магнитным полем~\cite{Doronin_2007a}.
-Также возможно исследовать многоспиновую запутанность, когда та же самая система первоначально подготовлена в диполярном упорядоченном состоянии~\cite{Goldman_1970}, используя либо метод адиабатического размагничивания во вращающейся системе отсчета~\cite{Goldman_1970, Slichter_1961} , либо двухимпульную последовательность Брукерта-Джинера~\cite{Goldman_1970, Jeener_1967}.
+Также возможно исследовать многоспиновую запутанность, когда та же самая система первоначально подготовлена в диполярном упорядоченном состоянии~\cite{Goldman_1970}, используя либо метод адиабатического размагничивания во вращающейся системе отсчета~\cite{Goldman_1970, Slichter_1961}, либо двухимпульную последовательность Брукерта-Джинера~\cite{Goldman_1970, Jeener_1967}.
 Динамика МК ЯМР с этим начальным состоянием моделировалась как в малых спиновых системах~\cite{Doronin_2007a, Doronin_2007b}, так и в системе, состоящей из 200-600 спин-несущих молекул (атомов), заполняющих нанопоры ~\cite{Doronin_2011}.
@@
 
-\section{Numerical analysis of many-spin entanglement at different temperatures and numbers of spins in the system}
+\section{Численный анализ многоспиновой запутанности при различных температурах и различном числе спинов в системе}
 \label{sec:5}
@@
 	\caption{
-	    The dependence of the lower bound on the quantum Fisher Information $F_\mathrm{Q} = 2 M_{2}$ 
-	    on the dimensionless time $D\tau$ at $N=101$.
-	    a) $T=6\cdot10^{-4}$~K, the inequality~(\ref{eq:20}) yields the region of pair entanglement (k+1=2), the region is above the horizontal line; 
-	    b) $T=3.2\cdot10^{-4}$~K, the region of the many-spin entanglement is a strip bounded by the horizontal lines with~$k=19$~and~$k=46$; 
-	    c) $T = 1.6\cdot10^{_4}$~K, the horizontal lines ($k=18$ and k=$86$) bound the strip with many-spin entanglement;
-	    d) $T=4.8\cdot10^{-5}$~K, entangled clusters with $10-92$ spins emerge.
+	    Зависимость нижней границы от квантовой информации Фишера $F_\mathrm{Q} = 2 M_{2}$ 
+	    на безразмерном времени $D\tau$ при $N=101$.
+	    a) $T=6\cdot10^{-4}$~K, неравенство~(\ref{eq:20}) определяет область запутывания пары (k+1=2), область выше горизонтальной линии; 
+	    b) $T=3.2\cdot10^{-4}$~K, область многоспиновой запутанности представляет собой полосу, ограниченную горизонтальными линиями с ~$k=19$~и~$k=46$; 
+	    c) $T = 1.6\cdot10^{_4}$~K, горизонтальные линии ($k=18$ и $k=86$) связывают полосу с многоспиновым переплетением;
+	    d) $T=4.8\cdot10^{-5}$~K, появляются запутанные кластеры с $10-92$ спинами.
 	}
@@
 
-The considered model of the spin-carrying molecules (atoms) in a nanopore in the dipolar ordered states expands possibilities of the investigation of many-spin entanglement in comparison with the related model~\cite{Doronin_2019},
-in which the system was initially in the thermodynamic equilibrium in a strong external magnetic field.
-The model~\cite{Doronin_2019}  is not useful for the investigation of the time-evolution of the system
-because the stationary distribution of MQ NMR coherences establishes very quickly~\cite{Doronin_2009}.
-Many-spin entanglement changes with the temperature in a very narrow temperature interval in the model~\cite{Doronin_2019}.
-For example, all spins are entangled in the system consisting of 201 spins at the temperature $T=6.856\cdot10^{-3}$~K~\cite{Doronin_2019}.
+Рассматриваемая модель спин-несущих молекул (атомов) в нанопоре в диполярно упорядоченных состояниях расширяет возможности исследования многоспинойо запутанности по сравнению с родственной моделью~\cite{Doronin_2019},
+в которой система изначально находилась в термодинамическом равновесии в сильном внешнем магнитном поле.
+Модель~\cite{Doronin_2019} не применима для исследования эволюции системы во времени,
+потому что распределение МК когерентностей ЯМР быстро становится стационарным~\cite{Doronin_2009}.
+Многоспиновая запутанность изменяется с температурой в очень узком температурном интервале в модели~\cite{Doronin_2019}.
+Например, все спины запутаны в системе, состоящей из 201 спина при температуре $T=6.856\cdot10^{-3}$~K~\cite{Doronin_2019}.
 
-The time dependence of the quantum Fisher information in the system consisting of 101 spins is presented in Fig.~(\ref{fig:2}) at different temperatures. 
-One can see from Fig.~(\ref{fig:2}a) that only pair entanglement exists at the temperature $T=6\cdot10^{-4}$~K.
-At the temperature $T=3.2\cdot10^{-4}$, one can see a strip in Fig.~(\ref{fig:2}b), in which the inequality~(\ref{eq:20}) can be satisfied when $19 \leq k \leq 46$.
-Thus, there is many-spin entanglement in spin clusters consisting of 20-47 spins at the temperature $3.2\cdot10^{-4}$~K.
-When the temperature decreases, the width of the strip, in which many-spin entanglement exists, increases. 
-At the temperature $T=1.6\cdot10^{-4}$~K (Fig.~(\ref{fig:2}c)), clusters of 19-87 entangled spins emerge, and at the temperature $T=4.8\cdot10^{-5}$~K (Fig.~(\ref{fig:2}d)), we have 11-92 entangled spins.
+Временная зависимость квантовой информации Фишера в системе, состоящей из 101 спина, представлена на Рис.~(\ref{fig:2}) при различных температурах.
+Из Рис.~(\ref{fig:2}a) видно, что при температуре $T=6\cdot10^{-4}$~K существует только парная запутанность.
+При температуре $T=3.2\cdot10^{-4}$ на Рис.~(\ref{fig:2}b) видна полоса, в которой неравенство~(\ref{eq:20}) может быть решено, когда $19 \leq k \leq 46$.
+Таким образом, существует многоспиновая запутанность в спиновых кластерах, состоящих из 20-47 спинов, при температуре $3.2\cdot10^{-4}$~K.
+Когда температура снижается, ширина полосы, в которой существует многоспиновая запутанность, увеличивается.
+При температуре $T=1.6\cdot10^{-4}$~K (Рис.~(\ref{fig:2}c)), появляются кластеры из 19-87 запутанных спинов, а при температуре $T=4.8\cdot10^{-5}$~K (Рис.~(\ref{fig:2}d)), наблюдаются 11-92 запутанных спина.
 
@@
 	\caption{
-	    The dependence of the maximal number of the entangled spins,
-	    averaged over the evolution time $(0 \leq D\tau \leq 3)$, 
-	    on the temperature at a) $N=51$; b) $N=75$; c) $N=101$.
+	    Зависимость максимального количества запутанных спинов,
+	    усредненная по времени эволюции $(0 \leq D\tau \leq 3)$, 
+	    по теспературе при a) $N=51$; b) $N=75$; c) $N=101$.
 	}
@@
 
-The dependence of the average of the maximal number of the entangled spins over the evolution time $({0}\leq \mathrm{D}\tau\leq{3})$ on the temperature at different numbers of the spins in a nanopore is presented in Fig.~(\ref{fig:3}).
-The maximal number of the entangled spins decreases when the temperature increases. 
-The maximal number of the entangled spins increases when the number of the spins in the nanopore increases, because the system in the nanopore gets denser.
+Зависимость среднего максимального числа запутанных спинов за время эволюции $({0}\leq \mathrm{D}\tau\leq{3})$ от температуры при разных числах спинов в нанопоре представлена на Рис.~(\ref{fig:3}).
+Максимальное количество запутанных спинов уменьшается при повышении температуры.
+Максимальное количество запутанных спинов увеличивается, когда увеличивается число спинов в нанопоре, потому что система в нанопоре становится плотнее.
 
-\section{Conclusion}
+\section{Выводы}
 \label{sec:6}
 
-We investigated many-spin entanglement in a system of spin-carrying molecules (atoms) filling a non-spherical nanopore in the conditions of the MQ NMR spectroscopy.
-The spins are in the dipolar ordered state initially.
-We found the dependence of many-spin entanglement on the temperature and the number of the spins in the nanopore.
+Была исследована многоспиновая запутанность в системе спин-несущих молекул (атомов), заполняющих несферические нанопоры в условиях эксперимента МК спектроскопии ЯМР.
+Спины изначально находились в диполярно упорядоченном состоянии.
+Найдена зависимость многоспиновой запутанности от температуры и количества спинов в нанопоре.
 
-We believe that the MQ NMR spectroscopy is a subtle and useful method for the investigation of different quantum information problems.
-In particularly, it is a very effective method for the exploration of quantum entanglement.
+Мы считаем, что МК спектроскопия ЯМР является утонченным и полезным методом для исследования различных проблем квантовой информации.
+В частности, это очень эффективный метод исследования квантовой запутанности.
 
 \section{Acknowledgements}
-This work was performed as a part of a state task, State Registration No. 0089-2019-0002. 
-This work was partially supported by the Russian Foundation for Basic Research (Grants Nos. 20-03-00147, 19-32-80004). 
-I.L. acknowledges support from the Advancement of Theoretical Physics and Mathematics BASIS No. 19-1-5-130-1.
+Эта работа выполнена в рамках государственного задания, госрегистрации № 0089-2019-0002. 
+Работа частично поддержана Российским фондом фундаментальных исследований (гранты № 20-03-00147, 19-32-80004).
+И.Л. поддержан фондом Базис грантом Основы теоретической физики и математики №19-1-5-130-1.
 
 \appendix
-\section{The two-pulse Broekaert-Jeener experiment at a low Zeeman temperature and a high dipolar temperature.}
+\section{Двухимпульсный эксперимент Брукерта-Джинера при низкой зеемановской температуре и высокой дипольной температуре.}
 
-Initially the system is in the thermodynamic equilibrium state in the strong external magnetic field with the density matrix
+Изначально система находится в состоянии термодинамического равновесия в сильном внешнем магнитном поле с матрицей плотности
 %
@@
 %
-After the first resonance rf x-pulse, one has
+После первого резонансного Х-импульса
 %
@@
 %
-Then the system evolves freely during the time $\tau$, 
-and one applies the second resonance y-pulse rotating spins by angle $\theta$ around the y-axis of the RRF.
-As a result, one obtains that
+Тогда система свободно эволюционирует в течение времени $\tau$,
+и применяется второй резонансный импульс, который поворачивает спины на угол $\theta$ вокруг оси y вращающейся системы координат.
+В результате получаем, что
 \begin{equation}
@@
 %
-After the time $T_2$ ($T_2$ is the spin relaxation time \cite{Goldman_1970}) the system achieves the thermodynamic equilibrium state
+По истечении времени $T_2$ ($T_2$ - время спиновой релаксации \cite{Goldman_1970}) система достигает состояния термодинамического равновесия
 \begin{equation}
@@
 %
-where $\alpha$ and $\beta$ are the inverse Zeeman and dipolar temperatures.
-It is evident that the system has a single equilibrium state 
-and there is a unique choice of the temperatures $\alpha$ and $\beta$ 
-that is consistent with the conservation laws.
-Those temperatures can be obtained from the conservation laws
+где $\alpha$ и $\beta$ - это обратные Зеемановские и дипольные температуры.
+Очевидно, что система имеет одно равновесное состояние 
+и существуют уникальные температуры $\alpha$ и $\beta$,
+что согласуется с закона сохранения.
+Данные температуры могут быть получены из законов сохранения
 \begin{align}
@@
 %
-One can rewrite $\mathrm{Tr} \left\{ I_\mathrm{z} \sigma'(\tau) \right\}$ as 
+Можно переписать $\mathrm{Tr} \left\{ I_\mathrm{z} \sigma'(\tau) \right\}$ как
 %
@@
 %
-In~(\ref{eq:a7}) we took into account that $\left[ e^{-i \pi \sy}, \hdz \right] = 0$.
-Since we consider the case of a high dipolar temperature, it is possible for rewrite~(\ref{eq:a5}) as
+В~(\ref{eq:a7}) было учтено, что $\left[ e^{-i \pi \sy}, \hdz \right] = 0$.
+Поскольку мы рассматриваем случай высокой дипольной температуры, можно переписать~(\ref{eq:a5}) как 
 \begin{equation}
@@
 %
-Notice that $\tr{\sz} = \tr{\sz\hdz} = 0$. It means that $\alpha = 0$ satisfies Eq.~(\ref{eq:5}). 
-Thus, we obtain the dipolar ordered state in the considered case.
+Заметим, что $\tr{\sz} = \tr{\sz\hdz} = 0$. В таком случае $\alpha = 0$ удовлетворяет уравнению ~(\ref{eq:5}). 
+Таким образом, в рассматриваемом случае мы получаем дипольное упорядоченное состояние.
 

### 2020-05-28 manuscript.tex
Add manuscript translation to Russian.
Updates from Overleaf

--- 2020-05-17 manuscript.tex
@@
 	    b) $T=3.2\cdot10^{-4}$~K, the region of the many-spin entanglement is a strip bounded by the horizontal lines with~$k=19$~and~$k=46$; 
-	    c) $T = 1.6\cdot10^{_4}$~K, the horizontal lines ($k=18$ and k=$86$) bound the strip with many-spin entanglement;
+	    c) $T = 1.6\cdot10^{_4}$~K, the horizontal lines ($k=18$ and $k=86$) bound the strip with many-spin entanglement;
 	    d) $T=4.8\cdot10^{-5}$~K, entangled clusters with $10-92$ spins emerge.

### 2020-05-28 manuscript.tex

--- 2020-05-17 manuscript.tex
@@
-\documentclass[review]{elsarticle}
-
 \usepackage{amsmath}
@@
 	    b) $T=3.2\cdot10^{-4}$~K, the region of the many-spin entanglement is a strip bounded by the horizontal lines with~$k=19$~and~$k=46$;
-	    c) $T = 1.6\cdot10^{_4}$~K, the horizontal lines ($k=18$ and k=$86$) bound the strip with many-spin entanglement;
 	    d) $T=4.8\cdot10^{-5}$~K, entangled clusters with $11-92$ spins emerge.
+	    c) $T = 1.6\cdot10^{_4}$~K, the horizontal lines ($k=18$ and $k=86$) bound the strip with many-spin entanglement;
+	    d) $T=4.8\cdot10^{-5}$~K, entangled clusters with $10-92$ spins emerge.
 	}

### 2020-05-28 maniscript_rus.tex
Add JETP style.

@@
-\documentclass[review]{elsarticle}
-\usepackage[english,russian]{babel}
+\documentclass[utf8]{jetp}
 
@@
 
-\usepackage{lineno,hyperref}
+\usepackage{lineno}
 \modulolinenumbers[1]
+\linenumbers
 
@@
 
-\journal{Journal of Magnetic Resonance}
-
-%% `Elsevier LaTeX' style
-%\bibliographystyle{elsarticle-num}
-\bibliographystyle{naturemag}
+\bibliographystyle{unsrt}
 
@@
 
-\begin{frontmatter}
-
 \title{Многоспиновая запутанность в многоквантовом ЯМР с диполярно упорядоченным начальным состоянием}
 
-\author[icp]{Э.~Б.~Фельдман}
-\author[icp,msu]{И.~Д.~Лазарев} %
+\author{И.~Д.}{Лазарев}
+\email{ilia.lazarev@icp.ac.ru}
+\affiliation{Институт проблем химической физики РАН,  \\ Черноголовка, Московская область, Россия 142432}
+\affiliation{Факультет фундаментальной физико-химической инженерии, \\ МГУ GSP-1, Москва, Россия 119991}
 
-\address[icp]{Институт проблем химической физики РАН, \\ Черноголовка, Московская область, Россия 142432}
-\address[msu]{Факультет фундаментальной физико-химической инженерии, МГУ GSP-1, Москва, Россия 119991}
+\author{Э.~Б.}{Фельдман}
+\affiliation{Институт проблем химической физики РАН, \\ Черноголовка, Московская область, Россия 142432}
 
-\begin{abstract}
+\abstract{
 Многоквантовый (МК)  ЯМР с диполярно упорядоченным начальным состоянием открывает новые возможности для изучения многоспиновой запутанности. 
@@
 Многоспиновая запутанность исследуется при различных температурах и различном количестве спинов.
-\end{abstract}
+}
 
-\begin{keyword}
-многоквантовый (МК) ЯМР \sep  
-квантовые корреляции \sep 
-квантовая информация Фишера \sep 
-запутанность, нанопора \sep 
-МК ЯМР когерентность \sep 
-второй момент, температура \sep 
-диполярно упорядоченное состояние \sep 
-двухимпульсная последовательность Брукерта-Джинера
-\end{keyword}
-
-\end{frontmatter}
+% \begin{keyword}
+% многоквантовый (МК) ЯМР \sep  
+% квантовые корреляции \sep 
+% квантовая информация Фишера \sep 
+% запутанность, нанопора \sep 
+% МК ЯМР когерентность \sep 
+% второй момент, температура \sep 
+% диполярно упорядоченное состояние \sep 
+% двухимпульсная последовательность Брукерта-Джинера
+% \end{keyword}
 
 %\linenumbers
+
+\maketitle
 

### 2020-06-03 maniscript_rus.tex
Fix translation

@@
 
-\title{Многоспиновая запутанность в многоквантовом ЯМР с диполярно упорядоченным начальным состоянием}
+\title{Многоспиновая запутанность в многоквантовом~ЯМР~с дипольно упорядоченным начальным состоянием}
 
@@
 \abstract{
-Многоквантовый (МК)  ЯМР с диполярно упорядоченным начальным состоянием открывает новые возможности для изучения многоспиновой запутанности. 
-В данной статье исследуется многоспиновая запутанность в газе спин-несущих молекул (атомов) в нанорезонаторах
-в условиях ЯМР с дипольно упорядоченным начальным состоянием.
-Для оценки количества запутанных спинов используется второй момент распределения интенсивнойстей МК ЯМР-когерентностей, 
+Многоквантовый (МК)~ЯМР~с~дипольно упорядоченным начальным состоянием открывает новые возможности для изучения многоспиновой запутанности.
+В~данной статье исследуется многоспиновая запутанность в~газе спин-несущих молекул (атомов) в нанорезонаторах
+в~условиях~ЯМР~с дипольно упорядоченным начальным состоянием.
+Для~оценки количества запутанных спинов используется второй момент распределения интенсивностей МК~ЯМР~когерентностей,
 который определяет нижнюю границу квантовой информации Фишера.
@@
 % \begin{keyword}
-% многоквантовый (МК) ЯМР \sep  
+% многоквантовый (МК)~ЯМР~\sep
 % квантовые корреляции \sep
@@
 % запутанность, нанопора \sep
-% МК ЯМР когерентность \sep 
+% МК~ЯМР~когерентность \sep
 % второй момент, температура \sep
-% диполярно упорядоченное состояние \sep 
+% дипольно упорядоченное состояние \sep
 % двухимпульсная последовательность Брукерта-Джинера
@@
 
-Запутанность~\cite{Nielsen_2009} является важным понятием квантовой механики. Наличие данного понятия определеяет преимущество квантовых компьютеров перед их классическими аналогами. 
+Запутанность~\cite{Nielsen_2009} является важным понятием квантовой механики.
+Она определеяет преимущество квантовых компьютеров перед их классическими аналогами.
 Продемонстрированное квантовое превосходство программируемого сверхпроводящего процессора~\cite{Arute2019} также связано с понятием запутанности, которое отсутствует в классической физике.
-Среди многочисленных методов исследования запутанности мы сосредоточились на многоквантовом (МК) ЯМР в твердых телах~\cite{Baum_1985}, который широко используется для характеристики запутанности в двоичных системах~\cite{Furman_2008, Furman_2009, Fel_dman_2008, Fel_dman_2012}.
-МК ЯМР-спектроскопия~\cite{Baum_1985} позволяет извлекать информацию о многоспиновой запутанности~\cite{G_rttner_2018} с помощью квантовой информации Фишера~\cite{T_th_2014, Pezz__2018}.
+Среди многочисленных методов исследования запутанности мы сосредоточились на многоквантовом~(МК)~ЯМР в~твердых телах~\cite{Baum_1985}, который широко используется для изучения запутанности в бинарных системах~\cite{Furman_2008, Furman_2009, Fel_dman_2008, Fel_dman_2012}.
+МК~ЯМР~спектроскопия~\cite{Baum_1985} позволяет извлекать информацию о многоспиновой запутанности~\cite{G_rttner_2018} с~помощью квантовой информации Фишера~\cite{T_th_2014, Pezz__2018}.
 
-Квантовая информация Фишера описывает скорость изменения квантовых состояний, определяемых матрицей плотности в ответ на изменение какого-либо параметра.
-В МК спектроскопии ЯМР данный параметр представляет собой приращение фазы между радиочастотными импульсами, облучающими систему в периоды приготовления и смешивания в эксперименте по МК ЯМР~\cite{Baum_1985},
-что приводит к разделению сигналов, соответсвующих МК когерентности ЯМР разных порядков, и позволяет получить полный спектр МК ЯМР. 
+Квантовая информация Фишера описывает скорость изменения квантовых состояний,
+определяемых матрицей плотности в ответ на изменение какого-либо параметра.
+В~МК~спектроскопии~ЯМР~данный параметр представляет собой приращение фазы между радиочастотными импульсами,
+облучающими систему в периоды приготовления и смешивания в МК~ЯМР~эксперименте~\cite{Baum_1985},
+что приводит к разделению сигналов, соответсвующих МК~когерентности~ЯМР разных~порядков,
+и позволяет получить полный спектр МК~ЯМР.
 Приращение фазы пропорционально продолжительности периода эволюции.
-Используя квантовую информацию Фишера~\cite{Liu_2014} для анализа спектра МК ЯМР, можно получить важную информацию о многоспиновой запутанности,
-поскольку сущесвует связь между вторым моментом спектра ~\cite{Khitrin_1997} и квантовой информацией Фишера~\cite{G_rttner_2018,Doronin_2019}.
-Кроме того второй момент спектра МК ЯМР определяет нижнюю границу квантовой информации Фишера~\cite{G_rttner_2018}.
-Это означает, что МК ЯМР-спектроскопия является ценным методом решения квантовых информационных задач.
+Используя квантовую информацию Фишера~\cite{Liu_2014} для анализа спектра МК~ЯМР,
+можно получить важную информацию о многоспиновой запутанности,
+поскольку сущесвует связь между вторым моментом спектра~\cite{Khitrin_1997} и квантовой информацией Фишера~\cite{G_rttner_2018,Doronin_2019}.
+Кроме того второй момент спектра МК~ЯМР~определяет нижнюю границу квантовой информации Фишера~\cite{G_rttner_2018}.
+Это означает, что МК~ЯМР~спектроскопия является ценным методом решения квантовых информационных задач.
 
-Многоспиновая запутанность была исследована~\cite{Doronin_2019} для несферической нанопоры, заполненной газом переносящих спин молекул в сильном внешнем магнитном поле~\cite{Baugh_2001,Doronin_2009}.
+Многоспиновая запутанность была исследована~\cite{Doronin_2019} для несферической нанопоры,
+заполненной газом переносящих спин молекул в сильном внешнем магнитном поле~\cite{Baugh_2001,Doronin_2009}.
 Термически равновесное начальное состояние системы определялось односпиновым зеемановским взаимодействием с внешним магнитным полем~\cite{Doronin_2007a}.
-Также возможно исследовать многоспиновую запутанность, когда та же самая система первоначально подготовлена в диполярном упорядоченном состоянии~\cite{Goldman_1970}, используя либо метод адиабатического размагничивания во вращающейся системе отсчета~\cite{Goldman_1970, Slichter_1961}, либо двухимпульную последовательность Брукерта-Джинера~\cite{Goldman_1970, Jeener_1967}.
-Динамика МК ЯМР с этим начальным состоянием моделировалась как в малых спиновых системах~\cite{Doronin_2007a, Doronin_2007b}, так и в системе, состоящей из 200-600 спин-несущих молекул (атомов), заполняющих нанопоры ~\cite{Doronin_2011}.
+Также возможно исследовать многоспиновую запутанность,
+когда та же самая система первоначально подготовлена в дипольном упорядоченном состоянии~\cite{Goldman_1970},
+используя либо метод адиабатического размагничивания во вращающейся системе отсчета~\cite{Goldman_1970, Slichter_1961},
+либо двухимпульную последовательность Брукерта-Джинера~\cite{Goldman_1970, Jeener_1967}.
+Динамика МК~ЯМР~с этим начальным состоянием моделировалась как в малых спиновых системах~\cite{Doronin_2007a, Doronin_2007b},
+так и в системе, состоящей из 200-600 спин-несущих молекул (атомов), заполняющих нанопоры~\cite{Doronin_2011}.
 Однако подходы, разработанные для этих исследований, ограничены высокими температурами и не могут применяться к многоспиновому запутыванию.
@@
 В настоящей статье мы рассматриваем среднетемпературный случай с низкими зеемановскими и высокими дипольными.
-Магнитное упорядочевание~\cite{Abragam_1982} выходит за рамки данной статьи.
+Магнитное упорядочение~\cite{Abragam_1982} выходит за рамки данной статьи.
 Стоит обратить внимание, что двухимпульсный эксперимент Брукерта-Дженира~\cite{Jeener_1967} был выполнен при высоких температурах.
 В данной статье было доказано, что этот эксперимент~\cite{Jeener_1967} также может выполняться при средних температурах.
-Было показано~\cite{Doronin_2011}, что в МК эксперименте ЯМР с диполярно упорядоченным начальным состоянием МК когерентности ЯМР возникают быстрее, 
-чем в МК эксперименте ЯМР с начальным состоянием теплового равновесия в сильном внешнем магнитном поле.
-Данное наблюдение является важным в области исследований многоспиновой запутанности, поскольку они используют расчеты второго момента распределения МК когерентностей ЯМР. 
+Было показано~\cite{Doronin_2011}, что в МК~эксперименте~ЯМР~с дипольно упорядоченным начальным состоянием МК~когерентности~ЯМР~возникают быстрее,
+чем в МК~эксперименте~ЯМР~с начальным состоянием теплового равновесия в сильном внешнем магнитном поле.
+Данное наблюдение является важным в области исследований многоспиновой запутанности, поскольку они используют расчеты второго момента распределения МК~когерентностей~ЯМР~.
 Также оно является значительным в области исследований распространения корреляции~\cite{Baugh_2001,Baum_1986,S_nchez_2014,Munowitz_1987} и локализации~\cite{Alvarez_2015,Wei_2018}.
-В действительности, скорость распространения может быть описана с помощью вне временных упорядоченных корреляций, которые связаны с распределением МК когерентностей ЯМР.
+В действительности, скорость распространения может быть описана с помощью out-of-time ordered correlations, которые связаны с распределением МК~когерентностей~ЯМР.
 
-В данной статье исследуется многоспиновая запутанность с использованием спектра МК ЯМР спин-несущих атомов (молекул) в нанопоре, когда система подготовлена в диполярно упорядоченном состоянии.
-В разделе~\ref{sec:2} описана разработанная теория МК динамики ЯМР при низкой зеемановской температуре и высокой дипольной температуре.
-Аналитическое решение для МК динамики ЯМР трехспиновой системы получено при таких же температурах и описано в разеделе~\ref{sec:3}.
-Второй момент спектра МК ЯМР в качесвте меры многоспиновой запутанности рассматривается в разделе~\ref{sec:4}.
+В данной статье исследуется многоспиновая запутанность с использованием спектра МК~ЯМР~спин-несущих атомов (молекул) в нанопоре, когда система подготовлена в дипольно упорядоченном состоянии.
+В разделе~\ref{sec:2} описана разработанная теория МК~динамики~ЯМР~при низкой зеемановской температуре и высокой дипольной температуре.
+Аналитическое решение для МК~динамики~ЯМР трехспиновой системы получено при таких же температурах и описано в разеделе~\ref{sec:3}.
+Второй момент спектра~МК~ЯМР~в качесвте меры многоспиновой запутанности рассматривается в разделе~\ref{sec:4}.
 В разделе~\ref{sec:5} исследуется зависимость многоспиновой запутанности от дипольной температуры и числа спинов в системе.
@@
 
-\section{Теория МК динамики ЯМР в нанопоре при низкой зеемановской температуре и высокой диполярной}
+\section{Теория МК~динамики~ЯМР~в нанопоре при низкой зеемановской температуре и высокой дипольной}
 \label{sec:2}
 
-МК динамика ЯМР в нанопоре определяется гамильтонианом~\cite{Doronin_2019,Doronin_2009} 
+МК~динамика~ЯМР~в нанопоре определяется гамильтонианом~\cite{Doronin_2019,Doronin_2009}
 %
@@
 %
-$N$ - число спинов в нанопоре, $I^{\pm}_{j}$ - повышающие или понижающие операторы спина $j$, $D$ - константа диполярной связи, усредненная по быстрой молекулярной диффузии спин-несущих атомов (молекул) в нанопоре.
-Подчеркнем, что константа диполярной связи $D$ одинакова для всех пар взаимодействующих спинов в нанопоре~\cite{Doronin_2019,Doronin_2009}.
-Матрица плотности $\rho(\tau)$ на время подготовки МК эксперимента ЯМР~\cite{Baum_1985} может быть получена из эволюционного уравнения Лиувилля~\cite{Goldman_1970,Abragam_1982} 
+$N$ - число спинов в нанопоре, $I^{\pm}_{j}$ - повышающие или понижающие операторы спина $j$, $D$ - константа дипольной связи, усредненная по быстрой молекулярной диффузии спин-несущих атомов (молекул) в нанопоре.
+Подчеркнем, что константа дипольной связи $D$ одинакова для всех пар взаимодействующих спинов в нанопоре~\cite{Doronin_2019,Doronin_2009}.
+Матрица плотности $\rho(\tau)$ на время подготовки МК~эксперимента~ЯМР~\cite{Baum_1985} может быть получена из эволюционного уравнения Лиувилля~\cite{Goldman_1970,Abragam_1982}
 %
@@
 %
-с начальной термодинамической матрицей равновесной плотности
+с начальной термодинамически равновесной матрицей плотности
 %
@@
 где
-$Z = \mathrm{Tr} \left\{ e^{\frac{\hslash \omega}{k} \alpha_\mathrm{z} I_\mathrm{z} + \frac{\hslash  }{k} \beta_\mathrm{d} H_\mathrm{dz}} \right\}$ - функция разделения, 
+$Z = \mathrm{Tr} \left\{ e^{\frac{\hslash \omega}{k} \alpha_\mathrm{z} I_\mathrm{z} + \frac{\hslash }{k} \beta_\mathrm{d} H_\mathrm{dz}} \right\}$ - статистическая сумма,
 $\hslash$ и $k$ - константы Планка и Больцмана,
-$\omega_{0}$ - частота Лармора , $I_\mathrm{z}$ является оператором проекции полного углового момента вращения на ось z, 
+$\omega_{0}$ - частота Лармора , 
+$I_\mathrm{z}$ является оператором проекции полного углового момента вращения на ось~$z$,
 который направлен вдоль сильного внешнего магнитного поля,
-$H_\mathrm{dz}$ является секулярной частью гамильтониана диполь-дипольного взаимодействия~(DDI) в сильном внешнем магнитном поле, и $\alpha_\mathrm{z}$, $\beta_\mathrm{d}$ являются обратными зеемановскими и дипольными температурами.
-Мы рассмотрим случай, когда температура Зеемана является низкой $({\frac{\hslash \omega}{k} \alpha_\mathrm{z}}\gg 1)$ 
-, а диполярная высокой $\left( \frac{\hslash{D}}{k}\beta_\mathrm{d} \ll 1\right)$.
+$H_\mathrm{dz}$ является секулярной частью гамильтониана диполь-дипольного взаимодействия~(DDI) в сильном внешнем магнитном поле, 
+и $\alpha_\mathrm{z}$, $\beta_\mathrm{d}$ являются обратными зеемановскими и дипольными температурами.
+Мы рассмотрим случай, когда температура Зеемана является низкой $({\frac{\hslash \omega}{k} \alpha_\mathrm{z}}\gg 1)$, 
+а дипольная высокой $\left( \frac{\hslash{D}}{k}\beta_\mathrm{d} \ll 1\right)$.
 Мы предполагаем, что $\omega_{0} = 2\pi \cdot 500 \cdot 10^{6}$~s$^{-1}$ и $D = 2\pi \cdot 10^{4}$~s$^{-1}$.
-В приложении мы доказываем, что двухимпульсная последовательность Брукерта-Джинера~\cite{Goldman_1970,Jeener_1967} приводит к диполярному упорядоченному состоянию даже при низкой зеемановской температуре.
-Адиабатическое размагничивание~\cite{Goldman_1970,Slichter_1961} является вторым методом подготовки системы в диполярном упорядоченном состоянии.
+В приложении мы доказываем, что двухимпульсная последовательность Брукерта-Джинера~\cite{Goldman_1970,Jeener_1967} приводит к дипольному упорядоченному состоянию даже при низкой зеемановской температуре.
+Адиабатическое размагничивание~\cite{Goldman_1970,Slichter_1961} является вторым методом подготовки системы в дипольно упорядоченном состоянии.
 Используя эти методы, мы можем получить систему в состоянии термодинамического равновесия с матрицей плотности
@@
 %
-где функция разделения
+где статистическая сумма
 %
@@
 %
-МК динамика ЯМР в нанопоре будет исследована на основе уравнения~(\ref{eq:3}) с начальным состоянием уравнения~(\ref{eq:5}).
+МК~динамика~ЯМР~в нанопоре будет исследована на основе уравнения~(\ref{eq:3}) с начальным состоянием уравнения~(\ref{eq:5}).
 Также важно отметить, что гамильтониан $H_{dz}$ частично усредняется быстрой молекулярной диффузией в нанопоре, а усредненный гамильтониан можно записать как \cite{Fel_dman_2004,Doronin_2011}
@@
 
-Пусть $G(\tau,\phi)$ будет сигналом после периодов подготовки, эволюции и смешивания в МК эксперименте ЯМР~\cite{Baum_1985}, усредненном по матрице равновесной плотности.
+Пусть $G(\tau,\phi)$ будет сигналом после периодов подготовки, эволюции и смешивания в МК~эксперименте~ЯМР~\cite{Baum_1985}, усредненном по равновесной матрице плотности. 
 $G(\tau,\phi)$ может записать как~\cite{Doronin_2019}
@@
 %
-является решением уравнения~(\ref{eq:3}) при начальном условии уравнения~(\ref{eq:5}).
-Матрица спиновой плотности $\rho(\tau)$ раскладывается в ряд как
+является решением уравнения~(\ref{eq:3}) при начальном условии~(\ref{eq:5}).
+Матрица плотности $\rho(\tau)$ раскладывается в ряд
 %
@@
 %
-где $\rho_{n}(\tau)$ - вклад в $\rho(\tau)$ из МК когерентности $n$-го порядка~\cite{Fel_dman_1996}.
-ТОгда функция $G(\tau,\phi)$ уравнения ~(\ref{eq:8}) может быть переписана как
+где $\rho_{n}(\tau)$ - вклад в $\rho(\tau)$ из МК~когерентности $n$-го порядка~\cite{Fel_dman_1996}.
+В это случае функция $G(\tau,\phi)$ уравнения~(\ref{eq:8}) можено переписать как
 %
@@
 %
-Для дальнейших расчетов необходимо ввести нормированные интенсивности $J_{n}(\tau)$ $(n=0, \pm 2, \pm 4, \cdots)$ МК когерентностей ЯМР
+Для дальнейших расчетов необходимо ввести нормированные интенсивности $J_{n}(\tau)$ $(n=0, \pm 2, \pm 4, \cdots)$ МК~когерентностей~ЯМР
 %
@@
 %
-Используя уравнения ~(\ref{eq:9}),~(\ref{eq:10}) определим, что
+Используя уравнения~(\ref{eq:9}),~(\ref{eq:10}) определим, что
 %
@@
 %
-Из уравнения~(\ref{eq:14} можно сделать вывод, что сумма МК когерентнойстей ЯМР сохраняется на период МК эксперимента ЯМР~\cite{Baum_1985}.
+Из уравнения~(\ref{eq:14} можно сделать вывод, что сумма МК~когерентностей~ЯМР~сохраняется на подготовительном периоде МК~эксперимента~ЯМР~\cite{Baum_1985}.
 
-Базис, состоящий из собственных состояний оператора $I_\mathrm{z}$ (названный мультипликативным базисом), широко используется для численных расчетов МК динамики ЯМР~\cite{Zhang_2009}.
+Базис, состоящий из собственных состояний оператора $I_\mathrm{z}$ (называемый мультипликативным базисом), широко используется для численных расчетов МК~динамики~ЯМР~\cite{Zhang_2009}.
 В связи с быстрым расширением гильбертова пространства с ростом числа спинов такие вычисления возможны только для систем с небольшим числом спинов.
 Такой подход не подходит для исследований многоспиновой запутанности.
-Поскольку гамильтониан $H_{MQ}$ уравнения ~(\ref{eq:1}) коммутирует с квадратом полного углового момента спина $\hat I^2$, 
-можно использовать базис, состоящий из общих собственных состояний $\hat I^2$ и $I_\mathrm{z}$ для изучения МК динамики ЯМР, как это было сделано в статьях ~\cite{Doronin_2009,Doronin_2011,Doronin_2019}.
-В этом базисе гамильтониан $H_{MQ}$ и исходная матрица плотности уравнения~(\ref{eq:5}) (см.
-также уравнение~(\ref{eq:7})) состоят из блоков, соответствующих различным значениям углового момента спина~\cite{Doronin_2009}.
-Тогда исследование МК динамики ЯМР может быть сведено к решению ряда задач меньших размеров.
+Поскольку гамильтониан $H_{MQ}$ уравнения~(\ref{eq:1}) коммутирует с квадратом полного углового момента спина $\hat I^2$,
+можно использовать базис, состоящий из общих собственных состояний $\hat I^2$ и $I_\mathrm{z}$ для изучения МК~динамики~ЯМР, как это было сделано в статьях~\cite{Doronin_2009,Doronin_2011,Doronin_2019}.
+В этом базисе гамильтониан $H_{MQ}$ и исходная матрица плотности~(\ref{eq:5}) (см.
+также~(\ref{eq:7})) состоят из блоков, соответствующих различным значениям углового момента спина~\cite{Doronin_2009}.
+Тогда исследование МК~динамики~ЯМР~может быть сведено к решению ряда задач меньших размеров.
 
-Поскольку гамильтониан $H_{MQ}$ уравнения~(\ref{eq:1}) коммутирует с оператором $e^{i\pi I_\mathrm{z}}$, то $2^N \times 2^N$ гамильтонова матрица сводится к двум подматрицам $2^{N-1} \times 2^{N-1}$ подматрицам~\cite{Doronin_2009}.
-Для нечетных $N$ обе подматрицы вносят одинаковый вклад в МК когерентности ЯМР, и нужно решить проблему, используя только одну подматрицу $2^{N-1} \times 2^{N-1}$, и удвоить полученные интенсивности.
+Поскольку гамильтониан $H_{MQ}$ уравнения~(\ref{eq:1}) коммутирует с оператором $e^{i\pi I_\mathrm{z}}$, то $2^N \times 2^N$ матрица гамильтониана сводится к двум блокам$2^{N-1} \times 2^{N-1}$~\cite{Doronin_2009}.
+Для нечетных $N$ оба блока вносят одинаковый вклад в МК~когерентности~ЯМР~, и можно решить проблему, используя только один блок $2^{N-1} \times 2^{N-1}$, и удвоить полученные интенсивности.
 В наших расчетах мы берем только нечетные числа спинов.
-Используя этот метод, можно исследовать МК динамику ЯМР в системах, состоящих и сотен спинов.
+Используя этот метод, можно исследовать МК~динамику~ЯМР~в системах, состоящих и сотен спинов.
 
-\section{Аналитическое решение для МК динамики ЯМР трехспиновой системы в нанопоре в диполярном упорядоченном состоянии}
+\section{Аналитическое решение для МК~динамики~ЯМР~трехспиновой системы в нанопоре в дипольном упорядоченном состоянии}
 \label{sec:3}
@@
 	\caption{
-	    Интенсивность МК когерентности ЯМР $J_{n}$ ($n=0, 2$) в нанопоре с $N=3$.
+	  Интенсивность МК~когерентности~ЯМР~$J_{n}$ ($n=0, 2$) в нанопоре с $N=3$.
 	}
@@
 
-Проблема получения точного решения МК динамики ЯМР трехспиновой системы в диполярно упорядоченном состоянии в нанопоре аналогична проблеме, рассмотренной в ~\cite{Doronin_2019} для начального термодинамического равновесия в сильном внешнем магнитном поле.
+Проблема получения точного решения МК~динамики~ЯМР~трехспиновой системы в дипольно упорядоченном состоянии в нанопоре аналогична проблеме, рассмотренной в~\cite{Doronin_2019} для начального термодинамического равновесия в сильном внешнем магнитном поле.
 В работе мы не используем высокотемпературное приближение~\cite{Goldman_1970}.
 
-Гамильтониан $H_{MQ}$ уравнения ~(\ref{eq:1}) состоит из двух блоков для двух возможных значений углового момента спина $(I^2 = S(S+1),  \quad S=3/2,1/2)$.
-Эти блоки и соответсвующие им собственные значения и собственные состояния приведены в ~\cite{Doronin_2019}.
+Гамильтониан $H_{MQ}$ уравнения~(\ref{eq:1}) состоит из двух блоков для двух возможных значений углового момента спина $(I^2 = S(S+1), \quad S=3/2,1/2)$.
+Эти блоки и соответсвующие им собственные значения и собственные состояния приведены в~\cite{Doronin_2019}.
 Матрица плотности системы также состоит из двух блоков $\rho^{3/2}(\tau)$, $\rho^{1/2}(\tau)$, и
@@
 где $b = \dfrac{\hslash D}{k\mathrm{T}}$ и $T$ - температура.
-Простыми вычисленимий можно получить матрицы плотности $\rho^{3/2}(\tau)$ и $\rho^{1/2}(\tau)$,
-которые позволяют нам найти интенсивности МК когерентности ЯМР.
+Простыми вычислениями можно получить матрицы плотности $\rho^{3/2}(\tau)$ и $\rho^{1/2}(\tau)$,
+которые позволяют нам найти интенсивности МК~когерентности~ЯМР~.
 
-В рассматриваемых системах появляются только МК когерентности ЯМР нулевых и плюс/минус вторых порядков.
+В рассматриваемых системах появляются только МК~когерентности~ЯМР~нулевых и плюс/минус вторых порядков.
 Интенсивность этих когерентностей
@@
 %
-Сумма интенсивностей уравнения ~(\ref{eq:16}) равна единице в соответсвии с уравнением ~(\ref{eq:14}).
-Зависимости рассчитанных интенсивностей $J_{n}(\tau)$ $(n=0,2)$ от времени эволюции показаны на рисунке ~(\ref{fig:1}).
+Сумма интенсивностей уравнения~(\ref{eq:16}) равна единице в соответствии с уравнением~(\ref{eq:14}).
+Зависимости рассчитанных интенсивностей $J_{n}(\tau)$ $(n=0,2)$ от времени эволюции показаны на рисунке~(\ref{fig:1}).
 
-\section{Второй момент спектра МК ЯМР как мера многоспиновой запутанности}
+\section{Второй момент спектра МК~ЯМР~как мера многоспиновой запутанности}
 \label{sec:4}
 
-Выражение ~(\ref{eq:8}) для МК сигнала ЯМР $G(\tau,\phi)$ может быть последовательно расширено с приращением фазы $\phi$:
+Выражение~(\ref{eq:8}) для МК~сигнала~ЯМР~$G(\tau,\phi)$ может быть последовательно расширено с приращением фазы $\phi$:
 %
@@
 %
-В то же время легко проверить что уравнение $2 \mathrm{Tr} \left\{ \rho^2(\tau) I_\mathrm{z}^2 - \left( \rho(\tau) I_\mathrm{z} \right)^2 \right\}$ равно второму моменту $M_2$ распределения интенсивнсти МК когерентностей ЯМР~\cite{Khitrin_1997}
+В то же время легко проверить что уравнение $2 \mathrm{Tr} \left\{ \rho^2(\tau) I_\mathrm{z}^2 - \left( \rho(\tau) I_\mathrm{z} \right)^2 \right\}$ равно второму моменту $M_2$ распределения интенсивнсти МК~когерентностей~ЯМР~\cite{Khitrin_1997}
 %
@@
 %
-гле $J_n(\tau)$ ($n=0,\pm 2, \pm 4, \cdots$) определяется уравнением ~(\ref{eq:13}).
-Таким образом второй момент спектра МК ЯМР обеспечивает нижнюю границу квантовой информации Фишера $F_\mathrm{Q}(\rho,I_\mathrm{z})$.
+гле $J_n(\tau)$ ($n=0,\pm 2, \pm 4, \cdots$) определяется уравнением~(\ref{eq:13}).
+Таким образом второй момент спектра МК~ЯМР~обеспечивает нижнюю границу квантовой информации Фишера $F_\mathrm{Q}(\rho,I_\mathrm{z})$.
 Также показано~\cite{T_th_2014,Pezz__2018}, что, если
@@
 где $n$ - целая часть ${N/k}$, то система с матрицей плотности $\rho(\tau)$ $(k+1)$-спин запутанная~\cite{Pezz__2009,Hyllus_2012,T_th_2012}.
-Результаты численного анализа многоспиновой запутанности в системе спин-несущих молекул (атомов), первоначально приготовленных в диполярном упорядоченном состоянии, представлены в следующем разделе.
+Результаты численного анализа многоспиновой запутанности в системе спин-несущих молекул (атомов), первоначально приготовленных в дипольном упорядоченном состоянии, представлены в следующем разделе.
 
@@
 	  a) $T=6\cdot10^{-4}$~K, неравенство~(\ref{eq:20}) определяет область запутывания пары (k+1=2), область выше горизонтальной линии;
-	    b) $T=3.2\cdot10^{-4}$~K, область многоспиновой запутанности представляет собой полосу, ограниченную горизонтальными линиями с ~$k=19$~и~$k=46$; 
+	  b) $T=3.2\cdot10^{-4}$~K, область многоспиновой запутанности представляет собой полосу, ограниченную горизонтальными линиями с~$k=19$~и~$k=46$;
 	  c) $T = 1.6\cdot10^{_4}$~K, горизонтальные линии ($k=18$ и $k=86$) связывают полосу с многоспиновым переплетением;
@@
 
-Рассматриваемая модель спин-несущих молекул (атомов) в нанопоре в диполярно упорядоченных состояниях расширяет возможности исследования многоспинойо запутанности по сравнению с родственной моделью~\cite{Doronin_2019},
+Рассматриваемая модель спин-несущих молекул (атомов) в нанопоре с дипольно упорядоченным состоянием расширяет возможности исследования многоспиновой запутанности по сравнению с родственной моделью~\cite{Doronin_2019},
 в которой система изначально находилась в термодинамическом равновесии в сильном внешнем магнитном поле.
 Модель~\cite{Doronin_2019} не применима для исследования эволюции системы во времени,
-потому что распределение МК когерентностей ЯМР быстро становится стационарным~\cite{Doronin_2009}.
+потому что распределение МК~когерентностей~ЯМР~быстро становится стационарным~\cite{Doronin_2009}.
 Многоспиновая запутанность изменяется с температурой в очень узком температурном интервале в модели~\cite{Doronin_2019}.
@@
 	  Зависимость максимального количества запутанных спинов,
-	    усредненная по времени эволюции $(0 \leq D\tau \leq 3)$, 
-	    по теспературе при a) $N=51$; b) $N=75$; c) $N=101$.
+	  усредненное по времени эволюции $(0 \leq D\tau \leq 3)$,
+	  при температуре a) $N=51$; b) $N=75$; c) $N=101$.
 	}
@@
 
-Зависимость среднего максимального числа запутанных спинов за время эволюции $({0}\leq \mathrm{D}\tau\leq{3})$ от температуры при разных числах спинов в нанопоре представлена на Рис.~(\ref{fig:3}).
+Зависимость максимального числа запутанных спинов за время эволюции $({0}\leq \mathrm{D}\tau\leq{3})$ от температуры при разных числах спинов в нанопоре представлена на Рис.~(\ref{fig:3}).
 Максимальное количество запутанных спинов уменьшается при повышении температуры.
@@
 
-Была исследована многоспиновая запутанность в системе спин-несущих молекул (атомов), заполняющих несферические нанопоры в условиях эксперимента МК спектроскопии ЯМР.
-Спины изначально находились в диполярно упорядоченном состоянии.
+Была исследована многоспиновая запутанность в системе спин-несущих молекул (атомов), заполняющих не сферические нанопоры в условиях эксперимента МК~спектроскопии~ЯМР~.
+Спины изначально находились в дипольно упорядоченном состоянии.
 Найдена зависимость многоспиновой запутанности от температуры и количества спинов в нанопоре.
 
-Мы считаем, что МК спектроскопия ЯМР является утонченным и полезным методом для исследования различных проблем квантовой информации.
+Мы считаем, что МК~спектроскопия~ЯМР~является утонченным и полезным методом для исследования различных проблем квантовой информации.
 В частности, это очень эффективный метод исследования квантовой запутанности.
@@
 Работа частично поддержана Российским фондом фундаментальных исследований (гранты № 20-03-00147, 19-32-80004).
-И.Л. поддержан фондом Базис грантом Основы теоретической физики и математики №19-1-5-130-1.
+И.Л. благодарит Фонд развития теоретической физики «БАЗИС» №19-1-5-130-1.
 
@@
 %
-После первого резонансного Х-импульса
+После первого резонансного $x$-импульса
 %
@@
 %
-Тогда система свободно эволюционирует в течение времени $\tau$,
-и применяется второй резонансный импульс, который поворачивает спины на угол $\theta$ вокруг оси y вращающейся системы координат.
+Затем система свободно эволюционирует в течение времени $\tau$,
+и применяется второй резонансный $y$-импульс, который поворачивает спины на угол $\theta$ вокруг оси-$y$ вращающейся системы координат.
 В результате получаем, что
@@
 %
-где $\alpha$ и $\beta$ - это обратные Зеемановские и дипольные температуры.
+где $\alpha$ и $\beta$ - это обратная Зеемановская и дипольная температура.
 Очевидно, что система имеет одно равновесное состояние
 и существуют уникальные температуры $\alpha$ и $\beta$,
-что согласуется с закона сохранения.
+удовлетворяющие закону сохранения.
 Данные температуры могут быть получены из законов сохранения
@@
 В~(\ref{eq:a7}) было учтено, что $\left[ e^{-i \pi \sy}, \hdz \right] = 0$.
-Поскольку мы рассматриваем случай высокой дипольной температуры, можно переписать~(\ref{eq:a5}) как 
+Поскольку мы рассматриваем случай высокой дипольной температуры, можно переписать уравнение~(\ref{eq:a5}) как
 \begin{equation}
@@
 %
-Заметим, что $\tr{\sz} = \tr{\sz\hdz} = 0$. В таком случае $\alpha = 0$ удовлетворяет уравнению ~(\ref{eq:5}). 
-Таким образом, в рассматриваемом случае мы получаем дипольное упорядоченное состояние.
+Заметим, что $\tr{\sz} = \tr{\sz\hdz} = 0$. 
+В таком случае $\alpha = 0$ удовлетворяет уравнению~(\ref{eq:5}).
+Таким образом, в рассматриваемом случае мы получаем дипольно упорядоченное состояние.
 

### 2020-06-04 maniscript_rus.tex
Improve text

@@
 Многоквантовый (МК)~ЯМР~с~дипольно упорядоченным начальным состоянием открывает новые возможности для изучения многоспиновой запутанности.
-В~данной статье исследуется многоспиновая запутанность в~газе спин-несущих молекул (атомов) в нанорезонаторах
+В~данной статье исследуется многоспиновая запутанность в~газе спин-несущих молекул (атомов) в нано-поре
 в~условиях~ЯМР~с дипольно упорядоченным начальным состоянием.
@@
 
-Запутанность~\cite{Nielsen_2009} является важным понятием квантовой механики.
-Она определеяет преимущество квантовых компьютеров перед их классическими аналогами.
-Продемонстрированное квантовое превосходство программируемого сверхпроводящего процессора~\cite{Arute2019} также связано с понятием запутанности, которое отсутствует в классической физике.
+Запутанность~\cite{Nielsen_2009} является важней концепцией квантовой механики.
+В частности, она ответственна за преимущество квантовых компьютеров перед их классическими аналогами.
+Недавно продемонстрированное квантовое превосходство ~\cite{Arute2019} на  программируемом сверхпроводящем процессоре также связано с понятием запутанности, которое отсутствует в классической физике.
 Среди многочисленных методов исследования запутанности мы сосредоточились на многоквантовом~(МК)~ЯМР в~твердых телах~\cite{Baum_1985}, который широко используется для изучения запутанности в бинарных системах~\cite{Furman_2008, Furman_2009, Fel_dman_2008, Fel_dman_2012}.
-МК~ЯМР~спектроскопия~\cite{Baum_1985} позволяет извлекать информацию о многоспиновой запутанности~\cite{G_rttner_2018} с~помощью квантовой информации Фишера~\cite{T_th_2014, Pezz__2018}.
 
+Оказалось также, что МК~ЯМР~спектроскопия~\cite{Baum_1985} позволяет извлекать информацию о многоспиновой запутанности~\cite{G_rttner_2018} с~помощью квантовой информации Фишера~\cite{T_th_2014, Pezz__2018}, являющейся ключевой концепцией в квантовой теории информвации.
 Квантовая информация Фишера описывает скорость изменения квантовых состояний,
-определяемых матрицей плотности в ответ на изменение какого-либо параметра.
-В~МК~спектроскопии~ЯМР~данный параметр представляет собой приращение фазы между радиочастотными импульсами,
-облучающими систему в периоды приготовления и смешивания в МК~ЯМР~эксперименте~\cite{Baum_1985},
-что приводит к разделению сигналов, соответсвующих МК~когерентности~ЯМР разных~порядков,
-и позволяет получить полный спектр МК~ЯМР.
-Приращение фазы пропорционально продолжительности периода эволюции.
+определяемых матрицей плотности, как отклик системы на изменение наблюдаемой,  которая определяет МК когерентности ЯМР в~МК~спектроскопии~ЯМР~~\cite{Baum_1985}.
+В МК сспектроскопии ЯМР эта наблюдаемая определяется оператором полной проеции углового спинового момента на направление сильного внешнего магнитного поля.
 Используя квантовую информацию Фишера~\cite{Liu_2014} для анализа спектра МК~ЯМР,
@@
 Кроме того второй момент спектра МК~ЯМР~определяет нижнюю границу квантовой информации Фишера~\cite{G_rttner_2018}.
-Это означает, что МК~ЯМР~спектроскопия является ценным методом решения квантовых информационных задач.
+Это означает, что МК~ЯМР~спектроскопия является Эффективным методом решения квантовых информационных задач.
 
 Многоспиновая запутанность была исследована~\cite{Doronin_2019} для несферической нанопоры,
-заполненной газом переносящих спин молекул в сильном внешнем магнитном поле~\cite{Baugh_2001,Doronin_2009}.
-Термически равновесное начальное состояние системы определялось односпиновым зеемановским взаимодействием с внешним магнитным полем~\cite{Doronin_2007a}.
-Также возможно исследовать многоспиновую запутанность,
+заполненной газом  спин-несущих молекул в сильном внешнем магнитном поле~\cite{Baugh_2001,Doronin_2009}.
+Термодинамически равновесное начальное состояние системы определялось односпиновым зеемановским взаимодействием с внешним магнитным полем~\cite{Doronin_2007a}.
+Однако  многоспиновую запутанность можно  исследовать,
 когда та же самая система первоначально подготовлена в дипольном упорядоченном состоянии~\cite{Goldman_1970},
-используя либо метод адиабатического размагничивания во вращающейся системе отсчета~\cite{Goldman_1970, Slichter_1961},
-либо двухимпульную последовательность Брукерта-Джинера~\cite{Goldman_1970, Jeener_1967}.
-Динамика МК~ЯМР~с этим начальным состоянием моделировалась как в малых спиновых системах~\cite{Doronin_2007a, Doronin_2007b},
-так и в системе, состоящей из 200-600 спин-несущих молекул (атомов), заполняющих нанопоры~\cite{Doronin_2011}.
-Однако подходы, разработанные для этих исследований, ограничены высокими температурами и не могут применяться к многоспиновому запутыванию.
+используя либо метод адиабатического размагничивания во вращающейся системе координат~\cite{Goldman_1970, Slichter_1961},
+либо двухимпульную последовательность Брoкaерта-Джинера~\cite{Goldman_1970, Jeener_1967}.
+Динамика МК~ЯМР~с таким начальным состоянием моделировалась как для небольших спиновых систем~\cite{Doronin_2007a, Doronin_2007b},
+так и в системе, состоящей из 200-600 спин-несущих молекул (атомов), заполняющих нанопору~\cite{Doronin_2011}.
+Однако подходы, разработанные для этих исследований, ограничены случаем высоких температур и не могут применяться  для изучения многоспиновой запутанности.
 
-В настоящей статье мы рассматриваем среднетемпературный случай с низкими зеемановскими и высокими дипольными.
+В настоящей статье мы рассматриваем промежуточный температурный случай с низкой зеемановской и высокой дипольной температурами.
 Магнитное упорядочение~\cite{Abragam_1982} выходит за рамки данной статьи.
-Стоит обратить внимание, что двухимпульсный эксперимент Брукерта-Дженира~\cite{Jeener_1967} был выполнен при высоких температурах.
-В данной статье было доказано, что этот эксперимент~\cite{Jeener_1967} также может выполняться при средних температурах.
+Заметим, что двухимпульсный эксперимент Брокаерта-Дженира~\cite{Jeener_1967} был разработан для высокотемпературного случая.
+Мы теоретически  показываем, что этот эксперимент~\cite{Jeener_1967} также может выполняться и для промежуточного температурного случая, рассматриваемого в настоящей статье.
 Было показано~\cite{Doronin_2011}, что в МК~эксперименте~ЯМР~с дипольно упорядоченным начальным состоянием МК~когерентности~ЯМР~возникают быстрее,
-чем в МК~эксперименте~ЯМР~с начальным состоянием теплового равновесия в сильном внешнем магнитном поле.
-Данное наблюдение является важным в области исследований многоспиновой запутанности, поскольку они используют расчеты второго момента распределения МК~когерентностей~ЯМР~.
-Также оно является значительным в области исследований распространения корреляции~\cite{Baugh_2001,Baum_1986,S_nchez_2014,Munowitz_1987} и локализации~\cite{Alvarez_2015,Wei_2018}.
-В действительности, скорость распространения может быть описана с помощью out-of-time ordered correlations, которые связаны с распределением МК~когерентностей~ЯМР.
+чем в МК~эксперименте~ЯМР~с начальным м термодинамически равновесным состоянием в сильном внешнем магнитном поле.
+Данное обстоятельство является важным для исследования многоспиновой запутанности, поскольку при этом используется  второй момент распределения МК~когерентностей~ЯМР~.
+Указанное обстоятельство также важно для исследования распространения многоспиновых корреляций~\cite{Baugh_2001,Baum_1986,S_nchez_2014,Munowitz_1987} и локализации~\cite{Alvarez_2015,Wei_2018}.
+При этом важную роль играют неупорядочееные по времени корреляции (out-of-time ordered correlations), которые связаны с распределением МК~когерентностей~ЯМР.
 
-В данной статье исследуется многоспиновая запутанность с использованием спектра МК~ЯМР~спин-несущих атомов (молекул) в нанопоре, когда система подготовлена в дипольно упорядоченном состоянии.
+В данной статье исследуется многоспиновая запутанность с использованием спектра МК~ЯМР~спин-несущих атомов (молекул) в нанопоре, когда система приготовлена в дипольно упорядоченном состоянии.
 В разделе~\ref{sec:2} описана разработанная теория МК~динамики~ЯМР~при низкой зеемановской температуре и высокой дипольной температуре.
-Аналитическое решение для МК~динамики~ЯМР трехспиновой системы получено при таких же температурах и описано в разеделе~\ref{sec:3}.
-Второй момент спектра~МК~ЯМР~в качесвте меры многоспиновой запутанности рассматривается в разделе~\ref{sec:4}.
+Аналитическое решение для МК~динамики~ЯМР трехспиновой системы, полученное при таких же температурах,  описано в разеделе~\ref{sec:3}.
+Второй момент спектра~МК~ЯМР~в качестве меры многоспиновой запутанности рассматривается в разделе~\ref{sec:4}.
 В разделе~\ref{sec:5} исследуется зависимость многоспиновой запутанности от дипольной температуры и числа спинов в системе.
-Краткое изложение всех результатов приводится в разделе~\ref{sec:6}.
-В Приложении показано, что двухимпульсная последовательность Брукерта-Джинера может быть использована в случае, когда зеемановская температура низкая, а дипольная - высокая.
+Краткое изложение полученных результатов приведено в разделе~\ref{sec:6}.
+В Приложении показано, что двухимпульсная последовательность Брокаерта-Джинера может быть использована в случае, когда зеемановская температура низкая, а дипольная - высокая.
 
-\section{Теория МК~динамики~ЯМР~в нанопоре при низкой зеемановской температуре и высокой дипольной}
+\section{Теория МК~динамики~ЯМР~в нанопоре при низкой зеемановской  и высокой дипольной температурах}
 \label{sec:2}
@@
 %
-$N$ - число спинов в нанопоре, $I^{\pm}_{j}$ - повышающие или понижающие операторы спина $j$, $D$ - константа дипольной связи, усредненная по быстрой молекулярной диффузии спин-несущих атомов (молекул) в нанопоре.
-Подчеркнем, что константа дипольной связи $D$ одинакова для всех пар взаимодействующих спинов в нанопоре~\cite{Doronin_2019,Doronin_2009}.
-Матрица плотности $\rho(\tau)$ на время подготовки МК~эксперимента~ЯМР~\cite{Baum_1985} может быть получена из эволюционного уравнения Лиувилля~\cite{Goldman_1970,Abragam_1982}
+где $N$ - число спинов в нанопоре, $I^{\pm}_{j}$ - повышающий или понижающий операторы спина $j$, $D$ - константа диполь-дипольного ваимодействия (ДДВ) , усредненная по быстрой молекулярной диффузии спин-несущих атомов (молекул) в нанопоре.
+Подчеркнем, что константа ДДВ $D$ одинакова для всех пар взаимодействующих спинов в нанопоре~\cite{Doronin_2019,Doronin_2009}.
+Матрица плотности $\rho(\tau)$ на подготовительном периоде МК~эксперимента~ЯМР~\cite{Baum_1985} может быть получена из эволюционного уравнения Лиувилля~\cite{Goldman_1970,Abragam_1982}
 %
@@
 $\omega_{0}$ - частота Лармора ,
-$I_\mathrm{z}$ является оператором проекции полного углового момента вращения на ось~$z$,
+$I_\mathrm{z}$ -  оператор проекции полного углового спиновогомомента  на ось~$z$,
 который направлен вдоль сильного внешнего магнитного поля,
-$H_\mathrm{dz}$ является секулярной частью гамильтониана диполь-дипольного взаимодействия~(DDI) в сильном внешнем магнитном поле, 
-и $\alpha_\mathrm{z}$, $\beta_\mathrm{d}$ являются обратными зеемановскими и дипольными температурами.
-Мы рассмотрим случай, когда температура Зеемана является низкой $({\frac{\hslash \omega}{k} \alpha_\mathrm{z}}\gg 1)$, 
-а дипольная высокой $\left( \frac{\hslash{D}}{k}\beta_\mathrm{d} \ll 1\right)$.
+$H_\mathrm{dz}$ - секулярная часть гамильтониана ДДВ в сильном внешнем магнитном поле,
+и $\alpha_\mathrm{z}$, $\beta_\mathrm{d}$ - обратные зеемановская и дипольная температуры.
+Мы рассмотрим случай, когда зеемановская температура  является низкой $({\frac{\hslash \omega}{k} \alpha_\mathrm{z}}\gg 1)$,
+а дипольная - высокой $\left( \frac{\hslash{D}}{k}\beta_\mathrm{d} \ll 1\right)$.
 Мы предполагаем, что $\omega_{0} = 2\pi \cdot 500 \cdot 10^{6}$~s$^{-1}$ и $D = 2\pi \cdot 10^{4}$~s$^{-1}$.
-В приложении мы доказываем, что двухимпульсная последовательность Брукерта-Джинера~\cite{Goldman_1970,Jeener_1967} приводит к дипольному упорядоченному состоянию даже при низкой зеемановской температуре.
-Адиабатическое размагничивание~\cite{Goldman_1970,Slichter_1961} является вторым методом подготовки системы в дипольно упорядоченном состоянии.
+В приложении мы доказываем, что двухимпульсная последовательность Брокаерта-Джинера~\cite{Goldman_1970,Jeener_1967}позволяет получить дипольно упорядоченное состояние даже при низкой зеемановской температуре.
+Другим методом создания  дипольно упорядоченного состояния системы является адиабатическое размагничивание~\cite{Goldman_1970,Slichter_1961}.
 Используя эти методы, мы можем получить систему в состоянии термодинамического равновесия с матрицей плотности
@@
 %
-МК~динамика~ЯМР~в нанопоре будет исследована на основе уравнения~(\ref{eq:3}) с начальным состоянием уравнения~(\ref{eq:5}).
+МК~динамика~ЯМР~в нанопоре будет исследована на основе уравнения~(\ref{eq:3}) с начальным состоянием ~(\ref{eq:5}).
 Также важно отметить, что гамильтониан $H_{dz}$ частично усредняется быстрой молекулярной диффузией в нанопоре, а усредненный гамильтониан можно записать как \cite{Fel_dman_2004,Doronin_2011}
@@
 %
-где $I^{2}$ - квадрат углового момента вращения.
+где $I^{2}$ - квадрат углового спинового  момента.
 
-Пусть $G(\tau,\phi)$ будет сигналом после периодов подготовки, эволюции и смешивания в МК~эксперименте~ЯМР~\cite{Baum_1985}, усредненном по равновесной матрице плотности. 
+Пусть $G(\tau,\phi)$ описывает усредненный по равновесной матрице плотности сигнал после периодов подготовки, эволюции и смешивания в МК~эксперименте~ЯМР~\cite{Baum_1985}.
 $G(\tau,\phi)$ может записать как~\cite{Doronin_2019}
@@
 %
-где $\rho_{n}(\tau)$ - вклад в $\rho(\tau)$ из МК~когерентности $n$-го порядка~\cite{Fel_dman_1996}.
-В это случае функция $G(\tau,\phi)$ уравнения~(\ref{eq:8}) можено переписать как
+где $\rho_{n}(\tau)$ - вклад в $\rho(\tau)$ от МК~когерентности $n$-го порядка~\cite{Fel_dman_1996}.
+В этом случае функцию $G(\tau,\phi)$ в уравнении~(\ref{eq:8}) можено переписать как
 %
@@
 %
-Используя уравнения~(\ref{eq:9}),~(\ref{eq:10}) определим, что
+Используя уравнения~(\ref{eq:9}),~(\ref{eq:10}) можно проверить, что
 %
@@
 
-Проблема получения точного решения МК~динамики~ЯМР~трехспиновой системы в дипольно упорядоченном состоянии в нанопоре аналогична проблеме, рассмотренной в~\cite{Doronin_2019} для начального термодинамического равновесия в сильном внешнем магнитном поле.
-В работе мы не используем высокотемпературное приближение~\cite{Goldman_1970}.
+Задача получения точного решения МК~динамики~ЯМР~трехспиновой системы в дипольно упорядоченном состоянии в нанопоре аналогична задаче, рассмотренной в~\cite{Doronin_2019} для начального термодинамического равновесия в сильном внешнем магнитном поле.
+При решении задачи мы небудем  использовать высокотемпературное приближение~\cite{Goldman_1970}.
 
@@
 Простыми вычислениями можно получить матрицы плотности $\rho^{3/2}(\tau)$ и $\rho^{1/2}(\tau)$,
-которые позволяют нам найти интенсивности МК~когерентности~ЯМР~.
+которые позволяют нам найти интенсивности МК~когерентностей~ЯМР~.
 
-В рассматриваемых системах появляются только МК~когерентности~ЯМР~нулевых и плюс/минус вторых порядков.
-Интенсивность этих когерентностей
+В рассматриваемых системах появляются только МК~когерентности~ЯМР~нулевого и плюс/минус второго порядков.
+Интенсивности этих когерентностей равны
 %
@@
 %
-Сумма интенсивностей уравнения~(\ref{eq:16}) равна единице в соответствии с уравнением~(\ref{eq:14}).
+Сумма интенсивностей МК когерентностей согласно~(\ref{eq:16}) равна единице в соответствии с уравнением~(\ref{eq:14}).
 Зависимости рассчитанных интенсивностей $J_{n}(\tau)$ $(n=0,2)$ от времени эволюции показаны на рисунке~(\ref{fig:1}).
@@
 
-Выражение~(\ref{eq:8}) для МК~сигнала~ЯМР~$G(\tau,\phi)$ может быть последовательно расширено с приращением фазы $\phi$:
+Выражение~(\ref{eq:8}) для МК~сигнала~ЯМР~$G(\tau,\phi)$ может быть разложено в ряд по инкременту фазы импульсов
 %
@@
 %
-Можно доказать~\cite{Girolami_2017}, что квантовая информация Фишера $F_\mathrm{Q}(\rho,I_\mathrm{z})$~\cite{Helstrom_1976}
+Можно доказать~\cite{Girolami_2017}, что квантовая информация Фишера $F_\mathrm{Q}(\rho,I_\mathrm{z})$~\cite{Helstrom_1976 удовлетворяет неравенству:
 %
@@
 %
-В то же время легко проверить что уравнение $2 \mathrm{Tr} \left\{ \rho^2(\tau) I_\mathrm{z}^2 - \left( \rho(\tau) I_\mathrm{z} \right)^2 \right\}$ равно второму моменту $M_2$ распределения интенсивнсти МК~когерентностей~ЯМР~\cite{Khitrin_1997}
+В то же время легко проверить, что уравнение $2 \mathrm{Tr} \left\{ \rho^2(\tau) I_\mathrm{z}^2 - \left( \rho(\tau) I_\mathrm{z} \right)^2 \right\}$ равно второму моменту $M_2$ распределения интенсивнстей МК~когерентностей~ЯМР~\cite{Khitrin_1997}
 %
@@
 гле $J_n(\tau)$ ($n=0,\pm 2, \pm 4, \cdots$) определяется уравнением~(\ref{eq:13}).
-Таким образом второй момент спектра МК~ЯМР~обеспечивает нижнюю границу квантовой информации Фишера $F_\mathrm{Q}(\rho,I_\mathrm{z})$.
+Таким образом, второй момент распределения интенсивностей МК~ЯМР~ дает нижнюю границу квантовой информации Фишера $F_\mathrm{Q}(\rho,I_\mathrm{z})$.
 Также показано~\cite{T_th_2014,Pezz__2018}, что, если
@@
 %
-где $n$ - целая часть ${N/k}$, то система с матрицей плотности $\rho(\tau)$ $(k+1)$-спин запутанная~\cite{Pezz__2009,Hyllus_2012,T_th_2012}.
+где $n$ - целая часть ${N/k}$, то система с матрицей плотности $\rho(\tau)$ содержит  $(k+1)$ запутанных спинов ~\cite{Pezz__2009,Hyllus_2012,T_th_2012}.
 Результаты численного анализа многоспиновой запутанности в системе спин-несущих молекул (атомов), первоначально приготовленных в дипольном упорядоченном состоянии, представлены в следующем разделе.
@@
 	\caption{
-	  Зависимость нижней границы от квантовой информации Фишера $F_\mathrm{Q} = 2 M_{2}$
-	  на безразмерном времени $D\tau$ при $N=101$.
-	  a) $T=6\cdot10^{-4}$~K, неравенство~(\ref{eq:20}) определяет область запутывания пары (k+1=2), область выше горизонтальной линии;
+	  Зависимость нижней границы  квантовой информации Фишера $F_\mathrm{Q} = 2 M_{2}$
+	  от безразмерного времени $D\tau$ при $N=101$.
+	  a) $T=6\cdot10^{-4}$~K, неравенство~(\ref{eq:20}) определяет область парной запутанности  (k+1=2), эта область выше горизонтальной линии;
 	  b) $T=3.2\cdot10^{-4}$~K, область многоспиновой запутанности представляет собой полосу, ограниченную горизонтальными линиями с~$k=19$~и~$k=46$;
-	  c) $T = 1.6\cdot10^{_4}$~K, горизонтальные линии ($k=18$ и $k=86$) связывают полосу с многоспиновым переплетением;
-	  d) $T=4.8\cdot10^{-5}$~K, появляются запутанные кластеры с $10-92$ спинами.
+	  c) $T = 1.6\cdot10^{_4}$~K, горизонтальные линии ($k=18$ и $k=86$) ограничивают полосу с многоспиновой запутанностью;
+	  d) $T=4.8\cdot10^{-5}$~K, возникают запутанные кластеры с $10-92$ спинами.
 	}
@@
 
-Рассматриваемая модель спин-несущих молекул (атомов) в нанопоре с дипольно упорядоченным состоянием расширяет возможности исследования многоспиновой запутанности по сравнению с родственной моделью~\cite{Doronin_2019},
+Рассматриваемая модель спин-несущих молекул (атомов) в нанопоре в дипольно упорядоченном состоянии расширяет возможности исследования многоспиновой запутанности по сравнению с родственной моделью~\cite{Doronin_2019},
 в которой система изначально находилась в термодинамическом равновесии в сильном внешнем магнитном поле.
-Модель~\cite{Doronin_2019} не применима для исследования эволюции системы во времени,
+Модель~\cite{Doronin_2019} неприменима для исследования эволюции системы во времени,
 потому что распределение МК~когерентностей~ЯМР~быстро становится стационарным~\cite{Doronin_2009}.
 Многоспиновая запутанность изменяется с температурой в очень узком температурном интервале в модели~\cite{Doronin_2019}.
-Например, все спины запутаны в системе, состоящей из 201 спина при температуре $T=6.856\cdot10^{-3}$~K~\cite{Doronin_2019}.
+Например, все спины запутаны в системе, состоящей из 201 спина ужери температуре $T=6.856\cdot10^{-3}$~K~\cite{Doronin_2019}.
 
-Временная зависимость квантовой информации Фишера в системе, состоящей из 101 спина, представлена на Рис.~(\ref{fig:2}) при различных температурах.
+ Зависимость квантовой информации Фишера от времени в системе, состоящей из 101 спина, представлена на Рис.~(\ref{fig:2}) при различных температурах.
 Из Рис.~(\ref{fig:2}a) видно, что при температуре $T=6\cdot10^{-4}$~K существует только парная запутанность.
-При температуре $T=3.2\cdot10^{-4}$ на Рис.~(\ref{fig:2}b) видна полоса, в которой неравенство~(\ref{eq:20}) может быть решено, когда $19 \leq k \leq 46$.
+При температуре $T=3.2\cdot10^{-4}$ на Рис.~(\ref{fig:2}b) появляется полоса, в которой неравенство~(\ref{eq:20}) может быть выполнено, когда $19 \leq k \leq 46$.
 Таким образом, существует многоспиновая запутанность в спиновых кластерах, состоящих из 20-47 спинов, при температуре $3.2\cdot10^{-4}$~K.
-Когда температура снижается, ширина полосы, в которой существует многоспиновая запутанность, увеличивается.
-При температуре $T=1.6\cdot10^{-4}$~K (Рис.~(\ref{fig:2}c)), появляются кластеры из 19-87 запутанных спинов, а при температуре $T=4.8\cdot10^{-5}$~K (Рис.~(\ref{fig:2}d)), наблюдаются 11-92 запутанных спина.
+Когда температура понижается, ширина полосы, в которой существует многоспиновая запутанность, увеличивается.
+При температуре $T=1.6\cdot10^{-4}$~K (Рис.~(\ref{fig:2}c)) появляются кластеры из 19-87 запутанных спинов, а при температуре $T=4.8\cdot10^{-5}$~K (Рис.~(\ref{fig:2}d)), наблюдаются 11-92 запутанных спина.
 
@@
 	  Зависимость максимального количества запутанных спинов,
-	  усредненное по времени эволюции $(0 \leq D\tau \leq 3)$,
+	  усредненного по времени эволюции $(0 \leq D\tau \leq 3)$,
 	  при температуре a) $N=51$; b) $N=75$; c) $N=101$.
@@
 
-\section{Выводы}
+\section{Заключение}
 \label{sec:6}
 
-Была исследована многоспиновая запутанность в системе спин-несущих молекул (атомов), заполняющих не сферические нанопоры в условиях эксперимента МК~спектроскопии~ЯМР~.
+Мы исследовали многоспиновую запутанность в системе спин-несущих молекул (атомов), заполняющих несферические нанопоры в условиях эксперимента МК~спектроскопии~ЯМР~.
 Спины изначально находились в дипольно упорядоченном состоянии.
@@
 
-Мы считаем, что МК~спектроскопия~ЯМР~является утонченным и полезным методом для исследования различных проблем квантовой информации.
+Проведенные исследования позволяют заключить, что МК~спектроскопия~ЯМР~является тонким и полезным методом для исследования различных проблем квантовой информатики.
 В частности, это очень эффективный метод исследования квантовой запутанности.
@@
 \section{Acknowledgements}
-Эта работа выполнена в рамках государственного задания, госрегистрации № 0089-2019-0002.
+Эта работа выполнена в рамках Государственного задания, госрегистраци № 0089-2019-0002.
 Работа частично поддержана Российским фондом фундаментальных исследований (гранты № 20-03-00147, 19-32-80004).
@@
 \appendix
-\section{Двухимпульсный эксперимент Брукерта-Джинера при низкой зеемановской температуре и высокой дипольной температуре.}
+\section{Двухимпульсный эксперимент Брокаерта-Джинера при низкой зеемановской температуре и высокой дипольной температуре.}
 
@@
 Затем система свободно эволюционирует в течение времени $\tau$,
-и применяется второй резонансный $y$-импульс, который поворачивает спины на угол $\theta$ вокруг оси-$y$ вращающейся системы координат.
+и после этого подается второй резонансный $y$-импульс, который поворачивает спины на угол $\theta$ вокруг оси-$y$ ВСК.
 В результате получаем, что
@@
 %
-где $\alpha$ и $\beta$ - это обратная Зеемановская и дипольная температура.
-Очевидно, что система имеет одно равновесное состояние
-и существуют уникальные температуры $\alpha$ и $\beta$,
-удовлетворяющие закону сохранения.
-Данные температуры могут быть получены из законов сохранения
+где $\alpha$ и $\beta$ - обратные зеемановская и дипольная температуры.
+Очевидно, что система имеет единственное  равновесное состояние, а
+ температуры $\alpha$ и $\beta$ в равновесном состоянии находятся из
+законов сохранения:
+
 \begin{align}

### 2020-06-04 maniscript_rus.tex
Fix orfo

@@
 Многоквантовый (МК)~ЯМР~с~дипольно упорядоченным начальным состоянием открывает новые возможности для изучения многоспиновой запутанности.
-В~данной статье исследуется многоспиновая запутанность в~газе спин-несущих молекул (атомов) в нано-поре
+В~данной статье исследуется многоспиновая запутанность в~газе спин-несущих молекул (атомов) в нанопоре
 в~условиях~ЯМР~с дипольно упорядоченным начальным состоянием.
@@
 
-Запутанность~\cite{Nielsen_2009} является важней концепцией квантовой механики.
+Запутанность~\cite{Nielsen_2009} является важной концепцией квантовой механики.
 В частности, она ответственна за преимущество квантовых компьютеров перед их классическими аналогами.
 Недавно продемонстрированное квантовое превосходство ~\cite{Arute2019} на программируемом сверхпроводящем процессоре также связано с понятием запутанности, которое отсутствует в классической физике.
-Среди многочисленных методов исследования запутанности мы сосредоточились на многоквантовом~(МК)~ЯМР в~твердых телах~\cite{Baum_1985}, который широко используется для изучения запутанности в бинарных системах~\cite{Furman_2008, Furman_2009, Fel_dman_2008, Fel_dman_2012}.
+Среди многочисленных методов исследования запутанности мы сосредоточились на многоквантовом~(МК)~ЯМР в~твердых телах~\cite{Baum_1985},
+который широко используется для изучения запутанности в бинарных системах~\cite{Furman_2008, Furman_2009, Fel_dman_2008, Fel_dman_2012}.
 
-Оказалось также, что МК~ЯМР~спектроскопия~\cite{Baum_1985} позволяет извлекать информацию о многоспиновой запутанности~\cite{G_rttner_2018} с~помощью квантовой информации Фишера~\cite{T_th_2014, Pezz__2018}, являющейся ключевой концепцией в квантовой теории информвации.
+Оказалось также, что МК~ЯМР~спектроскопия~\cite{Baum_1985} позволяет извлекать информацию о многоспиновой запутанности~\cite{G_rttner_2018} с~помощью квантовой информации Фишера~\cite{T_th_2014, Pezz__2018},
+являющейся ключевой концепцией в квантовой теории информации.
 Квантовая информация Фишера описывает скорость изменения квантовых состояний,
-определяемых матрицей плотности, как отклик системы на изменение наблюдаемой,  которая определяет МК когерентности ЯМР в~МК~спектроскопии~ЯМР~~\cite{Baum_1985}.
-В МК сспектроскопии ЯМР эта наблюдаемая определяется оператором полной проеции углового спинового момента на направление сильного внешнего магнитного поля.
+определяемых матрицей плотности, как отклик системы на изменение наблюдаемой,
+которая определяет МК когерентности ЯМР в~МК~спектроскопии~ЯМР~~\cite{Baum_1985}.
+В МК спектроскопии ЯМР эта наблюдаемая определяется оператором полной проекции углового спинового момента на направление сильного внешнего магнитного поля.
 Используя квантовую информацию Фишера~\cite{Liu_2014} для анализа спектра МК~ЯМР,
 можно получить важную информацию о многоспиновой запутанности,
-поскольку сущесвует связь между вторым моментом спектра~\cite{Khitrin_1997} и квантовой информацией Фишера~\cite{G_rttner_2018,Doronin_2019}.
+поскольку существует связь между вторым моментом спектра~\cite{Khitrin_1997} и квантовой информацией Фишера~\cite{G_rttner_2018,Doronin_2019}.
 Кроме того второй момент спектра МК~ЯМР~определяет нижнюю границу квантовой информации Фишера~\cite{G_rttner_2018}.
@@
 
-Многоспиновая запутанность была исследована~\cite{Doronin_2019} для несферической нанопоры,
+Многоспиновая запутанность была исследована~\cite{Doronin_2019} для не сферической нанопоры,
 заполненной газом  спин-несущих молекул в сильном внешнем магнитном поле~\cite{Baugh_2001,Doronin_2009}.
@@
 используя либо метод адиабатического размагничивания во вращающейся системе координат~\cite{Goldman_1970, Slichter_1961},
-либо двухимпульную последовательность Брoкaерта-Джинера~\cite{Goldman_1970, Jeener_1967}.
+либо двухимпульную последовательность Брокаерта-Джинера~\cite{Goldman_1970, Jeener_1967}.
 Динамика МК~ЯМР~с таким начальным состоянием моделировалась как для небольших спиновых систем~\cite{Doronin_2007a, Doronin_2007b},
@@
 Магнитное упорядочение~\cite{Abragam_1982} выходит за рамки данной статьи.
-Заметим, что двухимпульсный эксперимент Брокаерта-Дженира~\cite{Jeener_1967} был разработан для высокотемпературного случая.
+Заметим, что двухимпульсный эксперимент Брокаерта-Джинира~\cite{Jeener_1967} был разработан для высокотемпературного случая.
 Мы теоретически  показываем, что этот эксперимент~\cite{Jeener_1967} также может выполняться и для промежуточного температурного случая, рассматриваемого в настоящей статье.
 Было показано~\cite{Doronin_2011}, что в МК~эксперименте~ЯМР~с дипольно упорядоченным начальным состоянием МК~когерентности~ЯМР~возникают быстрее,
-чем в МК~эксперименте~ЯМР~с начальным м термодинамически равновесным состоянием в сильном внешнем магнитном поле.
+чем в МК~эксперименте~ЯМР~с начальным термодинамически равновесным состоянием в сильном внешнем магнитном поле.
 Данное обстоятельство является важным для исследования многоспиновой запутанности, поскольку при этом используется  второй момент распределения МК~когерентностей~ЯМР~.
 Указанное обстоятельство также важно для исследования распространения многоспиновых корреляций~\cite{Baugh_2001,Baum_1986,S_nchez_2014,Munowitz_1987} и локализации~\cite{Alvarez_2015,Wei_2018}.
-При этом важную роль играют неупорядочееные по времени корреляции (out-of-time ordered correlations), которые связаны с распределением МК~когерентностей~ЯМР.
+При этом важную роль играют неупорядоченные по времени корреляции (out-of-time ordered correlations), которые связаны с распределением МК~когерентностей~ЯМР.
 
@@
 В разделе~\ref{sec:2} описана разработанная теория МК~динамики~ЯМР~при низкой зеемановской температуре и высокой дипольной температуре.
-Аналитическое решение для МК~динамики~ЯМР трехспиновой системы, полученное при таких же температурах,  описано в разеделе~\ref{sec:3}.
+Аналитическое решение для МК~динамики~ЯМР трехспиновой системы, полученное при таких же температурах,  описано в разделе~\ref{sec:3}.
 Второй момент спектра~МК~ЯМР~в качестве меры многоспиновой запутанности рассматривается в разделе~\ref{sec:4}.
@@
 %
-где $N$ - число спинов в нанопоре, $I^{\pm}_{j}$ - повышающий или понижающий операторы спина $j$, $D$ - константа диполь-дипольного ваимодействия (ДДВ) , усредненная по быстрой молекулярной диффузии спин-несущих атомов (молекул) в нанопоре.
+где $N$ - число спинов в нанопоре, $I^{\pm}_{j}$ - повышающий или понижающий операторы спина $j$, $D$ - константа диполь-дипольного взаимодействия (ДДВ),
+усредненная по быстрой молекулярной диффузии спин-несущих атомов (молекул) в нанопоре.
 Подчеркнем, что константа ДДВ $D$ одинакова для всех пар взаимодействующих спинов в нанопоре~\cite{Doronin_2019,Doronin_2009}.
@@
 $\omega_{0}$ - частота Лармора ,
-$I_\mathrm{z}$ -  оператор проекции полного углового спиновогомомента  на ось~$z$,
+$I_\mathrm{z}$ -  оператор проекции полного углового спинового момента  на ось~$z$,
 который направлен вдоль сильного внешнего магнитного поля,
@@
 Мы предполагаем, что $\omega_{0} = 2\pi \cdot 500 \cdot 10^{6}$~s$^{-1}$ и $D = 2\pi \cdot 10^{4}$~s$^{-1}$.
-В приложении мы доказываем, что двухимпульсная последовательность Брокаерта-Джинера~\cite{Goldman_1970,Jeener_1967}позволяет получить дипольно упорядоченное состояние даже при низкой зеемановской температуре.
+В приложении мы доказываем, что двухимпульсная последовательность Брокаерта-Джинера~\cite{Goldman_1970,Jeener_1967} позволяет получить дипольно упорядоченное состояние даже при низкой зеемановской температуре.
 Другим методом создания  дипольно упорядоченного состояния системы является адиабатическое размагничивание~\cite{Goldman_1970,Slichter_1961}.
@@
 где $\rho_{n}(\tau)$ - вклад в $\rho(\tau)$ от МК~когерентности $n$-го порядка~\cite{Fel_dman_1996}.
-В этом случае функцию $G(\tau,\phi)$ в уравнении~(\ref{eq:8}) можено переписать как
+В этом случае функцию $G(\tau,\phi)$ в уравнении~(\ref{eq:8}) можно переписать как
 %
@@
 Задача получения точного решения МК~динамики~ЯМР~трехспиновой системы в дипольно упорядоченном состоянии в нанопоре аналогична задаче, рассмотренной в~\cite{Doronin_2019} для начального термодинамического равновесия в сильном внешнем магнитном поле.
-При решении задачи мы небудем  использовать высокотемпературное приближение~\cite{Goldman_1970}.
+При решении задачи мы не будем  использовать высокотемпературное приближение~\cite{Goldman_1970}.
 
 Гамильтониан $H_{MQ}$ уравнения~(\ref{eq:1}) состоит из двух блоков для двух возможных значений углового момента спина $(I^2 = S(S+1), \quad S=3/2,1/2)$.
-Эти блоки и соответсвующие им собственные значения и собственные состояния приведены в~\cite{Doronin_2019}.
+Эти блоки и соответствующие им собственные значения и собственные состояния приведены в~\cite{Doronin_2019}.
 Матрица плотности системы также состоит из двух блоков $\rho^{3/2}(\tau)$, $\rho^{1/2}(\tau)$, и
@@
 %
-Можно доказать~\cite{Girolami_2017}, что квантовая информация Фишера $F_\mathrm{Q}(\rho,I_\mathrm{z})$~\cite{Helstrom_1976 удовлетворяет неравенству:
+Можно доказать~\cite{Girolami_2017}, что квантовая информация Фишера $F_\mathrm{Q}(\rho,I_\mathrm{z})$~\cite{Helstrom_1976} удовлетворяет неравенству:
 %
@@
 %
-В то же время легко проверить, что уравнение $2 \mathrm{Tr} \left\{ \rho^2(\tau) I_\mathrm{z}^2 - \left( \rho(\tau) I_\mathrm{z} \right)^2 \right\}$ равно второму моменту $M_2$ распределения интенсивнстей МК~когерентностей~ЯМР~\cite{Khitrin_1997}
+В то же время легко проверить, что уравнение $2 \mathrm{Tr} \left\{ \rho^2(\tau) I_\mathrm{z}^2 - \left( \rho(\tau) I_\mathrm{z} \right)^2 \right\}$ равно второму моменту $M_2$ распределения интенсивностей МК~когерентностей~ЯМР~\cite{Khitrin_1997}
 %
@@
 %
-гле $J_n(\tau)$ ($n=0,\pm 2, \pm 4, \cdots$) определяется уравнением~(\ref{eq:13}).
+где $J_n(\tau)$ ($n=0,\pm 2, \pm 4, \cdots$) определяется уравнением~(\ref{eq:13}).
 Таким образом, второй момент распределения интенсивностей МК~ЯМР~ дает нижнюю границу квантовой информации Фишера $F_\mathrm{Q}(\rho,I_\mathrm{z})$.
@@
 Многоспиновая запутанность изменяется с температурой в очень узком температурном интервале в модели~\cite{Doronin_2019}.
-Например, все спины запутаны в системе, состоящей из 201 спина ужери температуре $T=6.856\cdot10^{-3}$~K~\cite{Doronin_2019}.
+Например, все спины запутаны в системе, состоящей из 201 спина уже при температуре $T=6.856\cdot10^{-3}$~K~\cite{Doronin_2019}.
 
@@
 
-Мы исследовали многоспиновую запутанность в системе спин-несущих молекул (атомов), заполняющих несферические нанопоры в условиях эксперимента МК~спектроскопии~ЯМР~.
+Мы исследовали многоспиновую запутанность в системе спин-несущих молекул (атомов), заполняющих не сферические нанопоры в условиях эксперимента МК~спектроскопии~ЯМР~.
 Спины изначально находились в дипольно упорядоченном состоянии.

### 2020-06-05 maniscript_rus.tex
Improvements

@@
 Квантовая информация Фишера описывает скорость изменения квантовых состояний,
-определяемых матрицей плотности, как отклик системы на изменение наблюдаемой,
+определяемых матрицей плотности, при изменении наблюдаемой,
 которая определяет МК когерентности ЯМР в~МК~спектроскопии~ЯМР~~\cite{Baum_1985}.
@@
 Кроме того второй момент спектра МК~ЯМР~определяет нижнюю границу квантовой информации Фишера~\cite{G_rttner_2018}.
-Это означает, что МК~ЯМР~спектроскопия является Эффективным методом решения квантовых информационных задач.
+Это означает, что МК~ЯМР~спектроскопия является эффективным методом решения квантовых информационных задач.
 
-Многоспиновая запутанность была исследована~\cite{Doronin_2019} для не сферической нанопоры,
+Многоспиновая запутанность была исследована~\cite{Doronin_2019} для несферической нанопоры,
 заполненной газом  спин-несущих молекул в сильном внешнем магнитном поле~\cite{Baugh_2001,Doronin_2009}.
@@
 когда та же самая система первоначально подготовлена в дипольном упорядоченном состоянии~\cite{Goldman_1970},
-используя либо метод адиабатического размагничивания во вращающейся системе координат~\cite{Goldman_1970, Slichter_1961},
+используя либо метод адиабатического размагничивания во вращающейся системе координат (ВСК) ~\cite{Goldman_1970, Slichter_1961},
 либо двухимпульную последовательность Брокаерта-Джинера~\cite{Goldman_1970, Jeener_1967}.
@@
 Было показано~\cite{Doronin_2011}, что в МК~эксперименте~ЯМР~с дипольно упорядоченным начальным состоянием МК~когерентности~ЯМР~возникают быстрее,
-чем в МК~эксперименте~ЯМР~с начальным термодинамически равновесным состоянием в сильном внешнем магнитном поле.
+чем в МК~эксперименте~ЯМР~с начальным термодинамическим равновесным состоянием в сильном внешнем магнитном поле.
 Данное обстоятельство является важным для исследования многоспиновой запутанности, поскольку при этом используется  второй момент распределения МК~когерентностей~ЯМР~.
@@
 
-В данной статье исследуется многоспиновая запутанность с использованием спектра МК~ЯМР~спин-несущих атомов (молекул) в нанопоре, когда система приготовлена в дипольно упорядоченном состоянии.
+В данной статье исследуется многоспиновая запутанность с использованием МК  спектра ~ЯМР~спин-несущих атомов (молекул) в нанопоре, когда система приготовлена в дипольно упорядоченном состоянии.
 В разделе~\ref{sec:2} описана разработанная теория МК~динамики~ЯМР~при низкой зеемановской температуре и высокой дипольной температуре.
@@
 %
-с начальной термодинамически равновесной матрицей плотности
+с начальной термодинамической равновесной матрицей плотности
 %
@@
 который направлен вдоль сильного внешнего магнитного поля,
-$H_\mathrm{dz}$ - секулярная часть гамильтониана ДДВ в сильном внешнем магнитном поле,
+$H_\mathrm{dz}$ - секулярная часть гамильтониана ДДВ в сильном внешнем магнитном поле
 и $\alpha_\mathrm{z}$, $\beta_\mathrm{d}$ - обратные зеемановская и дипольная температуры.
@@
 где $\rho_{n}(\tau)$ - вклад в $\rho(\tau)$ от МК~когерентности $n$-го порядка~\cite{Fel_dman_1996}.
-В этом случае функцию $G(\tau,\phi)$ в уравнении~(\ref{eq:8}) можно переписать как
+Тогда  функцию $G(\tau,\phi)$ в уравнении~(\ref{eq:8}) можно переписать как
 %
@@
 %
-Используя уравнения~(\ref{eq:9}),~(\ref{eq:10}) можно проверить, что
+Используя уравнения~(\ref{eq:9}),~(\ref{eq:10}), можно проверить, что
 %
@@
 %
-Из уравнения~(\ref{eq:14} можно сделать вывод, что сумма МК~когерентностей~ЯМР~сохраняется на подготовительном периоде МК~эксперимента~ЯМР~\cite{Baum_1985}.
+Из уравнения~(\ref{eq:14}) можно сделать вывод, что сумма МК~когерентностей~ЯМР~сохраняется на подготовительном периоде МК~эксперимента~ЯМР~\cite{Baum_1985}.
 
@@
 
-Поскольку гамильтониан $H_{MQ}$ уравнения~(\ref{eq:1}) коммутирует с оператором $e^{i\pi I_\mathrm{z}}$, то $2^N \times 2^N$ матрица гамильтониана сводится к двум блокам$2^{N-1} \times 2^{N-1}$~\cite{Doronin_2009}.
+Поскольку гамильтониан $H_{MQ}$ уравнения~(\ref{eq:1}) коммутирует с оператором $e^{i\pi I_\mathrm{z}}$, то $2^N \times 2^N$ матрица гамильтониана сводится к двум блокам $2^{N-1} \times 2^{N-1}$~\cite{Doronin_2009}.
 Для нечетных $N$ оба блока вносят одинаковый вклад в МК~когерентности~ЯМР~, и можно решить проблему, используя только один блок $2^{N-1} \times 2^{N-1}$, и удвоить полученные интенсивности.
@@
 	\caption{
-	  Интенсивность МК~когерентности~ЯМР~$J_{n}$ ($n=0, 2$) в нанопоре с $N=3$.
+	  Интенсивности МК~когерентностей~ЯМР~$J_{n}$ ($n=0, 2$) в нанопоре с $N=3$.
 	}
@@
 %
-В то же время легко проверить, что уравнение $2 \mathrm{Tr} \left\{ \rho^2(\tau) I_\mathrm{z}^2 - \left( \rho(\tau) I_\mathrm{z} \right)^2 \right\}$ равно второму моменту $M_2$ распределения интенсивностей МК~когерентностей~ЯМР~\cite{Khitrin_1997}
+В то же время легко проверить, что выражение $2 \mathrm{Tr} \left\{ \rho^2(\tau) I_\mathrm{z}^2 - \left( \rho(\tau) I_\mathrm{z} \right)^2 \right\}$ равно второму моменту $M_2$ распределения интенсивностей МК~когерентностей~ЯМР~\cite{Khitrin_1997}
 %
@@
 	  c) $T = 1.6\cdot10^{_4}$~K, горизонтальные линии ($k=18$ и $k=86$) ограничивают полосу с многоспиновой запутанностью;
-	  d) $T=4.8\cdot10^{-5}$~K, возникают запутанные кластеры с $10-92$ спинами.
+	  d) при $T=4.8\cdot10^{-5}$~K возникают запутанные кластеры с $11-92$ спинами.
 	}
@@
 	  усредненного по времени эволюции $(0 \leq D\tau \leq 3)$,
-	  при температуре a) $N=51$; b) $N=75$; c) $N=101$.
+	  от температуры при  a) $N=51$; b) $N=75$; c) $N=101$.
 	}
@@
 
-Мы исследовали многоспиновую запутанность в системе спин-несущих молекул (атомов), заполняющих не сферические нанопоры в условиях эксперимента МК~спектроскопии~ЯМР~.
+Мы исследовали многоспиновую запутанность в системе спин-несущих молекул (атомов), заполняющих несферические нанопоры в условиях эксперимента МК~спектроскопии~ЯМР~.
 Спины изначально находились в дипольно упорядоченном состоянии.
@@
 
-\section{Acknowledgements}
-Эта работа выполнена в рамках Государственного задания, госрегистраци № 0089-2019-0002.
+\section{Благодарности}
+Эта работа выполнена в рамках Государственного задания, госрегистрация № 0089-2019-0002.
 Работа частично поддержана Российским фондом фундаментальных исследований (гранты № 20-03-00147, 19-32-80004).
@@
 %
-После первого резонансного $x$-импульса
+После первого резонансного $x$-импульса получаем
 %

### 2020-06-05 maniscript_rus.tex
Fix

@@
 
-\title{Многоспиновая запутанность в многоквантовом~ЯМР~с дипольно упорядоченным начальным состоянием}
+\title{Многоспиновая запутанность в многоквантовом~ЯМР~с дипольном упорядоченным начальным состоянием}
 
@@
 \abstract{
-Многоквантовый (МК)~ЯМР~с~дипольно упорядоченным начальным состоянием открывает новые возможности для изучения многоспиновой запутанности.
+Многоквантовый (МК)~ЯМР~с~дипольном упорядоченным начальным состоянием открывает новые возможности для изучения многоспиновой запутанности.
 В~данной статье исследуется многоспиновая запутанность в~газе спин-несущих молекул (атомов) в нанопоре
-в~условиях~ЯМР~с дипольно упорядоченным начальным состоянием.
-Для~оценки количества запутанных спинов используется второй момент распределения интенсивностей МК~ЯМР~когерентностей,
+в~условиях~ЯМР~с дипольном упорядоченным начальным состоянием.
+Для~оценки количества запутанных спинов используется второй момент распределения МК~интенсивностей~ЯМР~когерентностей,
 который определяет нижнюю границу квантовой информации Фишера.
@@
 % запутанность, нанопора \sep
-% МК~ЯМР~когерентность \sep
+% МК~когерентностъ~ЯМР \sep
 % второй момент, температура \sep
-% дипольно упорядоченное состояние \sep
+% дипольном упорядоченное состояние \sep
 % двухимпульсная последовательность Брукерта-Джинера
@@
 В частности, она ответственна за преимущество квантовых компьютеров перед их классическими аналогами.
-Недавно продемонстрированное квантовое превосходство ~\cite{Arute2019} на программируемом сверхпроводящем процессоре также связано с понятием запутанности, которое отсутствует в классической физике.
+Недавно продемонстрированное квантовое превосходство~\cite{Arute2019} на программируемом сверхпроводящем процессоре также связано с понятием запутанности, которое отсутствует в классической физике.
 Среди многочисленных методов исследования запутанности мы сосредоточились на многоквантовом~(МК)~ЯМР в~твердых телах~\cite{Baum_1985},
@@
 
-Оказалось также, что МК~ЯМР~спектроскопия~\cite{Baum_1985} позволяет извлекать информацию о многоспиновой запутанности~\cite{G_rttner_2018} с~помощью квантовой информации Фишера~\cite{T_th_2014, Pezz__2018},
+Оказалось также, что МК~спектроскопия~ЯМР~\cite{Baum_1985} позволяет извлекать информацию о многоспиновой запутанности~\cite{G_rttner_2018} с~помощью квантовой информации Фишера~\cite{T_th_2014, Pezz__2018},
 являющейся ключевой концепцией в квантовой теории информации.
@@
 В МК спектроскопии ЯМР эта наблюдаемая определяется оператором полной проекции углового спинового момента на направление сильного внешнего магнитного поля.
-Используя квантовую информацию Фишера~\cite{Liu_2014} для анализа спектра МК~ЯМР,
+Используя квантовую информацию Фишера~\cite{Liu_2014} для анализа МК~спектра~ЯМР,
 можно получить важную информацию о многоспиновой запутанности,
 поскольку существует связь между вторым моментом спектра~\cite{Khitrin_1997} и квантовой информацией Фишера~\cite{G_rttner_2018,Doronin_2019}.
-Кроме того второй момент спектра МК~ЯМР~определяет нижнюю границу квантовой информации Фишера~\cite{G_rttner_2018}.
-Это означает, что МК~ЯМР~спектроскопия является эффективным методом решения квантовых информационных задач.
+Кроме того второй момент МК~спектра~ЯМР~определяет нижнюю границу квантовой информации Фишера~\cite{G_rttner_2018}.
+Это означает, что МК~спектроскопия~ЯМР является эффективным методом решения квантовых информационных задач.
 
@@
 когда та же самая система первоначально подготовлена в дипольном упорядоченном состоянии~\cite{Goldman_1970},
-используя либо метод адиабатического размагничивания во вращающейся системе координат (ВСК) ~\cite{Goldman_1970, Slichter_1961},
+используя либо метод адиабатического размагничивания во вращающейся системе координат (ВСК)~\cite{Goldman_1970, Slichter_1961},
 либо двухимпульную последовательность Брокаерта-Джинера~\cite{Goldman_1970, Jeener_1967}.
-Динамика МК~ЯМР~с таким начальным состоянием моделировалась как для небольших спиновых систем~\cite{Doronin_2007a, Doronin_2007b},
+МК~динамика~ЯМР~с таким начальным состоянием моделировалась как для небольших спиновых систем~\cite{Doronin_2007a, Doronin_2007b},
 так и в системе, состоящей из 200-600 спин-несущих молекул (атомов), заполняющих нанопору~\cite{Doronin_2011}.
@@
 Мы теоретически  показываем, что этот эксперимент~\cite{Jeener_1967} также может выполняться и для промежуточного температурного случая, рассматриваемого в настоящей статье.
-Было показано~\cite{Doronin_2011}, что в МК~эксперименте~ЯМР~с дипольно упорядоченным начальным состоянием МК~когерентности~ЯМР~возникают быстрее,
+Было показано~\cite{Doronin_2011}, что в МК~эксперименте~ЯМР~с дипольном упорядоченным начальным состоянием МК~когерентности~ЯМР~возникают быстрее,
 чем в МК~эксперименте~ЯМР~с начальным термодинамическим равновесным состоянием в сильном внешнем магнитном поле.
@@
 
-В данной статье исследуется многоспиновая запутанность с использованием МК  спектра ~ЯМР~спин-несущих атомов (молекул) в нанопоре, когда система приготовлена в дипольно упорядоченном состоянии.
+В данной статье исследуется многоспиновая запутанность с использованием МК  спектра~ЯМР~спин-несущих атомов (молекул) в нанопоре, когда система приготовлена в дипольном упорядоченном состоянии.
 В разделе~\ref{sec:2} описана разработанная теория МК~динамики~ЯМР~при низкой зеемановской температуре и высокой дипольной температуре.
 Аналитическое решение для МК~динамики~ЯМР трехспиновой системы, полученное при таких же температурах,  описано в разделе~\ref{sec:3}.
-Второй момент спектра~МК~ЯМР~в качестве меры многоспиновой запутанности рассматривается в разделе~\ref{sec:4}.
+Второй момент МК~спектра~ЯМР~в качестве меры многоспиновой запутанности рассматривается в разделе~\ref{sec:4}.
 В разделе~\ref{sec:5} исследуется зависимость многоспиновой запутанности от дипольной температуры и числа спинов в системе.
@@
 Мы предполагаем, что $\omega_{0} = 2\pi \cdot 500 \cdot 10^{6}$~s$^{-1}$ и $D = 2\pi \cdot 10^{4}$~s$^{-1}$.
-В приложении мы доказываем, что двухимпульсная последовательность Брокаерта-Джинера~\cite{Goldman_1970,Jeener_1967} позволяет получить дипольно упорядоченное состояние даже при низкой зеемановской температуре.
-Другим методом создания  дипольно упорядоченного состояния системы является адиабатическое размагничивание~\cite{Goldman_1970,Slichter_1961}.
+В приложении мы доказываем, что двухимпульсная последовательность Брокаерта-Джинера~\cite{Goldman_1970,Jeener_1967} позволяет получить дипольном упорядоченное состояние даже при низкой зеемановской температуре.
+Другим методом создания  дипольном упорядоченного состояния системы является адиабатическое размагничивание~\cite{Goldman_1970,Slichter_1961}.
 Используя эти методы, мы можем получить систему в состоянии термодинамического равновесия с матрицей плотности
@@
 %
-МК~динамика~ЯМР~в нанопоре будет исследована на основе уравнения~(\ref{eq:3}) с начальным состоянием ~(\ref{eq:5}).
+МК~динамика~ЯМР~в нанопоре будет исследована на основе уравнения~(\ref{eq:3}) с начальным состоянием~(\ref{eq:5}).
 Также важно отметить, что гамильтониан $H_{dz}$ частично усредняется быстрой молекулярной диффузией в нанопоре, а усредненный гамильтониан можно записать как \cite{Fel_dman_2004,Doronin_2011}
@@
 
-Задача получения точного решения МК~динамики~ЯМР~трехспиновой системы в дипольно упорядоченном состоянии в нанопоре аналогична задаче, рассмотренной в~\cite{Doronin_2019} для начального термодинамического равновесия в сильном внешнем магнитном поле.
+Задача получения точного решения МК~динамики~ЯМР~трехспиновой системы в дипольном упорядоченном состоянии в нанопоре аналогична задаче, рассмотренной в~\cite{Doronin_2019} для начального термодинамического равновесия в сильном внешнем магнитном поле.
 При решении задачи мы не будем  использовать высокотемпературное приближение~\cite{Goldman_1970}.
@@
     \\
-    0 & 0 & e^{-\frac{-3b}{2}} & 0
+    0 & 0 & e^{\frac{-3b}{2}} & 0
     \\
@@
 
-\section{Второй момент спектра МК~ЯМР~как мера многоспиновой запутанности}
+\section{Второй момент МК~спектра~ЯМР~как мера многоспиновой запутанности}
 \label{sec:4}
@@
 где $J_n(\tau)$ ($n=0,\pm 2, \pm 4, \cdots$) определяется уравнением~(\ref{eq:13}).
-Таким образом, второй момент распределения интенсивностей МК~ЯМР~ дает нижнюю границу квантовой информации Фишера $F_\mathrm{Q}(\rho,I_\mathrm{z})$.
+Таким образом, второй момент распределения МК~интенсивностей~ЯМР~дает нижнюю границу квантовой информации Фишера $F_\mathrm{Q}(\rho,I_\mathrm{z})$.
 Также показано~\cite{T_th_2014,Pezz__2018}, что, если
@@
 %
-где $n$ - целая часть ${N/k}$, то система с матрицей плотности $\rho(\tau)$ содержит  $(k+1)$ запутанных спинов ~\cite{Pezz__2009,Hyllus_2012,T_th_2012}.
+где $n$ - целая часть ${N/k}$, то система с матрицей плотности $\rho(\tau)$ содержит  $(k+1)$ запутанных спинов~\cite{Pezz__2009,Hyllus_2012,T_th_2012}.
 Результаты численного анализа многоспиновой запутанности в системе спин-несущих молекул (атомов), первоначально приготовленных в дипольном упорядоченном состоянии, представлены в следующем разделе.
@@
 
-Рассматриваемая модель спин-несущих молекул (атомов) в нанопоре в дипольно упорядоченном состоянии расширяет возможности исследования многоспиновой запутанности по сравнению с родственной моделью~\cite{Doronin_2019},
+Рассматриваемая модель спин-несущих молекул (атомов) в нанопоре в дипольном упорядоченном состоянии расширяет возможности исследования многоспиновой запутанности по сравнению с родственной моделью~\cite{Doronin_2019},
 в которой система изначально находилась в термодинамическом равновесии в сильном внешнем магнитном поле.
@@
 Мы исследовали многоспиновую запутанность в системе спин-несущих молекул (атомов), заполняющих несферические нанопоры в условиях эксперимента МК~спектроскопии~ЯМР~.
-Спины изначально находились в дипольно упорядоченном состоянии.
+Спины изначально находились в дипольном упорядоченном состоянии.
 Найдена зависимость многоспиновой запутанности от температуры и количества спинов в нанопоре.
@@
 В таком случае $\alpha = 0$ удовлетворяет уравнению~(\ref{eq:5}).
-Таким образом, в рассматриваемом случае мы получаем дипольно упорядоченное состояние.
+Таким образом, в рассматриваемом случае мы получаем дипольном упорядоченное состояние.
 

### 2020-06-05 maniscript_ru.tex
Rename file

--- 2020-06-05 maniscript_rus.tex
@@
 \modulolinenumbers[1]
-\linenumbers
+%\linenumbers
 
@@
 
-\title{Многоспиновая запутанность в многоквантовом~ЯМР~с дипольном упорядоченным начальным состоянием}
+\title{Многоспиновая запутанность в многоквантовом~ЯМР~с дипольным упорядоченным начальным состоянием}
 
@@
 \abstract{
-Многоквантовый (МК)~ЯМР~с~дипольном упорядоченным начальным состоянием открывает новые возможности для изучения многоспиновой запутанности.
+Многоквантовый (МК)~ЯМР~с~дипольным упорядоченным начальным состоянием открывает новые возможности для изучения многоспиновой запутанности.
 В~данной статье исследуется многоспиновая запутанность в~газе спин-несущих молекул (атомов) в нанопоре
-в~условиях~ЯМР~с дипольном упорядоченным начальным состоянием.
-Для~оценки количества запутанных спинов используется второй момент распределения МК~интенсивностей~ЯМР~когерентностей,
+в~условиях~ЯМР~с дипольным упорядоченным начальным состоянием.
+Для~оценки количества запутанных спинов используется второй момент распределения интенсивностей МК когерентностей ~ЯМР~,
 который определяет нижнюю границу квантовой информации Фишера.
@@
 Квантовая информация Фишера описывает скорость изменения квантовых состояний,
-определяемых матрицей плотности, при изменении наблюдаемой,
-которая определяет МК когерентности ЯМР в~МК~спектроскопии~ЯМР~~\cite{Baum_1985}.
+определяемых матрицей плотности, при изменении наблюдаемой, которая
+ответственна за МК когерентности  в~МК~спектроскопии~ЯМР~~\cite{Baum_1985}.
 В МК спектроскопии ЯМР эта наблюдаемая определяется оператором полной проекции углового спинового момента на направление сильного внешнего магнитного поля.
@@
 заполненной газом  спин-несущих молекул в сильном внешнем магнитном поле~\cite{Baugh_2001,Doronin_2009}.
-Термодинамически равновесное начальное состояние системы определялось односпиновым зеемановским взаимодействием с внешним магнитным полем~\cite{Doronin_2007a}.
+Термодинамическое равновесное начальное состояние системы определялось односпиновым зеемановским взаимодействием с внешним магнитным полем~\cite{Doronin_2007a}.
 Однако  многоспиновую запутанность можно  исследовать,
@@
 Мы теоретически  показываем, что этот эксперимент~\cite{Jeener_1967} также может выполняться и для промежуточного температурного случая, рассматриваемого в настоящей статье.
-Было показано~\cite{Doronin_2011}, что в МК~эксперименте~ЯМР~с дипольном упорядоченным начальным состоянием МК~когерентности~ЯМР~возникают быстрее,
+Было показано~\cite{Doronin_2011}, что в МК~эксперименте~ЯМР~с дипольным упорядоченным начальным состоянием МК~когерентности~ЯМР~возникают быстрее,
 чем в МК~эксперименте~ЯМР~с начальным термодинамическим равновесным состоянием в сильном внешнем магнитном поле.
@@
 %
-где $N$ - число спинов в нанопоре, $I^{\pm}_{j}$ - повышающий или понижающий операторы спина $j$, $D$ - константа диполь-дипольного взаимодействия (ДДВ),
+а $N$ - число спинов в нанопоре, $I^{\pm}_{j}$ - повышающий или понижающий операторы спина $j$, $D$ - константа диполь-дипольного взаимодействия (ДДВ),
 усредненная по быстрой молекулярной диффузии спин-несущих атомов (молекул) в нанопоре.
@@
 Мы предполагаем, что $\omega_{0} = 2\pi \cdot 500 \cdot 10^{6}$~s$^{-1}$ и $D = 2\pi \cdot 10^{4}$~s$^{-1}$.
-В приложении мы доказываем, что двухимпульсная последовательность Брокаерта-Джинера~\cite{Goldman_1970,Jeener_1967} позволяет получить дипольном упорядоченное состояние даже при низкой зеемановской температуре.
-Другим методом создания  дипольном упорядоченного состояния системы является адиабатическое размагничивание~\cite{Goldman_1970,Slichter_1961}.
+В приложении мы доказываем, что двухимпульсная последовательность Брокаерта-Джинера~\cite{Goldman_1970,Jeener_1967} позволяет получить дипольное упорядоченное состояние даже при низкой зеемановской температуре.
+Другим методом создания  дипольного упорядоченного состояния системы является адиабатическое размагничивание~\cite{Goldman_1970,Slichter_1961}.
 Используя эти методы, мы можем получить систему в состоянии термодинамического равновесия с матрицей плотности
@@
       \rho_i
-      e^{i H_\mathrm{MQ} \tau} e^{-i \phi I_\mathrm{z}} e^{-i \phi H_\mathrm{MQ} \tau}
+      e^{i H_\mathrm{MQ} \tau} e^{-i \phi I_\mathrm{z}} e^{-i H_\mathrm{MQ} \tau}
       \rho_i
@@
 также~(\ref{eq:7})) состоят из блоков, соответствующих различным значениям углового момента спина~\cite{Doronin_2009}.
-Тогда исследование МК~динамики~ЯМР~может быть сведено к решению ряда задач меньших размеров.
+Тогда исследование МК~динамики~ЯМР~может быть сведено к решению ряда задач меньшей размерности.
 
 Поскольку гамильтониан $H_{MQ}$ уравнения~(\ref{eq:1}) коммутирует с оператором $e^{i\pi I_\mathrm{z}}$, то $2^N \times 2^N$ матрица гамильтониана сводится к двум блокам $2^{N-1} \times 2^{N-1}$~\cite{Doronin_2009}.
-Для нечетных $N$ оба блока вносят одинаковый вклад в МК~когерентности~ЯМР~, и можно решить проблему, используя только один блок $2^{N-1} \times 2^{N-1}$, и удвоить полученные интенсивности.
+Для нечетных $N$ оба блока вносят одинаковый вклад в МК~когерентности~ЯМР~, и можно решить задачу, используя только один блок $2^{N-1} \times 2^{N-1}$, и удвоить полученные интенсивности.
 В наших расчетах мы берем только нечетные числа спинов.
-Используя этот метод, можно исследовать МК~динамику~ЯМР~в системах, состоящих и сотен спинов.
+Используя этот метод, можно исследовать МК~динамику~ЯМР~в системах, состоящих из сотен спинов.
 
@@
 В таком случае $\alpha = 0$ удовлетворяет уравнению~(\ref{eq:5}).
-Таким образом, в рассматриваемом случае мы получаем дипольном упорядоченное состояние.
+Таким образом, в рассматриваемом случае мы получаем дипольное упорядоченное состояние.
 

### 2020-07-11 maniscript_ru.tex
Add acknowledgement
Fix: omega index

@@
     e^{
-      \frac{\hslash \omega}{k} \alpha_\mathrm{z} I_\mathrm{z}
+      \frac{\hslash \omega_{0}}{k} \alpha_\mathrm{z} I_\mathrm{z}
       + \frac{\hslash }{k} \beta_\mathrm{d} H_\mathrm{dz}
@@
 где
-$Z = \mathrm{Tr} \left\{ e^{\frac{\hslash \omega}{k} \alpha_\mathrm{z} I_\mathrm{z} + \frac{\hslash }{k} \beta_\mathrm{d} H_\mathrm{dz}} \right\}$ - статистическая сумма,
+$Z = \mathrm{Tr} \left\{ e^{\frac{\hslash \omega_{0}}{k} \alpha_\mathrm{z} I_\mathrm{z} + \frac{\hslash }{k} \beta_\mathrm{d} H_\mathrm{dz}} \right\}$ - статистическая сумма,
 $\hslash$ и $k$ - константы Планка и Больцмана,
@@
 и $\alpha_\mathrm{z}$, $\beta_\mathrm{d}$ - обратные зеемановская и дипольная температуры.
-Мы рассмотрим случай, когда зеемановская температура  является низкой $({\frac{\hslash \omega}{k} \alpha_\mathrm{z}}\gg 1)$,
+Мы рассмотрим случай, когда зеемановская температура  является низкой $({\frac{\hslash \omega_{0}}{k} \alpha_\mathrm{z}}\gg 1)$,
 а дипольная - высокой $\left( \frac{\hslash{D}}{k}\beta_\mathrm{d} \ll 1\right)$.
@@
 \section{Благодарности}
-Эта работа выполнена в рамках Государственного задания, госрегистрация № 0089-2019-0002.
+Авторы благодарны В.А.Ацаркину за полезное обсуждение. Эта работа выполнена в рамках Государственного задания, госрегистрация № 0089-2019-0002.
 Работа частично поддержана Российским фондом фундаментальных исследований (гранты № 20-03-00147, 19-32-80004).
@@
   \label{eq:a8}
-  0 = \dfrac{1}{Z_f} \tr{ \sz e^{\alpha \omega_0 \sz}}
-  + \dfrac{\beta}{Z_f} \tr{\sz e^{\alpha \omega_0 \sz} \hdz}.
+  0 = \dfrac{1}{Z_f} \tr{ \sz e^{\alpha \omega_{0} \sz}}
+  + \dfrac{\beta}{Z_f} \tr{\sz e^{\alpha \omega_{0} \sz} \hdz}.
 \end{equation}

### 2020-07-11 maniscript_ru.tex
Add bibliography into tex file

@@
 
-\bibliographystyle{unsrt}
+\bibliographystyle{naturemag}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliography{bibliography}
+%\bibliography{bibliography}
+
+\begin{thebibliography}{35}
+\bibitem{Nielsen_2009}
+Nielsen, M. A. and  Chuang, I. L. Quantum Computation and Quantum Information (Cambridge University Press, 2009).
+
+\bibitem{Arute2019}
+Arute, F. et al. Quantum supremacy using a programmable superconducting processor. Nature 574,
+505–510 (2019).
+
+\bibitem{Baum_1985} 
+Baum, J., Munowitz, M., Garroway, A. N. and  Pines, A. Multiple-quantum dynamics in solid state NMR. The Journal of Chemical Physics 83, 2015–2025 (1985).
+
+\bibitem{Furman_2008}
+Furman, G. B., Meerovich, V. M. and  Sokolovsky, V. L. Multiple quantum NMR and entanglement dynamics in dipolar coupling spin systems. Physical Review A 78 (2008).
+
+\bibitem{Furman_2009} 
+Furman, G. B., Meerovich, V. M. and  Sokolovsky, V. L. Nuclear polarization and entanglement in spin systems. Quantum Information Processing 8, 283–291 (2009).
+
+\bibitem{Fel_dman_2008}
+Fel’dman, E. B. and  Pyrkov, A. N. Evolution of spin entanglement and an entanglement witness in multiplequantum NMR experiments. JETP Letters 88, 398–401 (2008).
+
+\bibitem{Fel_dman_2012}
+Fel'dman, E.
+B., Pyrkov, A.
+N.
+and  Zenchuk, A.
+I.
+Solid-state multiple quantum NMR in quantum information processing: exactly solvable models.
+Philosophical Transactions of the Royal Society A: Mathematical, Physical and Engineering Sciences 370, 4690–4712 (2012).
+
+\bibitem{G_rttner_2018}
+G\"arttner, M., Hauke, P. and  Rey, A. M. Relating out-of-time-order correlations to entanglement via multiplequantum coherences. Physical Review Letters 120, 040402 (2018).
+
+\bibitem{T_th_2014}
+T\'oth, G. and  Apellaniz, I. Quantum metrology from a quantum information science perspective. Journal of
+Physics A: Mathematical and Theoretical 47, 424006 (2014).
+
+\bibitem{Pezz__2018}
+Pezz\'e, L., Smerzi, A., Oberthaler, M. K., Schmied, R. and  Treutlein, P. Quantum metrology with nonclassical states of atomic ensembles. Reviews of Modern Physics 90, 035005 (2018).
+
+\bibitem{Liu_2014}
+Liu, J., Xiong, H.-N., Song, F. and  Wang, X. Fidelity susceptibility and quantum fisher information for
+density operators with arbitrary ranks. Physica A: Statistical Mechanics and its Applications 410, 167–173 (2014).
+
+\bibitem{Khitrin_1997}
+Khitrin, A. Growth of NMR multiple-quantum coherences in quasi-one-dimensional systems. Chemical
+Physics Letters 274, 217–220 (1997).
+
+\bibitem{Doronin_2019}
+Doronin, S. I., Fel'dman, E. B. and  Lazarev, I. D. Many-particle entanglement in multiple quantum nuclearmagnetic-resonance spectroscopy. Physical Review A 100, 022330 (2019).
+
+\bibitem{Baugh_2001}
+Baugh, J., Kleinhammes, A., Han, D., Wang, Q. and  Wu, Y. Confinement effect on dipole-dipole interactions in nanofluids. Science 294, 1505–1507 (2001).
+
+\bibitem{Doronin_2009}
+Doronin, S.
+I., Fedorova, A.
+V., Fel’dman, E.
+B.
+and  Zenchuk, A.
+I.
+Multiple quantum NMR dynamics of spin-$\frac 1 2$ carrying molecules of a gas in nanopores.
+The Journal of Chemical Physics 131, 104109 (2009).
+
+\bibitem{Doronin_2007a}
+Doronin, S. I., Fel’dman, E. B., Kuznetsova, E. I., Furman, G. B. and  Goren, S. D. Multiple quantum NMR dynamics in dipolar ordered spin systems. Physical Review B 76, 144405 (2007).
+
+\bibitem{Goldman_1970}
+Goldman, M. Spin temperature and nuclear magnetic resonance in solids (Clarendon Press, 1970).
+
+\bibitem{Slichter_1961}
+Slichter, C. P. and  Holton, W. C. Adiabatic demagnetization in a rotating reference system. Physical Review 122, 1701–1708 (1961).
+
+\bibitem{Jeener_1967}
+Jeener, J. and  Broekaert, P. Nuclear magnetic resonance in solids: Thermodynamic effects of a pair of rf
+pulses. Physical Review 157, 232–240 (1967).
+
+\bibitem{Doronin_2007b}
+Doronin, S.
+I., Fel’dman, E.
+B., Kuznetsova, E.
+I., Furman, G.
+B.
+and  Goren, S.
+D.
+Dipolar temperature and multiple-quantum NMR dynamics in dipolar ordered-spin systems.
+JETP Letters 86, 24–27 (2007).
+
+\bibitem{Doronin_2011}
+Doronin, S. I., Fel’dman, E. B. and  Zenchuk, A. I. The multiple quantum NMR dynamics in systems of
+equivalent spins with a dipolar ordered initial state. Journal of Experimental and Theoretical Physics 113, 495–501 (2011).
+
+\bibitem{Abragam_1982}
+Abragam, A. and  Goldman, M. Nuclear magnetism: Order and disorder (Clarendon Press, United Kingdom,
+1982).
+
+\bibitem{Baum_1986}
+Baum, J. and  Pines, A. NMR studies of clustering in solids. Journal of the American Chemical Society 108,
+7447–7454 (1986).
+
+\bibitem{S_nchez_2014}
+S\'anchez, C.
+M., Acosta, R.
+H., Levstein, P.
+R., Pastawski, H.
+M.
+and  Chattah, A.
+K.
+Clustering and decoherence of correlated spins under double quantum dynamics.
+Physical Review A 90, 042122 (2014).
+
+\bibitem{Munowitz_1987}
+Munowitz, M., Pines, A. and  Mehring, M. Multiple-quantum dynamics in NMR: A directed walk through liouville space. The Journal of Chemical Physics 86, 3172–3182 (1987).
+
+\bibitem{Alvarez_2015}
+Alvarez, G. A., Suter, D. and  Kaiser, R. Localization-delocalization transition in the dynamics of dipolarcoupled nuclear spins. Science 349, 846–848 (2015).
+
+\bibitem{Wei_2018}
+Wei, K. X., Ramanathan, C. and  Cappellaro, P. Exploring localization in nuclear spin chains. Physical Review Letters 120, 070501 (2018).
+
+\bibitem{Fel_dman_2004}
+Fel’dman, E. B. and  Rudavets, M. G. Nonergodic nuclear depolarization in nanocavities. Journal of
+Experimental and Theoretical Physics 98, 207–219 (2004).
+
+\bibitem{Fel_dman_1996}
+Fel’dman, E. B. and  Lacelle, S. Multiple quantum NMR spin dynamics in one-dimensional quantum spin
+chains. Chemical Physics Letters 253, 27–31 (1996).
+
+\bibitem{Zhang_2009}
+Zhang, W. et al. NMR multiple quantum coherences in quasi-one-dimensional spin systems: Comparison
+with ideal spin-chain dynamics. Physical Review A 80, 052323 (2009).
+
+\bibitem{Girolami_2017}
+Girolami, D. and  Yadin, B. Witnessing multipartite entanglement by detecting asymmetry. Entropy 19, 124
+(2017).
+
+\bibitem{Helstrom_1976}
+Helstrom, C. W. Quantum detection and estimation theory (New York : Academic Press, New York, 1976).
+
+\bibitem{Pezz__2009}
+Pezz\'e, L. and Smerzi, A. Entanglement, nonlinear dynamics, and the heisenberg limit. Physical Review
+Letters 102, 100401 (2009).
+
+\bibitem{Hyllus_2012}
+Hyllus, P. et al. Fisher information and multiparticle entanglement. Physical Review A 85, 022321 (2012).
+
+\bibitem{T_th_2012}
+T\'oth, G. Multipartite entanglement and high-precision metrology. Physical Review A 85, 022322 (2012).
+\end{thebibliography}
+
 \end{document}

### 2020-07-24 maniscript_ru.tex
Remove excess packages
Refactor references

--- 2020-07-11 maniscript_ru.tex
@@
 \documentclass[utf8]{jetp}
-
-\usepackage{amsmath}
-\usepackage{amssymb}
-
-\usepackage{soul,color}
-\usepackage{textcomp}
-
-\usepackage{lineno}
-\modulolinenumbers[1]
-%\linenumbers
 
@@
 \newcommand{\hdz}{H_\mathrm{dz}}
-
-\bibliographystyle{unsrt}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliography{bibliography}
+%\bibliographystyle{naturemag}
+%\bibliography{bibliography}
+
+\begin{thebibliography}{35}
+\bibitem{Nielsen_2009}
+M.A.~Nielsen, and  I.L.~Chuang, Cambridge University Press, (2009).
+
+\bibitem{Arute2019}
+F.~Arute, R.~Babbush, J.C.~Bardin et al., Nature 574, 505–510 (2019).
+
+\bibitem{Baum_1985} 
+J.~Baum, M.~Munowitz, A.N.~Garroway and A.~Pines, J.~Chem.~Phys.~83, 2015–2025 (1985).
+
+\bibitem{Furman_2008}
+G.B.~Furman, V.M.~Meerovich, and V.L.~Sokolovsky, Phys.~Rev.~A ~78,~042301 (2008).
+
+\bibitem{Furman_2009} 
+G.B.Furman, V.M.~Meerovich, and V.L.~Sokolovsky, Quantum Information Processing 8, 283–291 (2009).
+
+\bibitem{Fel_dman_2008}
+E.B.~Fel’dman, and A.N.~Pyrkov, JETP Lett.~88,~398–401 (2008).~
+
+\bibitem{Fel_dman_2012}
+E.B.~Fel'dman, A.N.~Pyrkov, and  A.I.~Zenchuk, Philosophical Transactions of the Royal Society A: Mathematical, Physical and Engineering Sciences~370,~4690–4712~(2012).
+
+\bibitem{G_rttner_2018}
+M.~G\"arttner, P.~Hauke, and  A.M.~Rey, Phys.~Rev.~Lett.~120, 040402 (2018).
+
+\bibitem{T_th_2014}
+G.~T\'oth, and I.~Apellaniz,~J Physics A: Mathematical and Theoretical~47,~424006 (2014).
+
+\bibitem{Pezz__2018}
+L.~Pezz\'e, A.~Smerzi, M.K.~Oberthaler et al., Rev.~Mod.~Phys.~90,~035005 (2018).
+
+\bibitem{Liu_2014}
+J.~Liu, H.-N.~Xiong, F.~Song and X. Wang., Physica A: Statistical Mechanics and its Applications.~410,~167–173 (2014).
+
+\bibitem{Khitrin_1997}
+A.~Khitrin, Chem.~Phys.~Lett.~274,~217–220 (1997).
+
+\bibitem{Doronin_2019}
+S.I.~Doronin, E.B.~Fel'dman, and  I.D.~Lazarev,~Phys.~Rev.~A~100,~022330~(2019).
+
+\bibitem{Baugh_2001}
+J.~Baugh, A.~Kleinhammes, D.~Han, and Q.~Wang  et al.~Science~294,~1505–1507 (2001).
+
+\bibitem{Doronin_2009}
+S.I.~Doronin, A.V.Fedorova, E.B.~Fel’dman and A. I. Zenchuk.~J Chem.~Phys.~131,~104109~(2009).
+
+\bibitem{Doronin_2007a}
+S.I.~Doronin, E.B.~Fel’dman, E.I.~Kuznetsova et al.~Phys.~Rev.~B~76,~144405~(2007).
+
+\bibitem{Goldman_1970}
+M.Goldman, Clarendon Press, (1970).
+
+\bibitem{Slichter_1961}
+C.P.~Slichter, and  W.C.~Holton, Phys.~Rev.~122,~1701–1708~(1961).
+
+\bibitem{Jeener_1967}
+J.~Jeener, and P.~Broekaert, Phys.~Rev.~157,232–240~(1967).
+
+\bibitem{Doronin_2007b}
+S.I.~Doronin, E.B.~Fel’dman, E.I.~Kuznetsova et al.~JETP Lett.~86,~24–27 (2007).
+
+\bibitem{Doronin_2011}
+S.I.~Doronin, E.B.~Fel’dman, and  A.I.~Zenchuk, JETP~113,~495–501 (2011).
+
+\bibitem{Abragam_1982}
+A.~Abragam, and M.~Goldman, Clarendon Press, United Kingdom, (1982).
+
+\bibitem{Baum_1986}
+J.Baum, and A.~Pines, JACS~108,~7447–7454~(1986).
+
+\bibitem{S_nchez_2014}
+C.M.~S\'anchez, R.H.~Acosta, P.R.~Levstein et al.~Phys.~Rev.~A~90,~042122~(2014).
+
+\bibitem{Munowitz_1987}
+M.~Munowitz, A.~Pines, and M.~Mehring, J Chem.~Phys.~86,~3172–3182 (1987).
+
+\bibitem{Alvarez_2015}
+G.A.~Alvarez, D.~Suter, and R.~Kaiser, Science~349,~846–848 (2015).
+
+\bibitem{Wei_2018}
+K.X.~Wei, C.~Ramanathan, and P.~Cappellaro, Phys.~Rev.~Lett.~120, 070501 (2018).
+
+\bibitem{Fel_dman_2004}
+E.B.~Fel’dman, and M.G.~Rudavets, JETP 98,~207–219 (2004).
+
+\bibitem{Fel_dman_1996}
+E.B.~Fel’dman, and S.~Lacelle, Chem.~Phys.~Lett.~253,~27–31 (1996).
+
+\bibitem{Zhang_2009}
+W.~Zhang et al., Phys.~Rev.~A 80, 052323 (2009).
+
+\bibitem{Girolami_2017}
+D.~Girolami, and B.~Yadin, Entropy~19,~124 (2017).
+
+\bibitem{Helstrom_1976}
+C.W.~Helstrom, New York: Academic Press, (New York, 1976).
+
+\bibitem{Pezz__2009}
+L.~Pezz\'e, and A.~Smerzi, Phys.~Rev.~Lett.~102,~100401 (2009).
+
+\bibitem{Hyllus_2012}
+P.~Hyllus et al., Phys.~Rev.~A~85,~022321 (2012).
+
+\bibitem{T_th_2012}
+G.~T\'oth, Phys.~Rev.~A~85,~022322 (2012).
+\end{thebibliography}
+
 \end{document}
